### 2020-09-19 manuscript/paper.tex
Initial files

\documentclass[preprint,12pt]{elsarticle}

\usepackage{caption}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{cleveref}

% For the TODOs
\usepackage{xcolor}
\usepackage{xargs}
\usepackage[colorinlistoftodos,textsize=footnotesize]{todonotes}
\newcommand{\todoin}{\todo[inline]}
% from here: https://tex.stackexchange.com/questions/9796/how-to-add-todo-notes
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}

%Boldtype for greek symbols
\newcommand{\teng}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\ten}[1]{\ensuremath{\mathbf{#1}}}

\usepackage{lineno}

\journal{}

\begin{document}

\begin{frontmatter}

  \title{Write title here}
  \author[IITB]{Adepu Dinesh \corref{cor1}}
  \ead{adepu.dinesh.a@gmail.com} \author[IITB]{Prabhu Ramachandran}
  \ead{prabhu@aero.iitb.ac.in} \address[IITB]{Department of Aerospace
    Engineering, Indian Institute of Technology Bombay, Powai, Mumbai 400076}

\cortext[cor1]{Corresponding author}

\begin{abstract}
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
{XXX}, {XXX}, {XXX}

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

% \linenumbers

\section{Introduction}
\label{sec:intro}

\section{Mathematical details}
\label{sec:sph}

\section{Results and discussion}
\label{sec:results}

\subsection{Benchmark 1}
\label{sec:benchmark-1}

\section{Conclusions}
\label{sec:conclusions}

\section*{References}
\bibliographystyle{model6-num-names}
\bibliography{references}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% fill-column: 78
%%% End:

### 2021-07-10 manuscript/paper.tex
3D solid transport in progress

@@
 
-\section{Mathematical details}
-\label{sec:sph}
+\section{Fluid mechanics}
+\label{sec:fluid-mechanics}
+
+\section{Rigid body dynamics}
+\label{sec:rbd-dynamics}
+
+\section{Rigid body contact model}
+\label{sec:rbd-contact-model}
+
+In the SPH literature there are a few ways to model the contact
+between rigid bodies. Few ways to note are
+
+\begin{itemize}
+\item \citet{albano2016modelling} models using pure elastic impingement force
+% Development of the Resolved Fluid-Solid SPH Coupling using Rigid Body Dynamics
+\item \citet{choidevelopment} models using DEM
+\item \citet{zhan2020sph} uses hybrid contact model
+\item \citet{} uses hybrid contact model
+\end{itemize}
+A  SPH  framework  for  dynamic interaction  between  soil  and  rigid  body  system  with  hybrid contact   metho
+
+\section{Rigid fluid coupling}
+\label{sec:rf-coupling}
 
@@
 \label{sec:results}
+\citet{wu2014two} has experimental solution to cube sinking and cube floating
+in a tank.
 
-\subsection{Benchmark 1}
-\label{sec:benchmark-1}
+\subsection{Cylinders collapsing under gravity in a tank}
+\label{sec:cylinders-collapsing-dem}
+
+This benchmark is taken from \citet{chen2019coupled} and
+\citet{wang2019numerical}. This is to validate the rigid contact model.
+
+Six layers of solid cylinders are stacked, and then suddenly released under
+gravity. This is done by 2009 Zhang and Canelas 2016.
+
+\subsection{A block of density 2000 freely falling in to a steady tank}
+\label{sec:2000-density-inside-tank}
+
+This benchmark is taken from \citet{qiu20173d}.
+
+A water tank of 150 $mm$ $\times$ 140 $mm$ $\times$ 140 $mm$ and the water
+depth in the tank was 131 $mm$. The cube with a side length of 20 $mm$. The
+density of the cube is 2120 $kg m^{-3}$. The cube is placed half way before
+the release into the fluid. The spring stiffness coefficient of 1 $\times$
+$10^{5}$ $N m^{-1}$.
+
+\subsection{A block of density $800.52$ floating in a steady tank}
+\label{sec:800-density-floating}
+
+This benchmark is taken from \citet{qiu20173d}, \citet{wang2019numerical}.
+
+A water tank of 150 mm $\times$ 140 mm $\times$ 140 mm and the water depth in
+the tank was 52 $mm$. A rectangular wooden block (with a width of 48 mm,
+length of 49 mm, height 24mm) whose density is 800.52 kg$m^{-1}$ is
+released from the bottom of the tank. We compare the vertical displacement of
+the center of mass of the cube.
+
+\subsection{Dam break with body transport}
+\label{sec:dam-break-with-body-transport}
+
+This benchmark is taken from \citet{wang2019numerical}.
+
+Here we simulate a solid body transport in a dam break.
+
+\subsection{Dam break with multiple body transport}
+\label{sec:dam-break-with-multiple-body-transport}
+
+This benchmark is taken from \citet{wang2019numerical}.
+
+Here we simulate a transport of multiple bodies in a dam break.
+
+\subsection{Cylinders in water collapsed under gravity}
+\label{sec:cylinders-in-water-collapsed-under-gravity}
+
+This benchmark is taken from \citet{chen2019coupled}.
+
+Here we simulate a collapse of cylinders submerged in a water under gravity.
+
+\subsection{Single cube transport in 3d dam break with out any obstructions}
+\label{sec:single-cube-transport-in-3d-dam-break-with-out-any-obstructions}
+
+This benchmark is taken from \citet{ji2019coupled}.
+
+A single body transport under 3d dam break. Here we don't have any
+obstructions. This is done in Canelas 2016 DCDEM paper. This is different from
+Amicarelli paper.
+
+\subsection{Three cube transport in 3d dam break with out any obstructions}
+\label{sec:three-cube-transport-in-3d-dam-break-with-out-any-obstructions}
+
+This benchmark is taken from \citet{ji2019coupled}.
+
+Three cubes transport under 3d dam break. Here we don't have any obstructions.
+This is done in Canelas 2016 DCDEM paper. This is different from Amicarelli
+paper.
 

### 2021-07-10 code/rb_case_1_old.py

@@ -1,0 +1,121 @@
+"""A cube translating and rotating freely without the influence of gravity.
+This is used to test the rigid body dynamics equations.
+"""
+
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+from rigid_body_2d import RigidBody2DScheme
+from rigid_body_3d import RigidBody3DScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+
+
+class Case0(Application):
+    def initialize(self):
+        self.rho0 = 10.0
+        self.hdx = 1.3
+        self.dx = 0.02
+        self.dy = 0.02
+        self.kn = 1e4
+        self.mu = 0.5
+        self.en = 1.0
+        self.dim = 2
+
+        self.dt = 1e-3
+        self.tf = 10
+
+    def create_scheme(self):
+        rb2d = RigidBody2DScheme(rigid_bodies=['body'], boundaries=None, dim=2)
+        rb3d = RigidBody3DScheme(rigid_bodies=['body'], boundaries=None, dim=2)
+        s = SchemeChooser(default='rb2d', rb2d=rb2d, rb3d=rb3d)
+        return s
+
+    def configure_scheme(self):
+        dt = self.dt
+        tf = self.tf
+        self.scheme.configure_solver(dt=dt, tf=tf, pfreq=100)
+
+    def create_particles(self):
+        nx, ny = 10, 10
+        dx = self.dx
+        x, y = np.mgrid[0:1:nx * 1j, 0:1:ny * 1j]
+        x = x.flat
+        y = y.flat
+        m = np.ones_like(x) * dx * dx * self.rho0
+        h = np.ones_like(x) * self.hdx * dx
+        # radius of each sphere constituting in cube
+        rad_s = np.ones_like(x) * dx
+        body = get_particle_array(name='body', x=x, y=y, h=h, m=m, rad_s=rad_s)
+        body_id = np.zeros(len(x), dtype=int)
+        body.add_property('body_id', type='int', data=body_id)
+
+        # setup the properties
+        self.scheme.setup_properties([body])
+
+        self.scheme.scheme.set_linear_velocity(body, np.array([0.5, 0.5, 0.]))
[…]

### 2021-07-10 code/rb_case_2_old.py

@@ -1,0 +1,124 @@
+"""
+Test the collision of two rigid bodues
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.05
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 3
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gy = 0.
+        self.dim = 2
+
+    def create_particles(self):
+        xb, yb = get_2d_block(dx=self.body_spacing,
+                              length=self.body_length,
+                              height=self.body_height)
+        m = self.body_density * self.body_spacing**self.dim
+        body1 = get_particle_array(name='body1',
+                                   x=xb,
+                                   y=yb,
+                                   h=self.body_h,
+                                   m=m,
+                                   rho=self.body_density,
+                                   m_fluid=0.,
+                                   rad_s=self.body_spacing / 2.)
+        body_id = np.zeros(len(xb), dtype=int)
+        dem_id = np.zeros(len(xb), dtype=int)
[…]

### 2021-07-10 code/rb_case_3_old.py

@@ -1,0 +1,129 @@
+"""
+Test the collision of two rigid bodues made of same particle array
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.05
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 3
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gy = 0.
+        self.dim = 2
+
+    def create_particles(self):
+        xf, yf, xt, yt = hydrostatic_tank_2d(
+            self.fluid_length, self.fluid_height, self.tank_height,
+            self.tank_layers, self.fluid_spacing, self.fluid_spacing)
+
+        m_fluid = self.fluid_density * self.fluid_spacing**2.
+
+        xb1, yb1 = get_2d_block(dx=self.body_spacing,
+                                length=self.body_length,
+                                height=self.body_height)
+        m = self.body_density * self.body_spacing**self.dim
+
[…]

### 2021-07-10 code/rigid_body.py

@@ -1,0 +1,700 @@
+"""
+
+We have use 3D formaulation rigid body using rotation matrices to evolve the
+dynamics of the bodies. So we will use one formualtion for both 2d and 3d
+simulations.
+
+Only GTVF (Leap frog) integrator is used. This will make the interaction between
+the rigid bodies seamless as the contact force law DEM is easier to implement.
+
+"""
+import numpy as np
+
+from pysph.sph.scheme import add_bool_argument
+
+from pysph.sph.equation import Equation
+from pysph.sph.scheme import Scheme
+from pysph.sph.scheme import add_bool_argument
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.integrator import EPECIntegrator
+from pysph.sph.wc.gtvf import GTVFIntegrator
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline)
+from textwrap import dedent
+from compyle.api import declare
+
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator_step import IntegratorStep
+
+# from pysph.sph.rigid_body import (BodyForce)
+
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
+                                WendlandQuinticC4, Gaussian, SuperGaussian)
+
+from rigid_body_common import (set_total_mass, set_center_of_mass,
+                               set_body_frame_position_vectors,
+                               set_body_frame_normal_vectors,
+                               set_moment_of_inertia_and_its_inverse,
+                               BodyForce, SumUpExternalForces,
+                               normalize_R_orientation, RigidBodyLVC)
+
+from dem import UpdateTangentialContactsLVCDisplacement
+
+# compute the boundary particles
+from boundary_particles import (get_boundary_identification_etvf_equations,
[…]

### 2021-07-10 code/rigid_body_2d.py

@@ -1,0 +1,682 @@
+import numpy as np
+
+from pysph.sph.scheme import add_bool_argument
+
+from pysph.sph.equation import Equation
+from pysph.sph.scheme import Scheme
+from pysph.sph.scheme import add_bool_argument
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.integrator import EPECIntegrator
+from pysph.sph.wc.gtvf import GTVFIntegrator
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline)
+from textwrap import dedent
+from compyle.api import declare
+
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator_step import IntegratorStep
+
+# from pysph.sph.rigid_body import (BodyForce)
+
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
+                                WendlandQuinticC4, Gaussian, SuperGaussian)
+
+from rigid_body_common import (set_total_mass, set_center_of_mass,
+                               set_moment_of_inertia_izz,
+                               set_body_frame_position_vectors, BodyForce,
+                               SumUpExternalForces)
+
+from numpy import sin, cos
+
+
+class LeapFrogRigidBody2DStep(IntegratorStep):
+    """
+    This step has to be used when Leap frog integrator is used
+    such as 'GTVFIntegrator'
+    """
+    def py_stage1(self, dst, t, dt):
+        dtb2 = dt / 2.
+        for i in range(dst.nb[0]):
+            i3 = 3 * i
+            i9 = 9 * i
+            for j in range(3):
+                dst.xcm[i3 + j] = dst.xcm0[i3 + j] + dtb2 * dst.vcm[i3 + j]
+                dst.vcm[i3 + j] = dst.vcm0[
+                    i3 + j] + dtb2 * dst.force[i3 + j] / dst.total_mass[i]
+
+            # angular velocity in terms of matrix
+            omega = dst.omega[i3 + 2]
+
+            # update the orientation angle
+            dst.orientation_angle[i] = dst.orientation_angle0[i] + omega * dtb2
+
[…]

### 2021-07-10 code/rigid_body_common.py

@@ -1,0 +1,383 @@
+import numpy as np
+from pysph.sph.equation import Equation
+
+from numpy import sqrt, log
+
+
+def set_total_mass(pa):
+    # left limit of body i
+    for i in range(max(pa.body_id) + 1):
+        fltr = np.where(pa.body_id == i)
+        pa.total_mass[i] = np.sum(pa.m[fltr])
+        assert pa.total_mass[i] > 0., "Total mass has to be greater than zero"
+
+
+def set_center_of_mass(pa):
+    # loop over all the bodies
+    for i in range(max(pa.body_id) + 1):
+        fltr = np.where(pa.body_id == i)
+        pa.xcm[3 * i] = np.sum(pa.m[fltr] * pa.x[fltr]) / pa.total_mass[i]
+        pa.xcm[3 * i + 1] = np.sum(pa.m[fltr] * pa.y[fltr]) / pa.total_mass[i]
+        pa.xcm[3 * i + 2] = np.sum(pa.m[fltr] * pa.z[fltr]) / pa.total_mass[i]
+
+
+def set_moment_of_inertia_izz(pa):
+    for i in range(max(pa.body_id) + 1):
+        fltr = np.where(pa.body_id == i)
+        izz = np.sum(pa.m[fltr] * ((pa.x[fltr] - pa.xcm[3 * i])**2. +
+                                   (pa.y[fltr] - pa.xcm[3 * i + 1])**2.))
+        pa.izz[i] = izz
+
+
+def set_moment_of_inertia_and_its_inverse(pa):
+    """Compute the moment of inertia at the beginning of the simulation.
+    And set moment of inertia inverse for further computations.
+    This method assumes the center of mass is already computed."""
+    # no of bodies
+    nb = pa.nb[0]
+    # loop over all the bodies
+    for i in range(nb):
+        fltr = np.where(pa.body_id == i)[0]
+        cm_i = pa.xcm[3 * i:3 * i + 3]
+
+        I = np.zeros(9)
+        for j in fltr:
+            # Ixx
+            I[0] += pa.m[j] * ((pa.y[j] - cm_i[1])**2. +
+                               (pa.z[j] - cm_i[2])**2.)
+
+            # Iyy
+            I[4] += pa.m[j] * ((pa.x[j] - cm_i[0])**2. +
+                               (pa.z[j] - cm_i[2])**2.)
+
+            # Izz
[…]

### 2021-07-10 code/rigid_fluid_coupling.py

@@ -1,0 +1,996 @@
+"""
+
+We have use 3D formaulation rigid body using rotation matrices to evolve the
+dynamics of the bodies. So we will use one formualtion for both 2d and 3d
+simulations.
+
+Only GTVF (Leap frog) integrator is used. This will make the interaction between
+the rigid bodies seamless as the contact force law DEM is easier to implement.
+
+"""
+import numpy as np
+
+from pysph.sph.scheme import add_bool_argument
+
+from pysph.sph.equation import Equation
+from pysph.sph.scheme import Scheme
+from pysph.sph.scheme import add_bool_argument
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.integrator import EPECIntegrator
+from pysph.sph.wc.gtvf import GTVFIntegrator
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline)
+from textwrap import dedent
+from compyle.api import declare
+
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator_step import IntegratorStep
+
+# from pysph.sph.rigid_body import (BodyForce)
+
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
+                                WendlandQuinticC4, Gaussian, SuperGaussian)
+
+from rigid_body_common import (set_total_mass, set_center_of_mass,
+                               set_body_frame_position_vectors,
+                               set_body_frame_normal_vectors,
+                               set_moment_of_inertia_and_its_inverse,
+                               BodyForce, SumUpExternalForces,
+                               normalize_R_orientation, RigidBodyLVC)
+
+from dem import UpdateTangentialContactsLVCDisplacement
+
+# compute the boundary particles
[…]

### 2021-07-10 code/single_body_transport_dam_break.py

@@ -1,0 +1,276 @@
+"""1. A Smoothed Particle Hydrodynamics model for 3D solid body transportin free surface flows
+
+2. Numerical modeling of floating bodies transport for flooding analysis in
+nuclear reactor building
+
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_3d_block
+
+
+def get_fluid_tank_3d(xf, yf, zf, tank_length, tank_height, tank_layers,
+                      tank_spacing):
+    """
+    Given the fluid block and tank dimensions, return the tank geometry
+    here
+
+    tank_length: length in x direction
+    tank_height: length in z direction
+    """
+    # create the left wall
+    min_yf = min(yf)
+    max_yf = max(yf)
+
+    # width is in y direction
+    left_width = max_yf - min_yf
+
+    # create a tank layer on the left
+    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
+                                             length=(tank_layers - 1.)*tank_spacing,
+                                             height=left_width,
+                                             depth=tank_height)
+    # adjust the left wall of tank
+    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
+    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
+    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
+
+    # create a tank layer on the right
+    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
+                                                length=(tank_layers - 1.)*tank_spacing,
+                                                height=left_width,
+                                                depth=tank_height)
+    # adjust the left wall of tank
[…]

### 2021-07-13 manuscript/paper.tex
Fix stack of cylinders so that the initial configuration is same.

@@
 \label{sec:rbd-dynamics}
+
+\subsection{A rigid body on a boundary}
+
+Consider a square rigid body on a surface, the density of the body is 800
+kg$m^{-3}$, the simulation is in 2 dimensions. The side of the body is
+$0.5$m. The stiffness in the normal direction is $10^5$N$m^{-1}$.
+
+\textbf{The analysis corresponding to the current section is done in file
+  code $rigidbodyonasurface.py$}
 

### 2021-07-13 code/bouncing_ball_rigid_body.py

@@ -1,0 +1,131 @@
+"""A ball bouncing on a wall
+"""
+
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+
+
+class Case0(Application):
+    def initialize(self):
+        self.rho0 = 10.0
+        self.hdx = 1.3
+        self.dx = 0.02
+        self.dy = 0.02
+        self.kn = 1e4
+        self.mu = 0.5
+        self.en = 1.0
+        self.dim = 2
+
+        self.dt = 1e-3
+        self.tf = 10
+
+    def create_scheme(self):
+        rfc = RigidFluidCouplingScheme(rigid_bodies=['body'],
+                                       fluids=[],
+                                       boundaries=[],
+                                       dim=2,
+                                       rho0=1000,
+                                       p0=1000000,
+                                       c0=100,
+                                       gy=0.)
+        s = SchemeChooser(default='rfc', rfc=rfc)
+        return s
+
+    def configure_scheme(self):
+        dt = self.dt
+        tf = self.tf
+        self.scheme.configure_solver(dt=dt, tf=tf, pfreq=100)
+
+    def create_particles(self):
+        nx, ny = 10, 10
+        dx = self.dx
+        x, y = np.mgrid[0:1:nx * 1j, 0:1:ny * 1j]
+        x = x.flat
+        y = y.flat
+        m = np.ones_like(x) * dx * dx * self.rho0
+        h = np.ones_like(x) * self.hdx * dx
+        # radius of each sphere constituting in cube
+        rad_s = np.ones_like(x) * dx
+        body = get_particle_array(name='body', x=x, y=y, h=h, m=m, rad_s=rad_s)
+        body_id = np.zeros(len(x), dtype=int)
+        body.add_property('body_id', type='int', data=body_id)
+        body.add_constant('max_tng_contacts_limit', 30)
+        body.add_property('dem_id', type='int', data=0)
+        body.add_constant('kn', np.array([1e8]))
+        body.add_constant('en', np.array([0.8]))
[…]

### 2021-07-13 code/fluids.py

@@ -1,0 +1,719 @@
+"""
+Run it by
+
+python lid_driven_cavity.py --openmp --scheme etvf --integrator pec --internal-flow --pst sun2019 --re 100 --tf 25 --nx 50 --no-edac -d lid_driven_cavity_scheme_etvf_integrator_pec_pst_sun2019_re_100_nx_50_no_edac_output --detailed-output --pfreq 100
+
+"""
+import numpy
+import numpy as np
+
+from pysph.sph.equation import Equation, Group, MultiStageEquations
+from pysph.sph.integrator_step import IntegratorStep
+from pysph.sph.scheme import Scheme
+from pysph.sph.scheme import add_bool_argument
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
+                                WendlandQuinticC4, Gaussian, SuperGaussian)
+
+from solid_mech import (ComputeAuHatETVF, ComputeAuHatETVFSun2019,
+                        SavePositionsIPSTBeforeMoving, AdjustPositionIPST,
+                        CheckUniformityIPST, ComputeAuhatETVFIPST,
+                        ResetParticlePositionsIPST, setup_ipst,
+                        SetHIJForInsideParticles, ContinuityEquationUhat,
+                        ContinuityEquationETVFCorrection, GTVFEOS, ComputeAuHatGTVF,
+                        VelocityGradient2DUhat)
+
+from pysph.sph.wc.edac import (SolidWallPressureBC)
+
+from pysph.sph.integrator import PECIntegrator
+from boundary_particles import (add_boundary_identification_properties)
+
+from boundary_particles import (ComputeNormals, SmoothNormals,
+                                IdentifyBoundaryParticleCosAngleEDAC)
+
+from common import EDACIntegrator
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.sph.wc.linalg import mat_vec_mult
[…]

### 2021-07-13 code/geometry.py

@@ -1,0 +1,155 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from pysph.tools.geometry import get_2d_block, get_2d_tank, get_3d_block
+
+
+def hydrostatic_tank_2d(fluid_length, fluid_height, tank_height, tank_layers,
+                        fluid_spacing, tank_spacing):
+    xt, yt = get_2d_tank(dx=tank_spacing,
+                         length=fluid_length + 2. * tank_spacing,
+                         height=tank_height,
+                         num_layers=tank_layers)
+    xf, yf = get_2d_block(dx=fluid_spacing,
+                          length=fluid_length,
+                          height=fluid_height,
+                          center=[-1.5, 1])
+
+    xf += (np.min(xt) - np.min(xf))
+    yf -= (np.min(yf) - np.min(yt))
+
+    # now adjust inside the tank
+    xf += tank_spacing * (tank_layers)
+    yf += tank_spacing * (tank_layers)
+
+    return xf, yf, xt, yt
+
+
+def get_fluid_tank_3d(fluid_length,
+                      fluid_height,
+                      fluid_depth,
+                      tank_length,
+                      tank_height,
+                      tank_layers,
+                      fluid_spacing,
+                      tank_spacing,
+                      hydrostatic=False):
+    """
+    length is in x-direction
+    height is in y-direction
+    depth is in z-direction
+    """
+    xf, yf, zf = get_3d_block(dx=fluid_spacing,
+                              length=fluid_length,
+                              height=fluid_height,
+                              depth=fluid_depth)
+
+    # create a tank layer on the left
+    xt_left, yt_left, zt_left = get_3d_block(dx=fluid_spacing,
+                                             length=tank_spacing *
+                                             (tank_layers - 1),
+                                             height=tank_height,
+                                             depth=fluid_depth)
+
+    xt_right, yt_right, zt_right = get_3d_block(dx=fluid_spacing,
+                                                length=tank_spacing *
+                                                (tank_layers - 1),
+                                                height=tank_height,
[…]

### 2021-07-13 code/rigid_body_common.py

@@ -195,7 +195,7 @@ class RigidBodyLVC(Equation):
 
     1. Simulation of solid-fluid mixture flow using moving particle methods
     """
-    def __init__(self, dest, sources, kn=1e5, mu=0.5, en=0.8):
+    def __init__(self, dest, sources, kn=1e5, mu=0.45, en=0.8):
         self.kn = kn
         self.kt = 2. / 7. * kn
         self.kt_1 = 1. / self.kt
@@ -246,7 +246,7 @@ class RigidBodyLVC(Equation):
                 vt_y = vr_y - vn_y
                 vt_z = vr_z - vn_z
                 # magnitude of the tangential velocity
-                # vt_magn = (vt_x * vt_x + vt_y * vt_y + vt_z * vt_z)**0.5
+                vt_magn = (vt_x * vt_x + vt_y * vt_y + vt_z * vt_z)**0.5
 
                 m_eff = d_m[d_idx] * s_m[s_idx] / (d_m[d_idx] + s_m[s_idx])
                 eta_n = self.alpha * sqrt(m_eff)
@@ -282,9 +282,9 @@ class RigidBodyLVC(Equation):
                             break
                 # if the particle is not been tracked then assign an index in
                 # tracking history.
-                # ft_x = 0.
-                # ft_y = 0.
-                # ft_z = 0.
+                ft_x = 0.
+                ft_y = 0.
+                ft_z = 0.
 
                 if found == 0:
                     found_at = q1
@@ -292,89 +292,83 @@ class RigidBodyLVC(Equation):
                     d_total_tng_contacts[d_idx] += 1
                     d_tng_idx_dem_id[found_at] = s_dem_id[s_idx]
 
-                # # implies we are tracking the particle
-                # else:
-                #     ####################################################
-                #     # rotate the tangential force to the current plane #
-                #     ####################################################
-                #     ft_magn = (d_tng_fx[found_at]**2. + d_tng_fy[found_at]**2. +
-                #                d_tng_fz[found_at]**2.)**0.5
-                #     ft_dot_nij = (d_tng_fx[found_at] * nx +
-                #                   d_tng_fy[found_at] * ny +
-                #                   d_tng_fz[found_at] * nz)
-                #     # tangential force projected onto the current normal of the
-                #     # contact place
-                #     ft_px = d_tng_fx[found_at] - ft_dot_nij * nx
[…]

### 2021-07-13 code/rigid_body_on_a_surface_2d.py

@@ -1,0 +1,140 @@
+"""
+
+My own idea
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.008 * 2.
+        self.hdx = 1.0
+
+        # the fluid dimensions are
+        # x-dimension (this is in the plane of the paper going right)
+        self.fluid_length = 0.5
+        # y-dimension (this goes into the paper)
+        self.fluid_width = 0.5
+        # z-dimension (this is in the plane of the paper going up)
+        self.fluid_height = 0.35
+
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_length = 3.5
+        self.tank_width = 0.5
+        self.tank_height = 0.5
+        self.tank_spacing = spacing
+        self.tank_layers = 3
+
+        self.obstacle_length = 0.15
+        self.obstacle_width = 0.15
+        self.obstacle_height = 0.75
+        self.obstacle_spacing = spacing
+
+        self.body_height = 0.5
+        self.body_length = 0.5
+        self.body_depth = 0.054
+        self.body_density = 2000.
+        self.body_spacing = spacing
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gy = -9.81
+        self.dim = 2
+
+    def create_particles(self):
+        # create the wall which should be lifted for the water to flow
[…]

### 2021-07-13 code/rigid_body_on_a_surface_3d_from_single_body_transport.py

@@ -89,9 +89,9 @@ def get_fluid_tank_3d(xf, yf, zf, tank_length, tank_height, tank_layers,
     yt_bottom += np.min(yt_front) - np.min(yt_front)
     zt_bottom += np.min(zt_left) - np.max(zt_bottom) - tank_spacing * 1
 
-    xt = np.concatenate([xt_left, xt_right, xt_front, xt_back, xt_bottom])
-    yt = np.concatenate([yt_left, yt_right, yt_front, yt_back, yt_bottom])
-    zt = np.concatenate([zt_left, zt_right, zt_front, zt_back, zt_bottom])
+    xt = xt_bottom
+    yt = yt_bottom
+    zt = zt_bottom
 
     return xt, yt, zt
 
@@ -169,9 +169,9 @@ class RigidFluidCoupling(Application):
         z_obstacle_2 += (np.min(zt) - np.min(z_obstacle_2) + (self.tank_length - 1.) *
                          self.tank_spacing)
 
-        xt = np.concatenate([xt, x_obstacle_1, x_obstacle_2])
-        yt = np.concatenate([yt, y_obstacle_1, y_obstacle_2])
-        zt = np.concatenate([zt, z_obstacle_1, z_obstacle_2])
+        xt = np.concatenate([xt])
+        yt = np.concatenate([yt])
+        zt = np.concatenate([zt])
 
         m_fluid = self.fluid_density * self.fluid_spacing**self.dim
 
@@ -236,6 +236,7 @@ class RigidFluidCoupling(Application):
                                   rho=self.body_density,
                                   m_fluid=m_fluid,
                                   rad_s=self.body_spacing / 2.)
+        body.z[:] += self.body_spacing/2.
         body_id = np.zeros(len(xb), dtype=int)
         body.add_property('body_id', type='int', data=body_id)
         body.add_constant('max_tng_contacts_limit', 30)
@@ -243,17 +244,18 @@ class RigidFluidCoupling(Application):
 
         self.scheme.setup_properties([fluid, tank, body, wall])
 
-
         # body.y[:] += 0.5
         body.m_fsi[:] += self.fluid_density * self.body_spacing**self.dim
         body.rho_fsi[:] = 1000
-        return [fluid, tank, body, wall]
+        return [tank, body]
 
     def create_scheme(self):
         rfc = RigidFluidCouplingScheme(rigid_bodies=["body"],
-                                       fluids=['fluid'],
-                                       boundaries=['tank', 'wall'],
[…]

### 2021-07-13 code/rigid_body_sliding_on_an_horizontal_plane.py

@@ -1,0 +1,149 @@
+"""DISCRETE ELEMENT METHOD FOR 3D SIMULATIONS OF MECHANICAL SYSTEMS OF
+NON-SPHERICAL GRANULAR MATERIALS by JIAN CHEN
+
+Section 5.4
+
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block, rotate
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.008 * 2.
+        self.hdx = 1.0
+
+        # the fluid dimensions are
+        # x-dimension (this is in the plane of the paper going right)
+        self.fluid_length = 0.5
+        # y-dimension (this goes into the paper)
+        self.fluid_width = 0.5
+        # z-dimension (this is in the plane of the paper going up)
+        self.fluid_height = 0.35
+
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_length = 3.5
+        self.tank_width = 0.5
+        self.tank_height = 0.5
+        self.tank_spacing = spacing
+        self.tank_layers = 3
+
+        self.obstacle_length = 0.15
+        self.obstacle_width = 0.15
+        self.obstacle_height = 0.75
+        self.obstacle_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_depth = 0.054
+        self.body_density = 2000.
+        self.body_spacing = spacing
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
[…]

### 2021-07-13 code/rigid_body_sliding_on_an_inclined_plane_2d.py

@@ -1,0 +1,149 @@
+"""DISCRETE ELEMENT METHOD FOR 3D SIMULATIONS OF MECHANICAL SYSTEMS OF
+NON-SPHERICAL GRANULAR MATERIALS by JIAN CHEN
+
+Section 5.4
+
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block, rotate
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.008 * 2.
+        self.hdx = 1.0
+
+        # the fluid dimensions are
+        # x-dimension (this is in the plane of the paper going right)
+        self.fluid_length = 0.5
+        # y-dimension (this goes into the paper)
+        self.fluid_width = 0.5
+        # z-dimension (this is in the plane of the paper going up)
+        self.fluid_height = 0.35
+
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_length = 3.5
+        self.tank_width = 0.5
+        self.tank_height = 0.5
+        self.tank_spacing = spacing
+        self.tank_layers = 3
+
+        self.obstacle_length = 0.15
+        self.obstacle_width = 0.15
+        self.obstacle_height = 0.75
+        self.obstacle_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_depth = 0.054
+        self.body_density = 2000.
+        self.body_spacing = spacing
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
[…]

### 2021-07-13 code/stack_of_cylinders.py

@@ -1,0 +1,400 @@
+"""
+Simulation of solid-fluid mixture flow using moving particle methods
+Shuai Zhang
+"""
+from __future__ import print_function
+import numpy as np
+
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from pysph.base.utils import (get_particle_array)
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.tools.geometry import get_2d_block
+from geometry import hydrostatic_tank_2d
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        print("no_of_points")
+        print(no_of_points)
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+def create_circle(diameter=1, spacing=0.05, center=None):
+    radius = diameter/2.
+    xtmp, ytmp = get_2d_block(spacing, diameter+spacing, diameter+spacing)
+    x = []
+    y = []
+    for i in range(len(xtmp)):
+        dist = xtmp[i]**2. + ytmp[i]**2.
+        if dist < radius**2:
+            x.append(xtmp[i])
+            y.append(ytmp[i])
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+class ZhangStackOfCylinders(Application):
+    def initialize(self):
+        self.dim = 2
+        spacing = 1.
+
+        self.dam_length = 26 * 1e-2
+        self.dam_height = 26 * 1e-2
[…]

### 2021-07-20 code/rigid_body_on_a_surface_2d.py
Add Bui 2014 bouncing cube example

@@ -1,6 +1,10 @@
 """
 
-My own idea
+A novel computational approach for large deformation and
+post-failure analyses of segmental retaining wall systems
+
+
+This is basically bouncing cube example.
 """
 import numpy as np
 
@@ -22,7 +26,7 @@ from pysph.tools.geometry import get_2d_block
 
 class RigidFluidCoupling(Application):
     def initialize(self):
-        spacing = 0.008 * 2.
+        spacing = 0.125 * 1e-2
         self.hdx = 1.0
 
         # the fluid dimensions are
@@ -47,8 +51,8 @@ class RigidFluidCoupling(Application):
         self.obstacle_height = 0.75
         self.obstacle_spacing = spacing
 
-        self.body_height = 0.5
-        self.body_length = 0.5
+        self.body_height = 2.5 * 1e-2
+        self.body_length = 3.2 * 1e-2
         self.body_depth = 0.054
         self.body_density = 2000.
         self.body_spacing = spacing
@@ -67,9 +71,10 @@ class RigidFluidCoupling(Application):
 
     def create_particles(self):
         # create the wall which should be lifted for the water to flow
-        xw, yw = get_2d_block(self.fluid_spacing, 1., self.tank_layers*self.tank_spacing)
+        xw, yw = get_2d_block(self.fluid_spacing, 3. * self.body_length, 0*self.tank_spacing)
+        yw -= self.body_spacing / 2.
         m = self.body_density * self.body_spacing**self.dim
-        rad_s = self.fluid_spacing
+        rad_s = self.fluid_spacing / 2.
         wall = get_particle_array(x=xw,
                                   y=yw,
                                   m=m,
@@ -77,13 +82,19 @@ class RigidFluidCoupling(Application):
                                   h=self.h,
                                   rho=self.fluid_density,
                                   rad_s=rad_s,
-                                  name="wall")
+                                  name="wall",
+                                  constants={
+                                      'E': 69 * 1e9,
+                                      'poisson_ratio': 0.3,
+                                  })
         wall.add_property('dem_id', type='int', data=1)
 
         # Create the rigid body
         xb, yb = get_2d_block(dx=self.body_spacing,
                               length=self.body_length,
                               height=self.body_height)
+        yb += np.max(yw) - np.min(yb) + self.body_spacing
+        yb += 0.1 - self.body_height / 2.
 
[…]

### 2021-07-20 code/rigid_fluid_coupling.py

@@ -36,7 +36,8 @@ from rigid_body_common import (set_total_mass, set_center_of_mass,
                                set_body_frame_normal_vectors,
                                set_moment_of_inertia_and_its_inverse,
                                BodyForce, SumUpExternalForces,
-                               normalize_R_orientation, RigidBodyLVC)
+                               normalize_R_orientation, RigidBodyLVC,
+                               RigidBodyCanelas)
 
 from dem import UpdateTangentialContactsLVCDisplacement, UpdateTangentialContactsLVCForce
 
@@ -742,8 +743,7 @@ class RigidFluidCouplingScheme(Scheme):
                               gz=self.gz))
 
             for name in self.rigid_bodies:
-                g5.append(RigidBodyLVC(dest=name, sources=self.rigid_bodies+self.boundaries,
-                                       kn=self.kn))
+                g5.append(RigidBodyCanelas(dest=name, sources=self.rigid_bodies+self.boundaries))
 
             # add the force due to fluid
             if len(self.fluids) > 0:

### 2021-07-20 code/single_cube_transport_in_3d_dam_break_with_out_any_obstructions.py

@@ -1,0 +1,260 @@
+"""Taken from \cite{ji2019coupled}, this is inturn was done in
+\citet{canelas2016sph}.
+
+
+This case models a single cube in the centre of the flume, with a face directly
+aligned with the flow direction.
+"""
+
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_3d_block
+
+
+def get_fluid_tank_3d(xf, yf, zf, tank_length, tank_height, tank_layers,
+                      tank_spacing):
+    """
+    Given the fluid block and tank dimensions, return the tank geometry
+    here
+
+    tank_length: length in x direction
+    tank_height: length in z direction
+    """
+    # create the left wall
+    min_yf = min(yf)
+    max_yf = max(yf)
+
+    # width is in y direction
+    left_width = max_yf - min_yf
+
+    # create a tank layer on the left
+    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
+                                             length=(tank_layers - 1.)*tank_spacing,
+                                             height=left_width,
+                                             depth=tank_height)
+    # adjust the left wall of tank
+    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
+    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
+    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
+
+    # create a tank layer on the right
+    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
+                                                length=(tank_layers - 1.)*tank_spacing,
+                                                height=left_width,
+                                                depth=tank_height)
+    # adjust the left wall of tank
+    xt_right += tank_length - (np.max(xt_right) - np.min(xf))
[…]

### 2021-08-02 code/2000_density_cube_drowning_3d.py
Stack of cylinders fix. Add new Rigid fluid coupling benchmarks. In progress

@@ -1,0 +1,360 @@
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_3d_block
+
+
+def get_fluid_tank_3d(xf, yf, zf, tank_height, tank_layers,
+                      tank_spacing):
+    """
+    Given the fluid block and tank dimensions, return the tank geometry
+    here
+
+    tank_length: length in x direction
+    tank_height: length in z direction
+    """
+    # create the left wall
+    min_yf = min(yf)
+    max_yf = max(yf)
+
+    # width is in y direction
+    left_width = max_yf - min_yf
+
+    # create a tank layer on the left
+    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
+                                             length=(tank_layers - 1.)*tank_spacing,
+                                             height=left_width,
+                                             depth=tank_height)
+    # adjust the left wall of tank
+    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
+    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
+    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
+
+    # create a tank layer on the right
+    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
+                                                length=(tank_layers - 1.)*tank_spacing,
+                                                height=left_width,
+                                                depth=tank_height)
+    # adjust the left wall of tank
+    xt_right += (np.max(xt_right) - np.min(xf)) + 1. * tank_spacing
+    yt_right += np.min(yf) - np.min(yt_right) + 0. * tank_spacing
+    zt_right += np.min(zf) - np.min(zt_right) + 0. * tank_spacing
+
+    # create the wall in the front
+    xt_front, yt_front, zt_front = get_3d_block(
+        dx=tank_spacing,
[…]

### 2021-08-02 code/rigid_body_on_a_surface_2d.py

@@ -93,6 +93,7 @@ class RigidFluidCoupling(Application):
         xb, yb = get_2d_block(dx=self.body_spacing,
                               length=self.body_length,
                               height=self.body_height)
+        xb += self.body_spacing / 2.
         yb += np.max(yw) - np.min(yb) + self.body_spacing
         yb += 0.1 - self.body_height / 2.
 
@@ -129,7 +130,8 @@ class RigidFluidCoupling(Application):
                                        fluids=None,
                                        boundaries=['wall'],
                                        dim=2,
-                                       en=0.1,
+                                       en=.5,
+                                       Cn=1e-3,
                                        rho0=self.fluid_density,
                                        p0=self.p0,
                                        c0=self.c0,
@@ -143,7 +145,7 @@ class RigidFluidCoupling(Application):
         scheme = self.scheme
         scheme.configure(h=self.h)
 
-        dt = 1e-5
+        dt = 5e-5
         print("DT: %s" % dt)
         tf = 1.
 

### 2021-08-02 code/rigid_fluid_coupling.py

@@ -37,7 +37,9 @@ from rigid_body_common import (set_total_mass, set_center_of_mass,
                                set_moment_of_inertia_and_its_inverse,
                                BodyForce, SumUpExternalForces,
                                normalize_R_orientation, RigidBodyLVC,
-                               RigidBodyCanelas)
+                               RigidBodyCanelasRigidRigid,
+                               RigidBodyCanelasRigidWall,
+                               RigidBodyBuiRigidRigid)
 
 from dem import UpdateTangentialContactsLVCDisplacement, UpdateTangentialContactsLVCForce
 
@@ -553,10 +555,9 @@ class EDACEquationFSI(Equation):
 
 class RigidFluidCouplingScheme(Scheme):
     def __init__(self, fluids, boundaries, rigid_bodies, dim, rho0, p0, c0, h,
-                 nu, kn=1e7, en=0.5,
-                 gamma=7.0, integrator="rk2", gx=0.0, gy=0.0, gz=0.0,
-                 alpha=0.1, beta=0.0, kernel_choice="1", kernel_factor=3,
-                 edac_alpha=0.5):
+                 nu, kn=1e7, en=0.5, Cn=1.4*1e-5, gamma=7.0, integrator="rk2",
+                 dem="bui", gx=0.0, gy=0.0, gz=0.0, alpha=0.1, beta=0.0,
+                 kernel_choice="1", kernel_factor=3, edac_alpha=0.5):
         self.rigid_bodies = rigid_bodies
 
         if boundaries is None:
@@ -583,12 +584,14 @@ class RigidFluidCouplingScheme(Scheme):
         # rigid body parameters
         self.kn = kn
         self.en = en
+        self.Cn = Cn
 
         self.dim = dim
 
         self.kernel = CubicSpline
 
         self.integrator = integrator
+        self.dem = dem
 
         self.rho0 = rho0
         self.p0 = p0
@@ -613,8 +616,16 @@ class RigidFluidCouplingScheme(Scheme):
                            choices=choices,
                            help="Specify what integrator to use " % choices)
 
+        choices = ['bui', 'canelas']
+        group.add_argument("--dem",
+                           action="store",
+                           dest='dem',
+                           default="bui",
+                           choices=choices,
+                           help="DEM interaction " % choices)
+
     def consume_user_options(self, options):
-        _vars = ['integrator']
+        _vars = ['integrator', 'dem']
         data = dict((var, self._smart_getattr(options, var)) for var in _vars)
         self.configure(**data)
 
[…]

### 2021-08-02 code/stack_of_cylinders.py

@@ -107,7 +107,7 @@ class ZhangStackOfCylinders(Application):
         self.wall_height = 20 * 1e-2
         self.wall_spacing = spacing * 1e-3
         self.wall_layers = 2
-        self.wall_time = 0.2
+        self.wall_time = 0.1
         self.wall_rho = 2700
 
         # simulation properties
@@ -118,7 +118,7 @@ class ZhangStackOfCylinders(Application):
 
         # solver data
         self.tf = 0.5 + self.wall_time
-        self.dt = 1e-4
+        self.dt = 5e-5
 
         # Rigid body collision related data
         self.limit = 6
@@ -136,7 +136,11 @@ class ZhangStackOfCylinders(Application):
                                        y=yc,
                                        h=h,
                                        m=m,
-                                       rad_s=rad_s)
+                                       rad_s=rad_s,
+                                       constants={
+                                           'E': 69 * 1e9,
+                                           'poisson_ratio': 0.3,
+                                       })
         cylinders.add_property('dem_id', type='int', data=dem_id)
         cylinders.add_property('body_id', type='int', data=body_id)
         cylinders.add_constant('max_tng_contacts_limit', 10)
@@ -150,7 +154,11 @@ class ZhangStackOfCylinders(Application):
         dam = get_particle_array(x=xd,
                                  y=yd,
                                  rad_s=self.dam_spacing / 2.,
-                                 name="dam")
+                                 name="dam",
+                                 constants={
+                                     'E': 30 * 1e9,
+                                     'poisson_ratio': 0.3,
+                                 })
         dam.add_property('dem_id', type='int', data=max(body_id) + 1)
 
         # create wall with normals
@@ -164,7 +172,11 @@ class ZhangStackOfCylinders(Application):
         wall = get_particle_array(x=xw,
                                   y=yw,
                                   rad_s=self.wall_spacing / 2.,
-                                  name="wall")
+                                  name="wall",
+                                  constants={
+                                      'E': 30 * 1e9,
+                                      'poisson_ratio': 0.3,
+                                  })
         wall.add_property('dem_id', type='int', data=max(body_id) + 2)
 
         self.scheme.setup_properties([cylinders, dam, wall])
@@ -352,7 +364,7 @@ class ZhangStackOfCylinders(Application):
[…]

### 2021-08-02 code/water_entry_of_cylinder_2d.py

@@ -1,0 +1,288 @@
+"""Numerical simulation of interactions between free surface and rigid body
+using a robust SPH method, Pengnan Sun, 2015
+
+3.1.3 Water entry of 2-D cylinder
+
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.005
+        self.hdx = 1.0
+
+        # the fluid dimensions are
+        # x-dimension (this is in the plane of the paper going right)
+        self.L = 0.7
+        self.fluid_length = 1. * self.L
+        # y-dimension (this is in the plane of the paper going up)
+        self.fluid_height = 1. * self.L
+
+        self.fluid_density = 1000.
+        self.fluid_spacing = spacing
[…]

### 2022-01-11 manuscript/paper.tex
Add Bui 2014 bouncing cube example
Stack of cylinders fix. Add new Rigid fluid coupling benchmarks. In progress
Implement new contact force law and validate examples

--- 2020-09-19 manuscript/paper.tex
@@
 
-\section{Mathematical details}
-\label{sec:sph}
+\section{Fluid mechanics}
+\label{sec:fluid-mechanics}
+
+\section{Rigid body dynamics}
+\label{sec:rbd-dynamics}
+
+\subsection{A rigid body on a boundary}
+
+Consider a square rigid body on a surface, the density of the body is 800
+kg$m^{-3}$, the simulation is in 2 dimensions. The side of the body is
+$0.5$m. The stiffness in the normal direction is $10^5$N$m^{-1}$.
+
+\textbf{The analysis corresponding to the current section is done in file
+  code $rigidbodyonasurface.py$}
+
+\section{Rigid body contact model}
+\label{sec:rbd-contact-model}
+
+In the SPH literature there are a few ways to model the contact
+between rigid bodies. Few ways to note are
+
+\begin{itemize}
+\item \citet{albano2016modelling} models using pure elastic impingement force
+% Development of the Resolved Fluid-Solid SPH Coupling using Rigid Body Dynamics
+\item \citet{choidevelopment} models using DEM
+\item \citet{zhan2020sph} uses hybrid contact model
+\item \citet{} uses hybrid contact model
+\end{itemize}
+A  SPH  framework  for  dynamic interaction  between  soil  and  rigid  body  system  with  hybrid contact   metho
+
+\section{Rigid fluid coupling}
+\label{sec:rf-coupling}
 
@@
 \label{sec:results}
+\citet{wu2014two} has experimental solution to cube sinking and cube floating
+in a tank.
 
-\subsection{Benchmark 1}
-\label{sec:benchmark-1}
+\begin{enumerate}
+\item Stack of cylinders (\citet{canelas2016sph}, \citet{wang2019numerical})
+\item A rigid box rotating and sinking in viscous liquid
+  (\citet{sun2015numerical})
+\item Water entry of 2-D cylinder (\citet{sun2015numerical})
+\item Water wedge entry (\citet{sun2015numerical})
+\item Dam break flow against cubes, single cube (\citet{canelas2016sph},
+  \citet{ji2019coupled})
+\item Dam break flow against cubes, three cubes (\citet{canelas2016sph},
+  \citet{ji2019coupled})
+\item Dam break flow against cubes, six cubes (\citet{canelas2016sph},
+  \citet{ji2019coupled})
+\item A block of density $800.52$ floating in a steady tank
+  (\citet{qiu20173d}, \citet{wang2019numerical})
+\item A block of density 2000 freely falling in to a steady tank
+  (\citet{qiu20173d}, \citet{wang2019numerical})
+\item Cylinders in water collapsed under gravity (\citet{chen2019coupled})
+\item Dam break with body transport (\citet{wang2019numerical})
+\item Dam break with multiple bodies transport (\citet{wang2019numerical})
+\end{enumerate}
+
+%
+\subsection{(Partially) Stack of cylinders}
+
+Stack of cylinders (\citet{canelas2016sph}, \citet{wang2019numerical})
+
+\begin{itemize}
+\item (TODO) Automan
+\item (TODO) Code implementation
+\item (TODO) Write in paper
+\item (TODO) Results
+\end{itemize}
+%
+\subsection{(Partially) A rigid box rotating and sinking in viscous liquid}
+
+A rigid box rotating and sinking in viscous liquid
+  (\citet{sun2015numerical})
+%
+\subsection{(Partially) Water entry of 2-D cylinder}
+
+Water entry of 2-D cylinder (\citet{sun2015numerical})
+%
+\subsection{(TODO) Water wedge entry}
+Water wedge entry (\citet{sun2015numerical})
+
+First preliminary creation of wedge, then by removing the boundary particles,
+add the particles such that they represent better boundary for wedge
+
+%
+
+\subsection{(TODO) Dam break flow against cubes, single cube}
+% code/dam_break_flow_against_a_single_cube.py
+Dam break flow against cubes, single cube (\citet{canelas2016sph},
+  \citet{ji2019coupled})
+%
+\subsection{(TODO) Dam break flow against cubes, three cubes}
+Dam break flow against cubes, three cubes (\citet{canelas2016sph},
+  \citet{ji2019coupled})
+%
+\subsection{(TODO) Dam break flow against cubes, six cubes}
+Dam break flow against cubes, six cubes (\citet{canelas2016sph},
+  \citet{ji2019coupled})
+%
+\subsection{(TODO) A block of density $800.52$ floating in a steady tank}
+A block of density $800.52$ floating in a steady tank
+  (\citet{qiu20173d}, \citet{wang2019numerical})
+%
+\subsection{(TODO) A block of density 2000 freely falling in to a steady tank}
+A block of density 2000 freely falling in to a steady tank
+  (\citet{qiu20173d}, \citet{wang2019numerical})
+%
+\subsection{(TODO) Cylinders in water collapsed under gravity}
+Cylinders in water collapsed under gravity (\citet{chen2019coupled})
+%
+\subsection{(TODO) Dam break with body transport}
+Dam break with body transport (\citet{wang2019numerical})
+%
+\subsection{(TODO) Dam break with multiple bodies transport}
+Dam break with multiple bodies transport (\citet{wang2019numerical})
+%
 
@@
 \label{sec:conclusions}
+
+\section*{References}
+\label{sec:references}
+
+The adaptive fluid solid interaction is done by \citet{hu2019consistent}.
 

### 2022-01-11 automate.py

@@ -1,19 +1,450 @@
 #!/usr/bin/env python
 import os
+import matplotlib.pyplot as plt
 
+from itertools import product
+import json
 from automan.api import PySPHProblem as Problem
-from automan.api import Automator, Simulation, filter_cases
+from automan.api import Automator, Simulation, filter_by_name
+from automan.jobs import free_cores
+
 import numpy as np
 import matplotlib
+from pysph.solver.utils import load, get_files
+
 matplotlib.use('pdf')
 
-# XXX
+n_core = 24
+n_thread = 24 * 2
+backend = ' --openmp '
+
+
+def pretty(d, indent=0):
+    for key, value in d.items():
+        print('\t' * indent + str(key))
+        if isinstance(value, dict):
+            pretty(value, indent + 1)
+        else:
+            print('\t' * (indent + 1) + str(value))
+
+
+def scheme_opts(params):
+    if isinstance(params, tuple):
+        return params[0]
+    return params
+
+
+def get_files_at_given_times(files, times):
+    from pysph.solver.utils import load
+    result = []
+    count = 0
+    for f in files:
+        data = load(f)
+        t = data['solver_data']['t']
+        if count >= len(times):
+            break
+        if abs(t - times[count]) < t * 1e-8:
+            result.append(f)
+            count += 1
+        elif t > times[count]:
+            result.append(f)
+            count += 1
+    return result
+
+
+def get_files_at_given_times_from_log(files, times, logfile):
+    import re
+    result = []
+    time_pattern = r"output at time\ (\d+(?:\.\d+)?)"
+    file_count, time_count = 0, 0
+    with open(logfile, 'r') as f:
+        for line in f:
+            if time_count >= len(times):
+                break
+            t = re.findall(time_pattern, line)
+            if t:
+                if float(t[0]) in times:
+                    result.append(files[file_count])
+                    time_count += 1
+                elif float(t[0]) > times[time_count]:
+                    result.append(files[file_count])
+                    time_count += 1
+                file_count += 1
+    return result
+
+
+class StackOfCylinders(Problem):
+    def get_name(self):
+        return 'stack_of_cylinders'
+
+    def setup(self):
+        get_path = self.input_path
+
+        cmd = 'python code/stack_of_cylinders.py' + backend
+
+        # Base case info
+        self.case_info = {
+            'bui': (dict(
+                pfreq=100,
+                dem="bui",
+                ), 'Bui'),
+        }
+
[…]

### 2022-01-11 code/rb_case_2.py

@@ -1,0 +1,137 @@
+"""
+Test the collision of two rigid bodues
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_body_3d import RigidBody3DScheme
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.05
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 3
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gy = 0.
+        self.dim = 2
+
+    def create_particles(self):
+        xb, yb = get_2d_block(dx=self.body_spacing,
+                              length=self.body_length,
+                              height=self.body_height)
+        m = self.body_density * self.body_spacing**self.dim
+        body1 = get_particle_array(name='body1',
+                                   x=xb,
+                                   y=yb,
+                                   h=self.body_h,
+                                   m=m,
+                                   rho=self.body_density,
+                                   m_fluid=0.,
+                                   rad_s=self.body_spacing / 2.,
+                                   constants={
[…]

### 2022-01-11 code/rb_case_3.py

@@ -1,0 +1,170 @@
+"""
+Test the collision of two rigid bodues made of same particle array
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_body_3d import RigidBody3DScheme
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.05
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 5
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gx = 0.
+        self.gy = -9.81
+        self.gz = 0.
+        self.dim = 2
+
+    def create_particles(self):
+        xf, yf, xt, yt = hydrostatic_tank_2d(
+            self.fluid_length, self.fluid_height, self.tank_height,
+            self.tank_layers, self.body_spacing, self.body_spacing)
+
+        m_fluid = self.fluid_density * self.fluid_spacing**2.
+
+        xb1, yb1 = get_2d_block(dx=self.body_spacing,
+                                length=self.body_length,
+                                height=self.body_height)
[…]

### 2022-01-11 code/rigid_body_3d.py

@@ -8,7 +8,7 @@ from pysph.sph.scheme import add_bool_argument
 from pysph.tools.sph_evaluator import SPHEvaluator
 from pysph.sph.equation import Group, MultiStageEquations
 from pysph.sph.integrator import EPECIntegrator
-from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline)
+from pysph.base.kernels import (QuinticSpline)
 from textwrap import dedent
 from compyle.api import declare
 
@@ -17,18 +17,212 @@ from pysph.sph.integrator_step import IntegratorStep
 
 # from pysph.sph.rigid_body import (BodyForce)
 
-from pysph.base.kernels import (CubicSpline, WendlandQuintic,
-                                QuinticSpline, WendlandQuinticC4,
-                                Gaussian, SuperGaussian)
+from pysph.base.kernels import (QuinticSpline)
 
-from rigid_body_common import (
-    set_total_mass, set_center_of_mass,
-    set_body_frame_position_vectors,
-    set_moment_of_inertia_and_its_inverse,
-    BodyForce,
-    SumUpExternalForces,
-    normalize_R_orientation)
+from pysph.sph.wc.gtvf import GTVFIntegrator
+from rigid_body_common import (add_properties_stride,
+                               set_total_mass, set_center_of_mass,
+                               set_body_frame_position_vectors,
+                               set_body_frame_normal_vectors,
+                               set_moment_of_inertia_and_its_inverse,
+                               BodyForce, SumUpExternalForces,
+                               normalize_R_orientation,
+                               ComputeContactForceNormals,
+                               ComputeContactForceDistanceAndClosestPoint,
+                               ComputeContactForce)
+
+# compute the boundary particles
+from boundary_particles import (get_boundary_identification_etvf_equations,
+                                add_boundary_identification_properties)
 from numpy import sin, cos
+
+
+class GTVFRigidBody3DStep(IntegratorStep):
+    def py_stage1(self, dst, t, dt):
+        dtb2 = dt / 2.
+        for i in range(dst.nb[0]):
+            i3 = 3 * i
+            i9 = 9 * i
[…]

### 2022-01-11 code/rigid_body_common.py

@@ -1,3 +1,8 @@
+"""
+The force interaction between, two rigid bodies, and rigid body wall and
+rigid body and an elastic body (with and with out erosion is different and
+needs different equations)
+"""
 import numpy as np
 from pysph.sph.equation import Equation
 
@@ -6,6 +11,11 @@ from math import sin, pi, log
 
 # constants
 M_PI = pi
+
+
+def add_properties_stride(pa, stride=1, *props):
+    for prop in props:
+        pa.add_property(name=prop, stride=stride)
 
 
 def set_total_mass(pa):
@@ -193,592 +203,6 @@ def normalize_R_orientation(orien):
     orien[8] = b3[2]
 
 
-class RigidBodyLVC(Equation):
-    """
-    linearViscoelasticContactModelWithCoulombFriction
-
-    1. Simulation of solid-fluid mixture flow using moving particle methods
-    """
-    def __init__(self, dest, sources, kn=1e5, nu=0.3, alpha=0.3, mu=0.001):
-        self.kn = kn
-        self.kt = self.kn / (2. * (1. + nu))
-        self.nu = nu
-        self.kt_1 = 1. / self.kt
-        self.mu = mu
-        self.alpha = alpha
-        super(RigidBodyLVC, self).__init__(dest, sources)
-
-    def loop(self, d_idx, d_total_mass, d_u, d_v, d_w, d_fx, d_fy, d_fz,
-             d_tng_idx, d_tng_idx_dem_id, d_tng_fx, d_tng_fy, d_tng_fz,
-             d_total_tng_contacts, d_dem_id, d_body_id,
-             d_max_tng_contacts_limit, XIJ,
-             RIJ, d_rad_s, s_idx, s_m, s_u, s_v, s_w, s_rad_s, s_dem_id, dt,
-             t):
-        p, q1, tot_ctcs, j, found_at, found = declare('int', 6)
-        overlap = -1.
-
-        if d_dem_id[d_idx] != s_dem_id[s_idx]:
-            # check the particles are not on top of each other.
-            if RIJ > 0:
-                overlap = d_rad_s[d_idx] + s_rad_s[s_idx] - RIJ
-
-            # ---------- force computation starts ------------
-            # if particles are overlapping
-            if overlap > 0:
-                # normal vector (nij) passing from d_idx to s_idx, i.e., i to j
-                rinv = 1.0 / RIJ
-                # in PySPH: XIJ[0] = d_x[d_idx] - s_x[s_idx]
[…]

### 2022-01-11 code/rigid_fluid_coupling.py

@@ -769,8 +769,6 @@ class RigidFluidCouplingScheme(Scheme):
                         g5.append(RigidBodyBuiRigidRigid(dest=name, sources=self.boundaries,
                                                          en=self.en))
 
-
-
             # add the force due to fluid
             if len(self.fluids) > 0:
                 for name in self.rigid_bodies:

### 2022-02-22 manuscript/paper.tex
New rigid body collision case example from Amaro Junior 2019

--- 2021-07-10 manuscript/paper.tex
@@
 
-  \title{Write title here}
+  \title{Rigid fluid coupling}
   \author[IITB]{Adepu Dinesh \corref{cor1}}
@@
 
-\section{Fluid mechanics}
+\section{Governing equations}
 \label{sec:fluid-mechanics}
 
+\section{CTVF formulation}
+\label{sec:ctvf-equations}
+
+\section{SPH discretization}
+\label{sec:sph-fluid-equations}
+
 \section{Rigid body dynamics}
-\label{sec:rbd-dynamics}
+\label{sec:rbd}
 
-\section{Rigid body contact model}
-\label{sec:rbd-contact-model}
+\section{How to handle rigid fluid coupling}
+\label{sec:rfc}
 
-In the SPH literature there are a few ways to model the contact
-between rigid bodies. Few ways to note are
+\section{Collision between rigid bodies}
+\label{sec:contact-force}
 
-\begin{itemize}
-\item \citet{albano2016modelling} models using pure elastic impingement force
-% Development of the Resolved Fluid-Solid SPH Coupling using Rigid Body Dynamics
-\item \citet{choidevelopment} models using DEM
-\item \citet{zhan2020sph} uses hybrid contact model
-\item \citet{} uses hybrid contact model
-\end{itemize}
-A  SPH  framework  for  dynamic interaction  between  soil  and  rigid  body  system  with  hybrid contact   metho
+\citet{chen2019coupled} has damping model. Also he mentioned the parameters
+required in stack of cylinders example.
 
-\section{Rigid fluid coupling}
-\label{sec:rf-coupling}
+% \todoin{
+% \begin{itemize}
+% \item \citet{albano2016modelling} models using pure elastic impingement force
+% % Development of the Resolved Fluid-Solid SPH Coupling using Rigid Body Dynamics
+% \item \citet{choidevelopment} models using DEM
+% \item \citet{zhan2020sph} uses hybrid contact model
+% \end{itemize}
+% A SPH framework for dynamic interaction between soil and rigid body system
+% with hybrid contact method}
 
@@
 \label{sec:results}
-\citet{wu2014two} has experimental solution to cube sinking and cube floating
-in a tank.
 
-\subsection{Cylinders collapsing under gravity in a tank}
-\label{sec:cylinders-collapsing-dem}
+\subsection{Rigid block of different densities allowed to sink into water}
+\label{sec:rigid-block-diff}
 
-This benchmark is taken from \citet{chen2019coupled} and
-\citet{wang2019numerical}. This is to validate the rigid contact model.
+\subsection{A 2d and 3d rigid body sliding}
+\label{sec:rigid-body-sliding}
 
-Six layers of solid cylinders are stacked, and then suddenly released under
-gravity. This is done by 2009 Zhang and Canelas 2016.
+\subsection{Bouncing cube on a wall under gravity}
+\label{sec:bouncing-cube}
 
-\subsection{A block of density 2000 freely falling in to a steady tank}
-\label{sec:2000-density-inside-tank}
+\subsection{Stack of cylinders}
+\label{sec:stack-of-cylinders}
 
-This benchmark is taken from \citet{qiu20173d}.
+\subsection{A test to check the conservation properties of rigid body}
+\label{sec:conservation-of-rb-properties}
 
-A water tank of 150 $mm$ $\times$ 140 $mm$ $\times$ 140 $mm$ and the water
-depth in the tank was 131 $mm$. The cube with a side length of 20 $mm$. The
-density of the cube is 2120 $kg m^{-3}$. The cube is placed half way before
-the release into the fluid. The spring stiffness coefficient of 1 $\times$
-$10^{5}$ $N m^{-1}$.
+\subsection{Debris dam break flow}
+\label{sec:debris-dam-break-canelas}
 
-\subsection{A block of density $800.52$ floating in a steady tank}
-\label{sec:800-density-floating}
+\subsubsection{Case I}
+\label{sec:debris-dam-break-canelas-case-I}
 
-This benchmark is taken from \citet{qiu20173d}, \citet{wang2019numerical}.
+\subsubsection{Case II}
+\label{sec:debris-dam-break-canelas-case-II}
 
-A water tank of 150 mm $\times$ 140 mm $\times$ 140 mm and the water depth in
-the tank was 52 $mm$. A rectangular wooden block (with a width of 48 mm,
-length of 49 mm, height 24mm) whose density is 800.52 kg$m^{-1}$ is
-released from the bottom of the tank. We compare the vertical displacement of
-the center of mass of the cube.
+\subsubsection{Case III}
+\label{sec:debris-dam-break-canelas-case-III}
 
@@
 
-This benchmark is taken from \citet{wang2019numerical}.
+\citet{wang2019numerical}
 
-Here we simulate a solid body transport in a dam break.
-
-\subsection{Dam break with multiple body transport}
-\label{sec:dam-break-with-multiple-body-transport}
-
-This benchmark is taken from \citet{wang2019numerical}.
-
-Here we simulate a transport of multiple bodies in a dam break.
+\subsection{Dam break with multiple bodies transport}
+\label{sec:dam-break-with-multiple-bodies-transport}
+\citet{wang2019numerical}
 
 \subsection{Cylinders in water collapsed under gravity}
-\label{sec:cylinders-in-water-collapsed-under-gravity}
-
-This benchmark is taken from \citet{chen2019coupled}.
-
-Here we simulate a collapse of cylinders submerged in a water under gravity.
-
-\subsection{Single cube transport in 3d dam break with out any obstructions}
-\label{sec:single-cube-transport-in-3d-dam-break-with-out-any-obstructions}
-
-This benchmark is taken from \citet{ji2019coupled}.
-
-A single body transport under 3d dam break. Here we don't have any
-obstructions. This is done in Canelas 2016 DCDEM paper. This is different from
-Amicarelli paper.
-
-\subsection{Three cube transport in 3d dam break with out any obstructions}
-\label{sec:three-cube-transport-in-3d-dam-break-with-out-any-obstructions}
-
-This benchmark is taken from \citet{ji2019coupled}.
-
-Three cubes transport under 3d dam break. Here we don't have any obstructions.
-This is done in Canelas 2016 DCDEM paper. This is different from Amicarelli
-paper.
+\label{sec:cylinders-collapse-in-water}
+\citet{chen2019coupled}
 

### 2022-02-22 code/amaro_2019_collision_between_three_rigid_cubes.py

@@ -1,0 +1,185 @@
+"""
+Amaro2019Improvement
+
+An improvement of rigid bodies contact for particle-based
+non-smooth walls modeling
+
+https://doi.org/10.1007/s40571-019-00233-4
+
+An implementation of collision of three rigid bodies.
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_body_3d import RigidBody3DScheme
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.01
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 3
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2 - spacing/2.
+        self.body_length = 0.2 - spacing/2.
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gy = 0.
+        self.dim = 2
+
+    def create_particles(self):
+        xb, yb = get_2d_block(dx=self.body_spacing,
+                              length=self.body_length,
+                              height=self.body_height)
+        self.body1_density = 1.5 / 0.2**2.
+        m = self.body1_density * self.body_spacing**self.dim
+        # left body
+        body1 = get_particle_array(name='body1',
+                                   x=xb,
+                                   y=yb,
+                                   h=self.body_h,
+                                   m=m,
[…]

### 2022-02-22 code/dam_break_flow_against_a_single_cube.py

@@ -1,0 +1,330 @@
+"""Taken from \cite{ji2019coupled}, this is inturn was done in
+\citet{canelas2016sph}.
+
+
+This case models a single cube in the centre of the flume, with a face directly
+aligned with the flow direction.
+"""
+
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_3d_block
+
+
+def get_fluid_tank_3d(xf, yf, zf, tank_length, tank_height, tank_layers,
+                      tank_spacing):
+    """
+    Given the fluid block and tank dimensions, return the tank geometry
+    here
+
+    tank_length: length in x direction
+    tank_height: length in z direction
+    """
+    # create the left wall
+    min_yf = min(yf)
+    max_yf = max(yf)
+
+    # width is in y direction
+    left_width = max_yf - min_yf
+
+    # create a tank layer on the left
+    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
+                                             length=(tank_layers - 1.)*tank_spacing,
+                                             height=left_width,
+                                             depth=tank_height)
+    # adjust the left wall of tank
+    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
+    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
+    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
+
+    # create a tank layer on the right
+    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
+                                                length=(tank_layers - 1.)*tank_spacing,
+                                                height=left_width,
+                                                depth=tank_height)
+    # adjust the left wall of tank
+    xt_right += tank_length - (np.max(xt_right) - np.min(xf))
+    yt_right += np.min(yf) - np.min(yt_right) + 0. * tank_spacing
[…]

### 2022-02-22 code/dam_break_flow_against_three_cubes.py

@@ -1,0 +1,400 @@
+"""Taken from \cite{ji2019coupled}, this is inturn was done in
+\citet{canelas2016sph}.
+
+
+This case models a single cube in the centre of the flume, with a face directly
+aligned with the flow direction.
+"""
+
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_3d_block
+
+
+def get_fluid_tank_3d(xf, yf, zf, tank_length, tank_height, tank_layers,
+                      tank_spacing):
+    """
+    Given the fluid block and tank dimensions, return the tank geometry
+    here
+
+    tank_length: length in x direction
+    tank_height: length in z direction
+    """
+    # create the left wall
+    min_yf = min(yf)
+    max_yf = max(yf)
+
+    # width is in y direction
+    left_width = max_yf - min_yf
+
+    # create a tank layer on the left
+    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
+                                             length=(tank_layers - 1.)*tank_spacing,
+                                             height=left_width,
+                                             depth=tank_height)
+    # adjust the left wall of tank
+    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
+    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
+    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
+
+    # create a tank layer on the right
+    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
+                                                length=(tank_layers - 1.)*tank_spacing,
+                                                height=left_width,
+                                                depth=tank_height)
+    # adjust the left wall of tank
+    xt_right += tank_length - (np.max(xt_right) - np.min(xf))
[…]

### 2022-02-22 code/rigid_body_common.py

@@ -216,23 +216,23 @@ def setup_damping_coefficient(body, rigid_bodies, boundaries=[]):
         for src in rigid_bodies:
             l1 = src.min_dem_id[0]
             l2 = src.max_dem_id[0] + 1
-            for j, k in zip(range(max(src.body_id)), range(l1, l2)):
-                print(j, k)
+            for j, k in zip(range(max(src.body_id)+1), range(l1, l2)):
                 t1 = body.total_mass[i] * src.total_mass[j]
                 t2 = body.total_mass[i] + src.total_mass[j]
                 m_star = t1 / t2
 
+                idx = i * body.total_no_bodies[0]
                 t1 = log(body.coeff_of_rest[idx+k])
                 t2 = t1**2. + M_PI**2.
                 tmp = (m_star / t2)**0.5
 
-                idx = i * body.total_no_bodies[0]
                 body.eta[idx+k] = -2. * t1 * tmp
 
         for src in boundaries:
-            dem_id = src.max_dem_id[0]
-            m_star = d_total_mass[d_idx]
-            t1 = log(e)
+            idx = i * body.total_no_bodies[0]
+            dem_id = src.dem_id[0]
+            m_star = body.total_mass[i]
+            t1 = log(body.coeff_of_rest[idx+dem_id])
             t2 = t1**2. + M_PI**2.
             tmp = (m_star / t2)**0.5
             eta = -2. * t1 * tmp
@@ -786,6 +786,7 @@ class ComputeContactForceDistanceAndClosestPoint(Equation):
              d_dem_id,
              s_dem_id,
              d_total_no_bodies,
+             d_dem_id_source,
              dt, t, WIJ, RIJ, XIJ):
         i, t1, t2, t3 = declare('int', 4)
 
@@ -794,12 +795,15 @@ class ComputeContactForceDistanceAndClosestPoint(Equation):
                 t1 = d_total_no_bodies[0] * d_idx
                 t2 = t1 + s_dem_id[s_idx]
 
+                d_dem_id_source[t2] = s_dem_id[s_idx]
+
                 tmp = d_m[d_idx] / (d_rho[d_idx]) * WIJ
                 tmp_1 = (d_contact_force_normal_x[t2] * XIJ[0] +
                          d_contact_force_normal_y[t2] * XIJ[1])
                 d_contact_force_dist_tmp[t2] += tmp_1 * tmp
 
                 d_contact_force_normal_wij[t2] += tmp
+
 
[…]

### 2022-02-22 code/test_setup_damping_coefficient.py

@@ -1,6 +1,9 @@
 from pysph.base.utils import get_particle_array
 from rigid_body_common import setup_damping_coefficient
 import numpy as np
+from math import sin, pi, log, pi
+
+M_PI = pi
 
 
 def create_particle_array(name, x, y, body_id, dem_id, total_mass, total_no_bodies):
@@ -14,13 +17,21 @@ def create_particle_array(name, x, y, body_id, dem_id, total_mass, total_no_bodi
     pa.add_constant('total_mass', total_mass)
 
     nb = int(np.max(pa.body_id) + 1)
+    # print("hereeee")
+    # print(nb)
     pa.add_constant('nb', nb)
-    pa.add_constant('eta', nb * pa.total_no_bodies[0])
+
+    eta = np.zeros(pa.nb[0]*pa.total_no_bodies[0] * 1,
+                   dtype=float)
+    pa.add_constant('eta', eta)
 
     return pa
 
 
 def test_single_rigid_body():
+    # =========================
+    # create the particle array
+    # =========================
     x = [1., 2.]
     body_id = np.ones_like(x, dtype=int) * 0
     dem_id = np.ones_like(x, dtype=int) * 0
@@ -29,11 +40,24 @@ def test_single_rigid_body():
                                dem_id=dem_id, total_mass=total_mass,
                                total_no_bodies=1, name="body1")
 
-    coeff_of_rest = np.ones(pa.nb[0]*pa.total_no_bodies[0],
-                            dtype=float)
+    coeff_of_rest = np.array([0.8])
     pa.add_constant('coeff_of_rest', coeff_of_rest)
+    # =========================
+    # create the particle array
+    # =========================
 
     setup_damping_coefficient(pa, [pa], boundaries=[])
+
+    # test the properties
+
+    t1 = 2. * 2.
+    t2 = 2. + 2.
+    m_star = t1 / t2
+    t1 = log(0.8)
+    t2 = t1**2. + M_PI**2.
+    tmp = (m_star / t2)**0.5
+    expected = -2. * t1 * tmp
+    np.testing.assert_array_almost_equal(pa.eta, [expected])
 
 
 def test_single_particle_array_with_2_rigid_bodies():
@@ -45,11 +69,50 @@ def test_single_particle_array_with_2_rigid_bodies():
                                dem_id=dem_id, total_mass=total_mass,
[…]

### 2022-03-08 manuscript/paper.tex
1st result, Mohseni sliding slope 2d done

@@
 
-\subsection{Rigid block of different densities allowed to sink into water}
-\label{sec:rigid-block-diff}
+\subsection{3D Bouncing cube on a wall under gravity}
+\label{sec:bouncing-cube}
+
+\subsubsection{A test to check the conservation properties of rigid body}
+\label{sec:conservation-of-rb-properties}
 
@@
 
-\subsection{Bouncing cube on a wall under gravity}
-\label{sec:bouncing-cube}
+\subsection{Controlled Sliding on a Flat Surface}
+\label{sec:controlled-rigid-body-sliding}
 
@@
 
-\subsection{A test to check the conservation properties of rigid body}
-\label{sec:conservation-of-rb-properties}
+\subsection{Rigid block of different densities allowed to sink into water}
+\label{sec:rigid-block-diff}
 
-\subsection{Debris dam break flow}
-\label{sec:debris-dam-break-canelas}
+\subsection{3D dam breaking flow hitting one cube}
+\label{sec:3d-dam-breaking-one-cube-hit}
 
-\subsubsection{Case I}
-\label{sec:debris-dam-break-canelas-case-I}
+\cite{amaro2019improvement}
 
-\subsubsection{Case II}
-\label{sec:debris-dam-break-canelas-case-II}
+\subsection{3D dam breaking flow hitting three cube}
+\label{sec:3d-dam-breaking-one-cube-hit}
 
-\subsubsection{Case III}
-\label{sec:debris-dam-break-canelas-case-III}
+\cite{amaro2019improvement}
 
-\subsection{Dam break with body transport}
-\label{sec:dam-break-with-body-transport}
+\subsection{3D dam breaking flow hitting pyramid cubes configuration}
+\label{sec:3d-dam-breaking-one-cube-hit}
 
-\citet{wang2019numerical}
+\cite{amaro2019improvement}
 
-\subsection{Dam break with multiple bodies transport}
-\label{sec:dam-break-with-multiple-bodies-transport}
-\citet{wang2019numerical}
+% \subsection{Dam break with body transport}
+% \label{sec:dam-break-with-body-transport}
 
-\subsection{Cylinders in water collapsed under gravity}
-\label{sec:cylinders-collapse-in-water}
-\citet{chen2019coupled}
+% \citet{wang2019numerical}
+
+% \subsection{Dam break with multiple bodies transport}
+% \label{sec:dam-break-with-multiple-bodies-transport}
+% \citet{wang2019numerical}
+
+% \subsection{Cylinders in water collapsed under gravity}
+% \label{sec:cylinders-collapse-in-water}
+% \citet{chen2019coupled}
 

### 2022-03-08 automate.py

@@ -428,14 +428,123 @@ class DamBreakWithMultipleBodiesTransport(Problem):
         self.make_output_dir()
 
 
+class Mohseni2021FreeSlidingOnASlope2D(Problem):
+    def get_name(self):
+        return 'mohseni_2021_free_sliding_on_a_slope_2d'
+
+    def setup(self):
+        get_path = self.input_path
+
+        cmd = 'python code/mohseni_2021_free_sliding_on_a_slope_2d.py' + backend
+
+        # Base case info
+        self.case_info = {
+            'fric_coeff_0_2': (dict(
+                scheme='rfc',
+                detail=None,
+                pfreq=300,
+                kr=1e5,
+                fric_coeff=0.2,
+                tf=3.,
+                ), r'$\mu=$0.2'),
+
+            'fric_coeff_0_4': (dict(
+                scheme='rfc',
+                detail=None,
+                pfreq=300,
+                kr=1e5,
+                fric_coeff=0.4,
+                tf=3.,
+                ), r'$\mu=$0.4'),
+
+            'fric_coeff_tan_30': (dict(
+                scheme='rfc',
+                detail=None,
+                pfreq=300,
+                kr=1e5,
+                fric_coeff=np.tan(np.pi/6),
+                tf=3.,
+                ), r'$\mu=$tan(30)'),
+
+            'fric_coeff_0.6': (dict(
+                scheme='rfc',
+                detail=None,
+                pfreq=300,
+                kr=1e5,
+                fric_coeff=0.6,
+                tf=3.,
+                ), r'$\mu=$0.6'),
+        }
+
+        self.cases = [
+            Simulation(get_path(name), cmd,
+                       job_info=dict(n_core=n_core,
+                                     n_thread=n_thread), cache_nnps=None,
+                       **scheme_opts(self.case_info[name][0]))
+            for name in self.case_info
+        ]
+
+    def run(self):
+        self.make_output_dir()
+        self.plot_velocity()
+        self.move_figures()
+
+    def plot_velocity(self):
+        data = {}
+        for name in self.case_info:
+            data[name] = np.load(self.input_path(name, 'results.npz'))
+
+        for name in self.case_info:
+            t_analytical = data[name]['t_analytical']
+            v_analytical = data[name]['v_analytical']
+
+            t = data[name]['t']
+            velocity_rbd = data[name]['velocity_rbd']
+
[…]

### 2022-03-08 code/mohseni_2021_free_sliding_on_a_slope_2d.py

@@ -1,0 +1,585 @@
+"""[1] Particle-Based Numerical Simulation Study of Solid Particle
+Erosion of Ductile Materials Leading to an Erosion Model,
+Including the Particle Shape Effect
+
+https://doi.org/10.3390/ma15010286
+
+
+3.3.2 Free sliding on a slope
+
+"""
+from __future__ import print_function
+import numpy as np
+
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from pysph.base.utils import (get_particle_array)
+
+# from rigid_body_3d import RigidBody3DScheme
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from pysph.sph.equation import Equation, Group
+import os
+
+from pysph.tools.geometry import get_2d_block, get_2d_tank, rotate
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+def create_circle(diameter=1, spacing=0.05, center=None):
+    radius = diameter/2.
+    xtmp, ytmp = get_2d_block(spacing, diameter+spacing, diameter+spacing)
+    x = []
+    y = []
+    for i in range(len(xtmp)):
+        dist = xtmp[i]**2. + ytmp[i]**2.
+        if dist < radius**2:
+            x.append(xtmp[i])
+            y.append(ytmp[i])
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
[…]

### 2022-03-08 code/rigid_fluid_coupling.py

@@ -31,17 +31,16 @@ from pysph.sph.integrator_step import IntegratorStep
 from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
                                 WendlandQuinticC4, Gaussian, SuperGaussian)
 
-from rigid_body_common import (set_total_mass, set_center_of_mass,
+from rigid_body_common import (add_properties_stride,
+                               set_total_mass, set_center_of_mass,
                                set_body_frame_position_vectors,
                                set_body_frame_normal_vectors,
                                set_moment_of_inertia_and_its_inverse,
                                BodyForce, SumUpExternalForces,
-                               normalize_R_orientation, RigidBodyLVC,
-                               RigidBodyCanelasRigidRigid,
-                               RigidBodyCanelasRigidWall,
-                               RigidBodyBuiRigidRigid)
-
-from dem import UpdateTangentialContactsLVCDisplacement, UpdateTangentialContactsLVCForce
+                               normalize_R_orientation,
+                               ComputeContactForceNormals,
+                               ComputeContactForceDistanceAndClosestPoint,
+                               ComputeContactForce)
 
 # compute the boundary particles
 from boundary_particles import (get_boundary_identification_etvf_equations,
@@ -555,11 +554,9 @@ class EDACEquationFSI(Equation):
 
 class RigidFluidCouplingScheme(Scheme):
     def __init__(self, fluids, boundaries, rigid_bodies, dim, rho0, p0, c0, h,
-                 nu, kn=1e7, en=0.5, Cn=1.4*1e-5, gamma=7.0, integrator="rk2",
-                 dem="bui", gx=0.0, gy=0.0, gz=0.0, alpha=0.1, beta=0.0,
+                 nu, kr=1e5, kf=1e5, en=0.5, fric_coeff=0.5, gamma=7.0,
+                 gx=0.0, gy=0.0, gz=0.0, alpha=0.1, beta=0.0,
                  kernel_choice="1", kernel_factor=3, edac_alpha=0.5):
-        self.rigid_bodies = rigid_bodies
-
         if boundaries is None:
             self.boundaries = []
         else:
@@ -581,17 +578,9 @@ class RigidFluidCouplingScheme(Scheme):
         self.art_nu = 0.
         self.nu = nu
 
-        # rigid body parameters
-        self.kn = kn
-        self.en = en
-        self.Cn = Cn
-
         self.dim = dim
 
[…]

### 2022-03-20 manuscript/paper.tex
2D RFC and solid-solid interaction validated.

@@
 
+In the current section we test the frictional part of the current solver by
+modeling the sliding of a rigid body on an inclined surface in 3D. We compare
+against the analytical solution to validate the test case.
+
+We consider a rigid body of length 0.1 m, height 0.1 and depth of 0.1m allowed
+to slide on an inclined surface at an angle $\frac{\pi}{3}$. A density of 2000
+kg\,m\textsuperscript{-3} is used for the body. Other numerical parameters,
+such as the repulsive spring stiffness $k_r=3.0 \times 10^{5}$ and tangential
+spring stiffness $k_t=3.0 \times 10^{5}$ is chosen, respectively. A particle
+spacing of $0.001$ is considered, resulting in $4400$ particles per body. From
+the analytical solution, the evolution of velocity is given by,
+\begin{equation}
+  \label{eq:ce}
+  \ten{v}(t) = (\mu \teng{g} \sin (\theta) - \teng{g} \cos (\theta)) t.
+\end{equation}
+
+We consider three different friction coefficients, $\mu=0.5$, $\mu=0.5$, and
+$\mu=0.5$. From the analytical solution, when the friction coefficient is
+greater than $\tan(frac{\pi}{3})$, the body doesn't slide.
+
+\Cref{fig:dinesh-2022-bouncing-cube-snapshots-3d} depicts the snapshots of the
+rigid body bouncing on a wall. The coefficient of restitution corresponding to
+the snapshots are equal to $1$. As the rigid body approaches the wall, its
+velocity is increases due to gravity. As soon as the body comes into contact
+of the wall, the collision happens, the body's velocity is reduced until it
+becomes zero, and then it rebounds, and bounces back to a certain height.
+
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time0}
+    \subcaption{t = 2.5e-03 sec}\label{fig:passing-0}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time1}
+    \subcaption{t = 2.5e-03 sec}\label{fig:passing-1}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time2}
+    \subcaption{t = 2.5e-03 sec}\label{fig:passing-2}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time3}
+    \subcaption{t = 2.5e-03 sec}\label{fig:passing-3}
+  \end{subfigure}
+  \caption{Elastic solid sliding}
+\label{fig:mohseni-2021-sliding-3d}
+\end{figure}
+%
+
+\Cref{fig:results-solid-sliding-velocity-vs-time} shows a evolution of
+velocity of the center of mass of the rigid body for different frictional
+coefficients against the analytical solution. From
+\Cref{fig:results-solid-sliding-velocity-vs-time} we can see that the current
+solver has an excellent match with the analytical solution and covers all the
+regimes of the sliding case.
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Velocity versus time}
+\label{fig:results-solid-sliding-velocity-vs-time}
+\end{figure}
+
 \subsubsection{A test to check the conservation properties of rigid body}
@@
 \label{sec:rigid-body-sliding}
+
+In the current section we test the frictional part of the current solver by
+modeling the sliding of a rigid body on an inclined surface in 3D. We compare
+against the analytical solution to validate the test case.
+
+We consider a rigid body of length 0.1 m, height 0.1 and depth of 0.1m allowed
+to slide on an inclined surface at an angle $\frac{\pi}{3}$. A density of 2000
+kg\,m\textsuperscript{-3} is used for the body. Other numerical parameters,
+such as the repulsive spring stiffness $k_r=3.0 \times 10^{5}$ and tangential
+spring stiffness $k_t=3.0 \times 10^{5}$ is chosen, respectively. A particle
+spacing of $0.001$ is considered, resulting in $4400$ particles per body. From
+the analytical solution, the evolution of velocity is given by,
+\begin{equation}
+  \label{eq:ce}
+  \ten{v}(t) = (\mu \teng{g} \sin (\theta) - \teng{g} \cos (\theta)) t.
+\end{equation}
+
+We consider three different friction coefficients, $\mu=0.5$, $\mu=0.5$, and
+$\mu=0.5$. From the analytical solution, when the friction coefficient is
+greater than $\tan(frac{\pi}{3})$, the body doesn't slide.
+
+\Cref{fig:mohseni-2021-sliding-3d} shows the snapshots of the rigid body at 4
+time instants. From \cref{fig:mohseni-2021-sliding-3d} we can see that the the
+body is freely sliding with out having any oscillations or unphysical jumping
+off the inclined wall. This is because of the new surface aware contact model
+as force is not computed by considering the wall as spherical particles but by
+ensemble of an overlap. The snapshots correspond to a friction coefficient of $0.4$.
+
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time0}
+    \subcaption{t = 2.5e-03 sec}\label{fig:passing-0}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time1}
+    \subcaption{t = 2.5e-03 sec}\label{fig:passing-1}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time2}
+    \subcaption{t = 2.5e-03 sec}\label{fig:passing-2}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time3}
+    \subcaption{t = 2.5e-03 sec}\label{fig:passing-3}
+  \end{subfigure}
+  \caption{Elastic solid sliding}
+\label{fig:mohseni-2021-sliding-3d}
+\end{figure}
+%
+
+\Cref{fig:results-solid-sliding-velocity-vs-time} shows a evolution of
+velocity of the center of mass of the rigid body for different frictional
+coefficients against the analytical solution. From
+\Cref{fig:results-solid-sliding-velocity-vs-time} we can see that the current
+solver has an excellent match with the analytical solution and covers all the
+regimes of the sliding case.
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Velocity versus time}
+\label{fig:results-solid-sliding-velocity-vs-time}
+\end{figure}
 
@@
 
-\subsection{Rigid block of different densities allowed to sink into water}
-\label{sec:rigid-block-diff}
+\subsection{Falling solid in water}
+\label{sec:falling-solid-in-water}
+
+\subsection{Floating solid in water}
+\label{sec:floating-solid-in-water}
 

### 2022-03-20 automate.py

@@ -441,7 +441,6 @@ class Mohseni2021FreeSlidingOnASlope2D(Problem):
         self.case_info = {
             'fric_coeff_0_2': (dict(
                 scheme='rfc',
-                detail=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=0.2,
@@ -450,7 +449,6 @@ class Mohseni2021FreeSlidingOnASlope2D(Problem):
 
             'fric_coeff_0_4': (dict(
                 scheme='rfc',
-                detail=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=0.4,
@@ -459,7 +457,6 @@ class Mohseni2021FreeSlidingOnASlope2D(Problem):
 
             'fric_coeff_tan_30': (dict(
                 scheme='rfc',
-                detail=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=np.tan(np.pi/6),
@@ -468,7 +465,6 @@ class Mohseni2021FreeSlidingOnASlope2D(Problem):
 
             'fric_coeff_0.6': (dict(
                 scheme='rfc',
-                detail=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=0.6,
@@ -545,7 +541,6 @@ class Mohseni2021FreeSlidingOnASlope3D(Problem):
         self.case_info = {
             'fric_coeff_0_2': (dict(
                 scheme='rfc',
-                detail=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=0.2,
@@ -554,7 +549,6 @@ class Mohseni2021FreeSlidingOnASlope3D(Problem):
 
             'fric_coeff_0_4': (dict(
                 scheme='rfc',
-                detail=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=0.4,
@@ -563,7 +557,6 @@ class Mohseni2021FreeSlidingOnASlope3D(Problem):
 
             'fric_coeff_tan_30': (dict(
                 scheme='rfc',
-                detail=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=np.tan(np.pi/6),
@@ -572,7 +565,6 @@ class Mohseni2021FreeSlidingOnASlope3D(Problem):
 
             'fric_coeff_0.6': (dict(
                 scheme='rfc',
-                detail=None,
                 pfreq=300,
                 kr=1e5,
[…]

### 2022-03-20 code/2000_density_cube_drowning_3d.py

@@ -1,360 +1,0 @@
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_3d_block
-
-
-def get_fluid_tank_3d(xf, yf, zf, tank_height, tank_layers,
-                      tank_spacing):
-    """
-    Given the fluid block and tank dimensions, return the tank geometry
-    here
-
-    tank_length: length in x direction
-    tank_height: length in z direction
-    """
-    # create the left wall
-    min_yf = min(yf)
-    max_yf = max(yf)
-
-    # width is in y direction
-    left_width = max_yf - min_yf
-
-    # create a tank layer on the left
-    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
-                                             length=(tank_layers - 1.)*tank_spacing,
-                                             height=left_width,
-                                             depth=tank_height)
-    # adjust the left wall of tank
-    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
-    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
-    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
-
-    # create a tank layer on the right
-    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
-                                                length=(tank_layers - 1.)*tank_spacing,
-                                                height=left_width,
-                                                depth=tank_height)
-    # adjust the left wall of tank
-    xt_right += (np.max(xt_right) - np.min(xf)) + 1. * tank_spacing
-    yt_right += np.min(yf) - np.min(yt_right) + 0. * tank_spacing
-    zt_right += np.min(zf) - np.min(zt_right) + 0. * tank_spacing
-
-    # create the wall in the front
-    xt_front, yt_front, zt_front = get_3d_block(
-        dx=tank_spacing,
[…]

### 2022-03-20 code/2d_wedge_entry.py

@@ -1,475 +1,0 @@
-"""Numerical simulation of interactions between free surface and rigid body
-using a robust SPH method, Pengnan Sun, 2015
-
-3.1.3 Water entry of 2-D cylinder
-
-"""
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-from pysph.sph.scheme import add_bool_argument
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_2d_block
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
-from pysph.sph.equation import Equation, Group
-from nrbc import ShepardInterpolateCharacteristics, EvaluatePropertyfromCharacteristics, EvaluateCharacterisctics
-
-
-def create_circle_1(diameter=1, spacing=0.05, center=None):
-    dx = spacing
-    x = [0.0]
-    y = [0.0]
-    r = spacing
-    nt = 0
-    radius = diameter / 2.
-
-    tmp_dist = radius - spacing/2.
-    i = 0
-    while tmp_dist > spacing/2.:
-        perimeter = 2. * np.pi * tmp_dist
-        no_of_points = int(perimeter / spacing) + 1
-        theta = np.linspace(0., 2. * np.pi, no_of_points)
-        for t in theta[:-1]:
-            x.append(tmp_dist * np.cos(t))
-            y.append(tmp_dist * np.sin(t))
-        i = i + 1
-        tmp_dist = radius - spacing/2. - i * spacing
-
-    x = np.array(x)
-    y = np.array(y)
-    x, y = (t.ravel() for t in (x, y))
-    if center is None:
-        return x, y
-    else:
-        return x + center[0], y + center[1]
-
-
-class SpongeLayerDamping(Equation):
-    def __init__(self, dest, sources, sponge_width):
-        self.sponge_width = sponge_width
-
-        super(SpongeLayerDamping, self).__init__(dest, sources)
-
[…]

### 2022-03-20 code/amaro_2019_dam_breaking_flow_hitting_one_cube_3d.py

@@ -1,0 +1,243 @@
+"""
+
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from geometry import hydrostatic_tank_2d, get_fluid_tank_3d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_3d_block
+
+
+class Amaro2019DamBreakingFlowHittingOneCube3d(Application):
+    def initialize(self):
+        spacing = 0.05
+        self.hdx = 1.3
+
+        # these dimensions are as per the paper Amaro
+
+        # assuming x-axis as length
+        self.fluid_length = 4.5
+        # assuming y-axis as depth
+        self.fluid_depth = 0.7
+        # assuming z-axis as height
+        self.fluid_height = 0.4
+
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 0.7
+        self.tank_length = 8.
+        self.tank_layers = 3
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_depth = 0.2
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gx = 0.
+        self.gy = -9.81
+        self.gz = 0.
+        self.dim = 3
+
+    def create_one_cube(self):
+        xb, yb, zb = get_3d_block(dx=self.body_spacing,
+                                  length=self.body_length,
+                                  height=self.body_height,
+                                  depth=self.body_depth)
+
+        body_id = np.zeros(len(xb), dtype=int)
[…]

### 2022-03-20 code/amaro_2019_dam_breaking_flow_hitting_six_stacked_cubes_3d.py

@@ -1,0 +1,301 @@
+"""
+
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from geometry import hydrostatic_tank_2d, get_fluid_tank_3d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_3d_block
+
+
+class Amaro2019DamBreakingFlowHittingSixStackedCubes3d(Application):
+    def initialize(self):
+        spacing = 0.05
+        self.hdx = 1.3
+
+        # these dimensions are as per the paper Amaro
+
+        # assuming x-axis as length
+        self.fluid_length = 4.5
+        # assuming y-axis as depth
+        self.fluid_depth = 0.7
+        # assuming z-axis as height
+        self.fluid_height = 0.4
+
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 0.7
+        self.tank_length = 8.
+        self.tank_layers = 3
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_depth = 0.2
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gx = 0.
+        self.gy = -9.81
+        self.gz = 0.
+        self.dim = 3
+
+    def create_six_cubes(self):
+        xb1, yb1, zb1 = get_3d_block(dx=self.body_spacing,
+                                length=self.body_length,
+                                height=self.body_height,
+                                depth=self.body_depth)
+
+
[…]

### 2022-03-20 code/amaro_2019_dam_breaking_flow_hitting_three_stacked_cubes_3d.py

@@ -1,0 +1,266 @@
+"""
+
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from geometry import hydrostatic_tank_2d, get_fluid_tank_3d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_3d_block
+
+
+class Amaro2019DamBreakingFlowHittingOneCube3d(Application):
+    def initialize(self):
+        spacing = 0.05
+        self.hdx = 1.3
+
+        # these dimensions are as per the paper Amaro
+
+        # assuming x-axis as length
+        self.fluid_length = 4.5
+        # assuming y-axis as depth
+        self.fluid_depth = 0.7
+        # assuming z-axis as height
+        self.fluid_height = 0.4
+
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 0.7
+        self.tank_length = 8.
+        self.tank_layers = 3
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_depth = 0.2
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gx = 0.
+        self.gy = -9.81
+        self.gz = 0.
+        self.dim = 3
+
+    def create_three_cubes(self):
+        xb1, yb1, zb1 = get_3d_block(dx=self.body_spacing,
+                                length=self.body_length,
+                                height=self.body_height,
+                                depth=self.body_depth)
+
+
[…]

### 2022-03-20 code/bouncing_ball_rigid_body.py

@@ -1,138 +1,0 @@
-"""A ball bouncing on a wall
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-
-
-class Case0(Application):
-    def initialize(self):
-        self.rho0 = 10.0
-        self.hdx = 1.3
-        self.dx = 0.02
-        self.dy = 0.02
-        self.kn = 1e4
-        self.mu = 0.5
-        self.en = 1.0
-        self.dim = 2
-
-        self.dt = 1e-3
-        self.tf = 10
-
-    def create_scheme(self):
-        rfc = RigidFluidCouplingScheme(rigid_bodies=['body'],
-                                       fluids=[],
-                                       boundaries=[],
-                                       dim=2,
-                                       rho0=1000,
-                                       p0=1000000,
-                                       c0=100,
-                                       gy=0.)
-        s = SchemeChooser(default='rfc', rfc=rfc)
-        return s
-
-    def configure_scheme(self):
-        dt = self.dt
-        tf = self.tf
-        self.scheme.configure_solver(dt=dt, tf=tf, pfreq=100)
-
-    def create_particles(self):
-        nx, ny = 10, 10
-        dx = self.dx
-        x, y = np.mgrid[0:1:nx * 1j, 0:1:ny * 1j]
-        x = x.flat
-        y = y.flat
-        m = np.ones_like(x) * dx * dx * self.rho0
-        h = np.ones_like(x) * self.hdx * dx
-        # radius of each sphere constituting in cube
-        rad_s = np.ones_like(x) * dx
-        body = get_particle_array(name='body', x=x, y=y, h=h, m=m, rad_s=rad_s,
-                                  constants={
-                                      'E': 69 * 1e9,
-                                      'n': 4,
-                                      'poisson_ratio': 0.3,
-                                      'spacing0': self.dx_plate,
-                                      'rho_ref': self.plate_rho0
-                                  })
[…]

### 2022-03-20 code/dam_break_flow_against_a_single_cube.py

@@ -1,330 +1,0 @@
-"""Taken from \cite{ji2019coupled}, this is inturn was done in
-\citet{canelas2016sph}.
-
-
-This case models a single cube in the centre of the flume, with a face directly
-aligned with the flow direction.
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_3d_block
-
-
-def get_fluid_tank_3d(xf, yf, zf, tank_length, tank_height, tank_layers,
-                      tank_spacing):
-    """
-    Given the fluid block and tank dimensions, return the tank geometry
-    here
-
-    tank_length: length in x direction
-    tank_height: length in z direction
-    """
-    # create the left wall
-    min_yf = min(yf)
-    max_yf = max(yf)
-
-    # width is in y direction
-    left_width = max_yf - min_yf
-
-    # create a tank layer on the left
-    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
-                                             length=(tank_layers - 1.)*tank_spacing,
-                                             height=left_width,
-                                             depth=tank_height)
-    # adjust the left wall of tank
-    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
-    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
-    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
-
-    # create a tank layer on the right
-    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
-                                                length=(tank_layers - 1.)*tank_spacing,
-                                                height=left_width,
-                                                depth=tank_height)
-    # adjust the left wall of tank
-    xt_right += tank_length - (np.max(xt_right) - np.min(xf))
-    yt_right += np.min(yf) - np.min(yt_right) + 0. * tank_spacing
[…]

### 2022-03-20 code/dam_break_flow_against_three_cubes.py

@@ -1,400 +1,0 @@
-"""Taken from \cite{ji2019coupled}, this is inturn was done in
-\citet{canelas2016sph}.
-
-
-This case models a single cube in the centre of the flume, with a face directly
-aligned with the flow direction.
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_3d_block
-
-
-def get_fluid_tank_3d(xf, yf, zf, tank_length, tank_height, tank_layers,
-                      tank_spacing):
-    """
-    Given the fluid block and tank dimensions, return the tank geometry
-    here
-
-    tank_length: length in x direction
-    tank_height: length in z direction
-    """
-    # create the left wall
-    min_yf = min(yf)
-    max_yf = max(yf)
-
-    # width is in y direction
-    left_width = max_yf - min_yf
-
-    # create a tank layer on the left
-    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
-                                             length=(tank_layers - 1.)*tank_spacing,
-                                             height=left_width,
-                                             depth=tank_height)
-    # adjust the left wall of tank
-    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
-    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
-    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
-
-    # create a tank layer on the right
-    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
-                                                length=(tank_layers - 1.)*tank_spacing,
-                                                height=left_width,
-                                                depth=tank_height)
-    # adjust the left wall of tank
-    xt_right += tank_length - (np.max(xt_right) - np.min(xf))
[…]

### 2022-03-20 code/dinesh_2022_hydrostatic_tank_2d.py

@@ -1,0 +1,153 @@
+"""[1] A 3D simulation of a moving solid in viscous free-surface flows by
+coupling SPH and DEM
+
+3.2 Falling solid in water.
+
+"""
+from __future__ import print_function
+import numpy as np
+
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from pysph.base.utils import (get_particle_array)
+
+# from rigid_body_3d import RigidBody3DScheme
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from pysph.sph.equation import Equation, Group
+import os
+from pysph.tools import geometry as G
+
+from pysph.tools.geometry import get_2d_block, get_2d_tank, rotate
+from geometry import hydrostatic_tank_2d
+
+
+class Dinesh2022HydrostaticTank2D(Application):
+    def initialize(self):
+        self.dim = 2
+        spacing = 2. * 1e-3
+        self.hdx = 1.0
+
+        # the fluid dimensions are
+        # x-dimension (this is in the plane of the paper going right)
+        self.fluid_length = 150. * 1e-3
+        # y-dimension (this goes into the paper)
+        self.fluid_height = 131 * 1e-3
+
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_length = 150. * 1e-3
+        self.tank_height = 140 * 1e-3
+        self.tank_spacing = spacing
+        self.tank_layers = 3
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        # fixme: why is it blowing up with higher alpha
+        self.alpha = 0.5
+        self.gx = 0.
+        self.gy = -9.81
+        self.gz = 0.
+        self.dim = 2
+
+        # solver data
+        self.tf = 0.5
+        self.dt = 0.25 * self.fluid_spacing * self.hdx / (self.c0 * 1.1)
+
+        # Rigid body collision related data
+        self.limit = 6
+        self.seval = None
+
+    def add_user_options(self, group):
+        group.add_argument("--dx",
+                           action="store",
+                           type=float,
+                           dest="dx",
+                           default=5. * 1e-3,
[…]

### 2022-03-20 code/dinesh_2022_multiple_cubes_colliding.py

@@ -1,11 +1,4 @@
-"""[1] Particle-Based Numerical Simulation Study of Solid Particle
-Erosion of Ductile Materials Leading to an Erosion Model,
-Including the Particle Shape Effect
-
-https://doi.org/10.3390/ma15010286
-
-
-3.3.2 Free sliding on a slope
+"""Multiple cubes colliding
 
 """
 from __future__ import print_function
@@ -21,7 +14,7 @@ from rigid_fluid_coupling import RigidFluidCouplingScheme
 from pysph.sph.equation import Equation, Group
 import os
 
-from pysph.tools.geometry import get_2d_block, get_2d_tank, rotate
+from pysph.tools.geometry import get_3d_block, get_2d_tank, rotate
 
 
 def create_circle_1(diameter=1, spacing=0.05, center=None):
@@ -108,164 +101,159 @@ def get_contact_force_is_boundary(x, y, spacing):
     return contact_force_is_boundary
 
 
-def setup_properties_for_gradual_force(pa):
-    pa.add_constant('normal_force_time', 0.)
-    pa.add_constant('tmp_normal_force', 0.)
-    pa.add_constant('delta_fn', 0.)
-
-    pa.add_constant('tangential_force_time', 0.)
-    pa.add_constant('tmp_tangential_force', 0.)
-    pa.add_constant('delta_ft', 0.)
-
-    force_idx_fn = np.zeros_like(pa.x)
-    force_idx_ft = np.zeros_like(pa.x)
-    pa.add_property('force_idx_fn', type='int', data=force_idx_fn)
-    pa.add_property('force_idx_ft', type='int', data=force_idx_ft)
-
-
-def force_index_single(body):
-    max_y = np.max(body.y)
-
-    indices_fn = np.where(max_y == body.y)[0]
-    body.force_idx_fn[indices_fn] = 1
-
-    min_x = np.min(body.x)
-    indices_ft = np.where(min_x == body.x)[0]
-    body.force_idx_ft[indices_ft] = 1
-
-
-class ApplyForceOnRigidBody(Equation):
-    def initialize(self, d_idx,
-                   d_m,
-                   d_fx,
-                   d_fy,
-                   d_fz,
-                   d_normal_force_time,
-                   d_tmp_normal_force,
-                   d_delta_fn,
-                   d_force_idx_fn,
-                   d_tangential_force_time,
-                   d_tmp_tangential_force,
-                   d_delta_ft,
[…]

### 2022-03-20 code/dinesh_2022_steady_cubes_on_a_wall_2d.py

@@ -1,0 +1,342 @@
+"""
+Test the collision of two rigid bodues made of same particle array
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class Dinesh2022SteadyCubesOnAWall2D(Application):
+    def initialize(self):
+        spacing = 0.05
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 5
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gx = 0.
+        self.gy = -9.81
+        self.gz = 0.
+        self.dim = 2
+
+    def add_user_options(self, group):
+        from pysph.sph.scheme import add_bool_argument
+        add_bool_argument(group, 'two-cubes', dest='use_two_cubes',
+                          default=False, help='Use two cubes')
+
+        add_bool_argument(group, 'three-cubes', dest='use_three_cubes',
+                          default=False, help='Use three cubes')
+
+        add_bool_argument(group, 'pyramid-cubes', dest='use_pyramid_cubes',
[…]

### 2022-03-20 code/mohseni_2021_free_sliding_on_a_slope_3d.py

@@ -419,7 +419,7 @@ class Mohseni2021FreeSlidingOnASlope(Application):
                                        c0=10.,
                                        gy=self.gy,
                                        nu=0.,
-                                       h=None)
+                                       h=self.h)
 
         s = SchemeChooser(default='rfc', rfc=rfc)
         return s

### 2022-03-20 code/qiu_2017_falling_solid_in_water_3d.py

@@ -1,0 +1,381 @@
+"""[1] A 3D simulation of a moving solid in viscous free-surface flows by
+coupling SPH and DEM
+
+3.2 Falling solid in water.
+
+"""
+from __future__ import print_function
+import numpy as np
+
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from pysph.base.utils import (get_particle_array)
+
+# from rigid_body_3d import RigidBody3DScheme
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from pysph.sph.equation import Equation, Group
+import os
+from pysph.tools import geometry as G
+
+from pysph.tools.geometry import get_3d_block, get_2d_tank, rotate
+from geometry import get_fluid_tank_3d
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+def create_circle(diameter=1, spacing=0.05, center=None):
+    radius = diameter/2.
+    xtmp, ytmp = get_2d_block(spacing, diameter+spacing, diameter+spacing)
+    x = []
+    y = []
+    for i in range(len(xtmp)):
+        dist = xtmp[i]**2. + ytmp[i]**2.
+        if dist < radius**2:
+            x.append(xtmp[i])
+            y.append(ytmp[i])
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+def get_contact_force_is_boundary(x, y, spacing):
[…]

### 2022-03-20 code/qiu_2017_floating_solid_in_water_2d.py

@@ -1,11 +1,12 @@
-"""[1] Particle-Based Numerical Simulation Study of Solid Particle
-Erosion of Ductile Materials Leading to an Erosion Model,
-Including the Particle Shape Effect
+"""[1] A 3D simulation of a moving solid in viscous free-surface flows by
+coupling SPH and DEM
 
-https://doi.org/10.3390/ma15010286
+[2] Numerical modeling of floating bodies transport for flooding analysis in
+nuclear reactor building
 
+[3] A two-way coupled simulation of moving solids in free-surface flows
 
-3.3.2 Free sliding on a slope
+[1] 3.3 Floating solid in water.
 
 """
 from __future__ import print_function
@@ -20,8 +21,10 @@ from pysph.base.utils import (get_particle_array)
 from rigid_fluid_coupling import RigidFluidCouplingScheme
 from pysph.sph.equation import Equation, Group
 import os
+from pysph.tools import geometry as G
 
 from pysph.tools.geometry import get_2d_block, get_2d_tank, rotate
+from geometry import hydrostatic_tank_2d
 
 
 def create_circle_1(diameter=1, spacing=0.05, center=None):
@@ -73,27 +76,6 @@ def create_circle(diameter=1, spacing=0.05, center=None):
         return x + center[0], y + center[1]
 
 
-def hydrostatic_tank_2d(fluid_length, fluid_height, tank_height, tank_layers,
-                        fluid_spacing, tank_spacing):
-    xt, yt = get_2d_tank(dx=tank_spacing,
-                         length=fluid_length + 2. * tank_spacing,
-                         height=tank_height,
-                         num_layers=tank_layers)
-    xf, yf = get_2d_block(dx=fluid_spacing,
-                          length=fluid_length,
-                          height=fluid_height,
-                          center=[-1.5, 1])
-
-    xf += (np.min(xt) - np.min(xf))
-    yf -= (np.min(yf) - np.min(yt))
-
-    # now adjust inside the tank
-    xf += tank_spacing * (tank_layers)
-    yf += tank_spacing * (tank_layers)
-
-    return xf, yf, xt, yt
-
-
 def get_contact_force_is_boundary(x, y, spacing):
     """To understand this snipped please comment few lines and check the
     viewer to see the boundary particles
@@ -123,96 +105,71 @@ def setup_properties_for_gradual_force(pa):
[…]

### 2022-03-20 code/rb_case_1.py

@@ -1,129 +1,0 @@
-"""A cube translating and rotating freely without the influence of gravity.
-This is used to test the rigid body dynamics equations.
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-from rigid_body_3d import RigidBody3DScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-
-
-class Case0(Application):
-    def initialize(self):
-        self.rho0 = 10.0
-        self.hdx = 1.3
-        self.dx = 0.02
-        self.dy = 0.02
-        self.kn = 1e4
-        self.mu = 0.5
-        self.en = 1.0
-        self.dim = 2
-
-        self.dt = 1e-3
-        self.tf = 10
-
-    def create_scheme(self):
-        rb3d = RigidBody3DScheme(rigid_bodies=['body'], boundaries=None, dim=2)
-        s = SchemeChooser(default='rb3d', rb3d=rb3d)
-        return s
-
-    def configure_scheme(self):
-        dt = self.dt
-        tf = self.tf
-        self.scheme.configure_solver(dt=dt, tf=tf, pfreq=100)
-
-    def create_particles(self):
-        nx, ny = 10, 10
-        dx = self.dx
-        x, y = np.mgrid[0:1:nx * 1j, 0:1:ny * 1j]
-        x = x.flat
-        y = y.flat
-        m = np.ones_like(x) * dx * dx * self.rho0
-        h = np.ones_like(x) * self.hdx * dx
-        # radius of each sphere constituting in cube
-        rad_s = np.ones_like(x) * dx
-        body = get_particle_array(name='body', x=x, y=y, h=h, m=m, rad_s=rad_s,
-                                       constants={
-                                           'E': 69 * 1e9,
-                                           'poisson_ratio': 0.3,
-                                           'initial_spacing0': self.dx
-                                       })
-        body_id = np.zeros(len(x), dtype=int)
-        dem_id = np.zeros(len(x), dtype=int)
-        body.add_property('body_id', type='int', data=body_id)
-        body.add_property('dem_id', type='int', data=dem_id)
-        body.add_constant('total_no_bodies', [1])
-
[…]

### 2022-03-20 code/rb_case_1_old.py

@@ -1,121 +1,0 @@
-"""A cube translating and rotating freely without the influence of gravity.
-This is used to test the rigid body dynamics equations.
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-from rigid_body_2d import RigidBody2DScheme
-from rigid_body_3d import RigidBody3DScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-
-
-class Case0(Application):
-    def initialize(self):
-        self.rho0 = 10.0
-        self.hdx = 1.3
-        self.dx = 0.02
-        self.dy = 0.02
-        self.kn = 1e4
-        self.mu = 0.5
-        self.en = 1.0
-        self.dim = 2
-
-        self.dt = 1e-3
-        self.tf = 10
-
-    def create_scheme(self):
-        rb2d = RigidBody2DScheme(rigid_bodies=['body'], boundaries=None, dim=2)
-        rb3d = RigidBody3DScheme(rigid_bodies=['body'], boundaries=None, dim=2)
-        s = SchemeChooser(default='rb2d', rb2d=rb2d, rb3d=rb3d)
-        return s
-
-    def configure_scheme(self):
-        dt = self.dt
-        tf = self.tf
-        self.scheme.configure_solver(dt=dt, tf=tf, pfreq=100)
-
-    def create_particles(self):
-        nx, ny = 10, 10
-        dx = self.dx
-        x, y = np.mgrid[0:1:nx * 1j, 0:1:ny * 1j]
-        x = x.flat
-        y = y.flat
-        m = np.ones_like(x) * dx * dx * self.rho0
-        h = np.ones_like(x) * self.hdx * dx
-        # radius of each sphere constituting in cube
-        rad_s = np.ones_like(x) * dx
-        body = get_particle_array(name='body', x=x, y=y, h=h, m=m, rad_s=rad_s)
-        body_id = np.zeros(len(x), dtype=int)
-        body.add_property('body_id', type='int', data=body_id)
-
-        # setup the properties
-        self.scheme.setup_properties([body])
-
-        self.scheme.scheme.set_linear_velocity(body, np.array([0.5, 0.5, 0.]))
[…]

### 2022-03-20 code/rb_case_2.py

@@ -1,137 +1,0 @@
-"""
-Test the collision of two rigid bodues
-"""
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_body_3d import RigidBody3DScheme
-from geometry import hydrostatic_tank_2d
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_2d_block
-
-
-class RigidFluidCoupling(Application):
-    def initialize(self):
-        spacing = 0.05
-        self.hdx = 1.3
-
-        self.fluid_length = 1.0
-        self.fluid_height = 1.0
-        self.fluid_density = 1000.0
-        self.fluid_spacing = spacing
-
-        self.tank_height = 1.5
-        self.tank_layers = 3
-        self.tank_spacing = spacing
-
-        self.body_height = 0.2
-        self.body_length = 0.2
-        self.body_density = 2000
-        self.body_spacing = spacing / 2.
-        self.body_h = self.hdx * self.body_spacing
-
-        self.h = self.hdx * self.fluid_spacing
-
-        # self.solid_rho = 500
-        # self.m = 1000 * self.dx * self.dx
-        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
-        self.p0 = self.fluid_density * self.co**2.
-        self.c0 = self.co
-        self.alpha = 0.1
-        self.gy = 0.
-        self.dim = 2
-
-    def create_particles(self):
-        xb, yb = get_2d_block(dx=self.body_spacing,
-                              length=self.body_length,
-                              height=self.body_height)
-        m = self.body_density * self.body_spacing**self.dim
-        body1 = get_particle_array(name='body1',
-                                   x=xb,
-                                   y=yb,
-                                   h=self.body_h,
-                                   m=m,
-                                   rho=self.body_density,
-                                   m_fluid=0.,
-                                   rad_s=self.body_spacing / 2.,
-                                   constants={
[…]

### 2022-03-20 code/rb_case_3_old.py

@@ -1,129 +1,0 @@
-"""
-Test the collision of two rigid bodues made of same particle array
-"""
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_2d_block
-
-
-class RigidFluidCoupling(Application):
-    def initialize(self):
-        spacing = 0.05
-        self.hdx = 1.3
-
-        self.fluid_length = 1.0
-        self.fluid_height = 1.0
-        self.fluid_density = 1000.0
-        self.fluid_spacing = spacing
-
-        self.tank_height = 1.5
-        self.tank_layers = 3
-        self.tank_spacing = spacing
-
-        self.body_height = 0.2
-        self.body_length = 0.2
-        self.body_density = 2000
-        self.body_spacing = spacing / 2.
-        self.body_h = self.hdx * self.body_spacing
-
-        self.h = self.hdx * self.fluid_spacing
-
-        # self.solid_rho = 500
-        # self.m = 1000 * self.dx * self.dx
-        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
-        self.p0 = self.fluid_density * self.co**2.
-        self.c0 = self.co
-        self.alpha = 0.1
-        self.gy = 0.
-        self.dim = 2
-
-    def create_particles(self):
-        xf, yf, xt, yt = hydrostatic_tank_2d(
-            self.fluid_length, self.fluid_height, self.tank_height,
-            self.tank_layers, self.fluid_spacing, self.fluid_spacing)
-
-        m_fluid = self.fluid_density * self.fluid_spacing**2.
-
-        xb1, yb1 = get_2d_block(dx=self.body_spacing,
-                                length=self.body_length,
-                                height=self.body_height)
-        m = self.body_density * self.body_spacing**self.dim
-
[…]

### 2022-03-20 code/rigid_body_on_a_surface_2d.py

@@ -1,195 +1,0 @@
-"""
-
-A novel computational approach for large deformation and
-post-failure analyses of segmental retaining wall systems
-
-
-This is basically bouncing cube example.
-"""
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_2d_block
-
-
-class RigidFluidCoupling(Application):
-    def initialize(self):
-        spacing = 0.125 * 1e-2
-        self.hdx = 1.0
-
-        # the fluid dimensions are
-        # x-dimension (this is in the plane of the paper going right)
-        self.fluid_length = 0.5
-        # y-dimension (this goes into the paper)
-        self.fluid_width = 0.5
-        # z-dimension (this is in the plane of the paper going up)
-        self.fluid_height = 0.35
-
-        self.fluid_density = 1000.0
-        self.fluid_spacing = spacing
-
-        self.tank_length = 3.5
-        self.tank_width = 0.5
-        self.tank_height = 0.5
-        self.tank_spacing = spacing
-        self.tank_layers = 3
-
-        self.obstacle_length = 0.15
-        self.obstacle_width = 0.15
-        self.obstacle_height = 0.75
-        self.obstacle_spacing = spacing
-
-        self.body_height = 2.5 * 1e-2
-        self.body_length = 3.2 * 1e-2
-        self.body_depth = 0.054
-        self.body_density = 2000.
-        self.body_spacing = spacing
-        self.body_h = self.hdx * self.body_spacing
-
-        self.h = self.hdx * self.fluid_spacing
-
-        # self.solid_rho = 500
-        # self.m = 1000 * self.dx * self.dx
-        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
-        self.p0 = self.fluid_density * self.co**2.
-        self.c0 = self.co
-        self.alpha = 0.1
-        self.gy = -9.81
-        self.dim = 2
-
[…]

### 2022-03-20 code/rigid_body_on_a_surface_3d_from_single_body_transport.py

@@ -1,289 +1,0 @@
-"""1. A Smoothed Particle Hydrodynamics model for 3D solid body transportin free surface flows
-
-2. Numerical modeling of floating bodies transport for flooding analysis in
-nuclear reactor building
-
-"""
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_3d_block
-
-
-def get_fluid_tank_3d(xf, yf, zf, tank_length, tank_height, tank_layers,
-                      tank_spacing):
-    """
-    Given the fluid block and tank dimensions, return the tank geometry
-    here
-
-    tank_length: length in x direction
-    tank_height: length in z direction
-    """
-    # create the left wall
-    min_yf = min(yf)
-    max_yf = max(yf)
-
-    # width is in y direction
-    left_width = max_yf - min_yf
-
-    # create a tank layer on the left
-    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
-                                             length=(tank_layers - 1.)*tank_spacing,
-                                             height=left_width,
-                                             depth=tank_height)
-    # adjust the left wall of tank
-    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
-    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
-    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
-
-    # create a tank layer on the right
-    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
-                                                length=(tank_layers - 1.)*tank_spacing,
-                                                height=left_width,
-                                                depth=tank_height)
-    # adjust the left wall of tank
-    xt_right += tank_length - (np.max(xt_right) - np.min(xf))
[…]

### 2022-03-20 code/rigid_body_sliding_on_an_horizontal_plane.py

@@ -1,149 +1,0 @@
-"""DISCRETE ELEMENT METHOD FOR 3D SIMULATIONS OF MECHANICAL SYSTEMS OF
-NON-SPHERICAL GRANULAR MATERIALS by JIAN CHEN
-
-Section 5.4
-
-"""
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_2d_block, rotate
-
-
-class RigidFluidCoupling(Application):
-    def initialize(self):
-        spacing = 0.008 * 2.
-        self.hdx = 1.0
-
-        # the fluid dimensions are
-        # x-dimension (this is in the plane of the paper going right)
-        self.fluid_length = 0.5
-        # y-dimension (this goes into the paper)
-        self.fluid_width = 0.5
-        # z-dimension (this is in the plane of the paper going up)
-        self.fluid_height = 0.35
-
-        self.fluid_density = 1000.0
-        self.fluid_spacing = spacing
-
-        self.tank_length = 3.5
-        self.tank_width = 0.5
-        self.tank_height = 0.5
-        self.tank_spacing = spacing
-        self.tank_layers = 3
-
-        self.obstacle_length = 0.15
-        self.obstacle_width = 0.15
-        self.obstacle_height = 0.75
-        self.obstacle_spacing = spacing
-
-        self.body_height = 0.2
-        self.body_length = 0.2
-        self.body_depth = 0.054
-        self.body_density = 2000.
-        self.body_spacing = spacing
-        self.body_h = self.hdx * self.body_spacing
-
-        self.h = self.hdx * self.fluid_spacing
-
-        # self.solid_rho = 500
-        # self.m = 1000 * self.dx * self.dx
-        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
-        self.p0 = self.fluid_density * self.co**2.
-        self.c0 = self.co
-        self.alpha = 0.1
[…]

### 2022-03-20 code/rigid_body_sliding_on_an_inclined_plane_2d.py

@@ -1,149 +1,0 @@
-"""DISCRETE ELEMENT METHOD FOR 3D SIMULATIONS OF MECHANICAL SYSTEMS OF
-NON-SPHERICAL GRANULAR MATERIALS by JIAN CHEN
-
-Section 5.4
-
-"""
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_2d_block, rotate
-
-
-class RigidFluidCoupling(Application):
-    def initialize(self):
-        spacing = 0.008 * 2.
-        self.hdx = 1.0
-
-        # the fluid dimensions are
-        # x-dimension (this is in the plane of the paper going right)
-        self.fluid_length = 0.5
-        # y-dimension (this goes into the paper)
-        self.fluid_width = 0.5
-        # z-dimension (this is in the plane of the paper going up)
-        self.fluid_height = 0.35
-
-        self.fluid_density = 1000.0
-        self.fluid_spacing = spacing
-
-        self.tank_length = 3.5
-        self.tank_width = 0.5
-        self.tank_height = 0.5
-        self.tank_spacing = spacing
-        self.tank_layers = 3
-
-        self.obstacle_length = 0.15
-        self.obstacle_width = 0.15
-        self.obstacle_height = 0.75
-        self.obstacle_spacing = spacing
-
-        self.body_height = 0.2
-        self.body_length = 0.2
-        self.body_depth = 0.054
-        self.body_density = 2000.
-        self.body_spacing = spacing
-        self.body_h = self.hdx * self.body_spacing
-
-        self.h = self.hdx * self.fluid_spacing
-
-        # self.solid_rho = 500
-        # self.m = 1000 * self.dx * self.dx
-        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
-        self.p0 = self.fluid_density * self.co**2.
-        self.c0 = self.co
-        self.alpha = 0.1
[…]

### 2022-03-20 code/rigid_fluid_coupling.py

@@ -573,6 +573,7 @@ class RigidFluidCouplingScheme(Scheme):
             self.rigid_bodies = rigid_bodies
 
         # fluids parameters
+        self.edac = False
         self.edac_alpha = edac_alpha
         self.h = h
         self.art_nu = 0.
@@ -580,7 +581,7 @@ class RigidFluidCouplingScheme(Scheme):
 
         self.dim = dim
 
-        self.kernel = CubicSpline
+        self.kernel = QuinticSpline
 
         self.rho0 = rho0
         self.p0 = p0
@@ -595,7 +596,7 @@ class RigidFluidCouplingScheme(Scheme):
         self.fric_coeff = fric_coeff
         self.en = en
 
-        self.alpha = alpha
+        self.fluid_alpha = alpha
         self.beta = beta
 
         self.solver = None
@@ -616,14 +617,21 @@ class RigidFluidCouplingScheme(Scheme):
                            type=float,
                            help="Friction coefficient")
 
+        group.add_argument("--fluid-alpha", action="store",
+                           dest="fluid_alpha", default=0.5,
+                           type=float,
+                           help="Artificial viscosity")
+
+        add_bool_argument(group, 'edac', dest='edac', default=True,
+                          help='Use pressure evolution equation EDAC')
+
     def consume_user_options(self, options):
-        _vars = ['kr', 'kf', 'fric_coeff']
+        _vars = ['kr', 'kf', 'fric_coeff', 'fluid_alpha', 'edac']
         data = dict((var, self._smart_getattr(options, var)) for var in _vars)
         self.configure(**data)
 
     def attributes_changed(self):
-        if self.h is not None and self.c0 is not None:
-            self.art_nu = self.edac_alpha * self.h * self.c0 / 8
+        self.edac_nu = self.fluid_alpha * self.h * self.c0 / 8
 
     def get_equations(self):
         # elastic solid equations
@@ -639,7 +647,7 @@ class RigidFluidCouplingScheme(Scheme):
         from pysph.sph.wc.edac import (SolidWallPressureBC)
 
         all = self.fluids + self.boundaries + self.rigid_bodies
-        nu_edac = self._get_edac_nu()
+        edac_nu = self.edac_nu
 
         stage1 = []
 
@@ -647,17 +655,20 @@ class RigidFluidCouplingScheme(Scheme):
         for fluid in self.fluids:
             eqs.append(ContinuityEquation(dest=fluid,
                                           sources=self.fluids+self.boundaries), )
[…]

### 2022-03-20 code/single_cube_transport_in_3d_dam_break_with_out_any_obstructions.py

@@ -1,260 +1,0 @@
-"""Taken from \cite{ji2019coupled}, this is inturn was done in
-\citet{canelas2016sph}.
-
-
-This case models a single cube in the centre of the flume, with a face directly
-aligned with the flow direction.
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_3d_block
-
-
-def get_fluid_tank_3d(xf, yf, zf, tank_length, tank_height, tank_layers,
-                      tank_spacing):
-    """
-    Given the fluid block and tank dimensions, return the tank geometry
-    here
-
-    tank_length: length in x direction
-    tank_height: length in z direction
-    """
-    # create the left wall
-    min_yf = min(yf)
-    max_yf = max(yf)
-
-    # width is in y direction
-    left_width = max_yf - min_yf
-
-    # create a tank layer on the left
-    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
-                                             length=(tank_layers - 1.)*tank_spacing,
-                                             height=left_width,
-                                             depth=tank_height)
-    # adjust the left wall of tank
-    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
-    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
-    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
-
-    # create a tank layer on the right
-    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
-                                                length=(tank_layers - 1.)*tank_spacing,
-                                                height=left_width,
-                                                depth=tank_height)
-    # adjust the left wall of tank
-    xt_right += tank_length - (np.max(xt_right) - np.min(xf))
[…]

### 2022-03-20 code/water_entry_of_cylinder_2d.py

@@ -1,288 +1,0 @@
-"""Numerical simulation of interactions between free surface and rigid body
-using a robust SPH method, Pengnan Sun, 2015
-
-3.1.3 Water entry of 2-D cylinder
-
-"""
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_2d_block
-from geometry import hydrostatic_tank_2d, create_tank_2d_from_block_2d
-
-
-def create_circle_1(diameter=1, spacing=0.05, center=None):
-    dx = spacing
-    x = [0.0]
-    y = [0.0]
-    r = spacing
-    nt = 0
-    radius = diameter / 2.
-
-    tmp_dist = radius - spacing/2.
-    i = 0
-    while tmp_dist > spacing/2.:
-        perimeter = 2. * np.pi * tmp_dist
-        no_of_points = int(perimeter / spacing) + 1
-        theta = np.linspace(0., 2. * np.pi, no_of_points)
-        for t in theta[:-1]:
-            x.append(tmp_dist * np.cos(t))
-            y.append(tmp_dist * np.sin(t))
-        i = i + 1
-        tmp_dist = radius - spacing/2. - i * spacing
-
-    x = np.array(x)
-    y = np.array(y)
-    x, y = (t.ravel() for t in (x, y))
-    if center is None:
-        return x, y
-    else:
-        return x + center[0], y + center[1]
-
-
-class RigidFluidCoupling(Application):
-    def initialize(self):
-        spacing = 0.005
-        self.hdx = 1.0
-
-        # the fluid dimensions are
-        # x-dimension (this is in the plane of the paper going right)
-        self.L = 0.7
-        self.fluid_length = 1. * self.L
-        # y-dimension (this is in the plane of the paper going up)
-        self.fluid_height = 1. * self.L
-
-        self.fluid_density = 1000.
-        self.fluid_spacing = spacing
[…]

### 2022-03-20 code/wooden_block_rising_in_water_tank.py

@@ -1,341 +1,0 @@
-"""Taken from \cite{}, this is inturn was done in
-\citet{canelas2016sph}.
-
-
-This case models a single cube in the centre of the flume, with a face directly
-aligned with the flow direction.
-"""
-
-import numpy as np
-
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
-from pysph.solver.application import Application
-from pysph.sph.scheme import SchemeChooser
-
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_3d_block
-
-
-def get_fluid_tank_3d(xf, yf, zf, tank_height, tank_layers,
-                      tank_spacing):
-    """
-    Given the fluid block and tank dimensions, return the tank geometry
-    here
-
-    tank_length: length in x direction
-    tank_height: length in z direction
-    """
-    # create the left wall
-    min_yf = min(yf)
-    max_yf = max(yf)
-
-    # width is in y direction
-    left_width = max_yf - min_yf
-
-    # create a tank layer on the left
-    xt_left, yt_left, zt_left = get_3d_block(dx=tank_spacing,
-                                             length=(tank_layers - 1.)*tank_spacing,
-                                             height=left_width,
-                                             depth=tank_height)
-    # adjust the left wall of tank
-    xt_left += np.min(xf) - np.max(xt_left) - tank_spacing
-    yt_left += np.min(yf) - np.min(yt_left) + 0. * tank_spacing
-    zt_left += np.min(zf) - np.min(zt_left) + 0. * tank_spacing
-
-    # create a tank layer on the right
-    xt_right, yt_right, zt_right = get_3d_block(dx=tank_spacing,
-                                                length=(tank_layers - 1.)*tank_spacing,
-                                                height=left_width,
-                                                depth=tank_height)
-    # adjust the left wall of tank
-    xt_right += (np.max(xt_right) - np.min(xf)) + 1. * tank_spacing
[…]

### 2022-05-10 manuscript/paper.tex
Working stack of cylinders with corrected Mohseni force law.

@@
 
-\usepackage{caption}
 \usepackage{hyperref}
@@
 \usepackage{multirow}
+\usepackage{relsize}
 \usepackage[utf8]{inputenc}
 \usepackage{cleveref}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
+\usepackage[section]{placeins}
+\usepackage{booktabs}
 
@@
 \label{sec:intro}
+\begin{itemize}
+\item Rigid bodies in fluid flows in nature. Where can we find them? What kind
+  of problems do they give rise to? Ice-Sea? Debris?
+\item Many different ways RFC is been modeled, this includes mesh based and
+  mess less. Explain in a good detail what meshless methods are out there
+  which handles these problems. This includes SPH too.
+\item Explain SPH history and its applications in different areas. Now SPH
+  specifically applied in RFC area. Detail some papers where how differently
+  fluid is modelled, this includes ISPH, WCSPH, TVF, delta+ SPH. Also mention
+  the latest multiphase flow, where air is considered, then mention the
+  adaptive formulation, where the author captures the cavity.
+\item Similarly explain the many ways the rigid-rigid coupling is been
+  handled. Detail how non-smooth boundaries are handled.
+\item Mention the open source software which provide SPH formulation (there are 2.)
+\item Explain what we are going to do in the current work. We adapt the
+  Mohseni formulation to handle the non-smooth boundaries, we also incorporate
+  the damping, and extend the formulation to 3d and simulate 3d problems.
+\item Explain the examples. 3d Sliding case, 3d controlled sliding case, body
+  falling in water, then 3d dam break over dynamics rigid obstacles.
+\end{itemize}
 
-\section{Governing equations}
-\label{sec:fluid-mechanics}
+\FloatBarrier%
+\section{Fluid dynamics}
+\label{sec:fluid-dynamics}
 
-\section{CTVF formulation}
-\label{sec:ctvf-equations}
+\todoin{Connor FSI}
 
-\section{SPH discretization}
-\label{sec:sph-fluid-equations}
+The mass and momentum conservation laws that govern the dynamics of fluid motion are given in Lagrangian form by:
+\begin{equation}
+  \label{eq:ce}
+  \frac{d \rho}{d t} = - \rho \; \frac{\partial u_i}{\partial x_i},
+\end{equation}
+\begin{equation}
+  \label{eq:me}
+  \frac{d u_i}{d t} = \frac{1}{\rho} \; \frac{\partial \sigma_{ij}}{\partial x_j}
+  + g_i,
+\end{equation}
+where $\rho$ is the density, $u_i$ is the $i$\textsuperscript{th} component of
+the velocity field, $x_j$ is the $j$\textsuperscript{th} component of the
+position vector, $g_i$ is the component of body force per unit mass. And $\frac{d}{d t}$ is
+\begin{equation}
+  \label{eq:material-derivative}
+  \frac{d}{d t} = \frac{\partial }{\partial t} +
+  {u}_j \frac{\partial }{\partial x_j}.
+\end{equation}
 
+Following CTVF formulation, and moving the particles with transport velocity,
+we have the modified material derivative as
+\begin{equation}
+  \label{eq:modified-material-derivative}
+  \frac{\tilde{d} }{d t} = \frac{\partial }{\partial t} +
+  \tilde{u}_j \frac{\partial }{\partial x_j}.
+\end{equation}
+
+The adjust equations for the modified derivative are given by:
+
+\begin{equation}
+  \label{eq:ce-tvf}
+  \frac{\tilde{d} \rho}{d t} =
+  - \rho \frac{\partial \tilde{u}_j}{\partial x_j} +
+  \frac{\partial (\rho (\tilde{u}_j - u_j))}{\partial x_j}.
+\end{equation}
+\begin{equation}
+  \label{eq:mom-tvf}
+  \frac{\tilde{d} u_i}{d t} =
+  \frac{\partial}{\partial x_j} (u_i (\tilde{u}_j - u_j))
+  - u_i \frac{\partial}{\partial x_j} (\tilde{u}_j - u_j)
+  + g_i
+  +\frac{1}{\rho} \frac{\partial \sigma_{ij}}{\partial x_j}.
+\end{equation}
+
+For a weakly-compressible or incompressible fluid, a viscous force is added:
+\begin{equation}
+  \label{eq:fluid-stress-decomposition}
+  \sigma_{ij} = - p \delta_{ij} + 2 \eta \frac{\partial u_i}{\partial x_j}
+\end{equation}
+where $\eta$ is the kinematic viscosity of the fluid.
+
+In both fluid and solid modelling the pressure is computed using an
+isothermal equation of state, given as,
+\begin{equation}
+  \label{eq:pressure-equation}
+  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
+\end{equation}
+where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
+$\rho_0$ are the reference speed of sound and density, respectively. For solids,
+$c_0$ is computed as $\sqrt{\frac{E}{3 (1 - 2 \nu)\rho_{0}}}$, $\nu$ is the
+Poisson ratio.
+
+SPH discretization of the modified governing equations are given by:
+\begin{equation}
+  \label{eq:sph-discretization-continuity}
+  \frac{\tilde{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; (
+  \rho_{a} \; \tilde{\ten{u}}_{ab} \; + \;
+  (\rho \; (\tilde{\ten{u}} \; - \;
+  \ten{u}))_{ab}) \; \cdot \nabla_{a} W_{ab},
+\end{equation}
+\begin{multline}
+  \label{eq:sph-momentum-fluid}
+  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
+  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
+  \bigg) \bigg]
+  \cdot \nabla_{a} W_{ab} \\
+  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
+  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
+    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
+  \ten{g}_{a},
+\end{multline}
+The particles in the current scheme are moved with the transport velocity,
+\begin{equation}
+  \label{eq:transport_velocity_position_derivative}
+  \frac{d\ten{r}_a}{dt} = \ten{\tilde{u}}_a.
+\end{equation}
+%
+The transport velocity is updated using,
+\begin{equation}
+  \label{eq:transport_velocity}
+  \ten{\tilde{u}}_a(t + \Delta t) =\ten{u}_a(t) + \Delta t \; \frac{\tilde{d} \ten{u}_a}{dt} +
+  \bigg(\frac{d \ten{u}_{a}}{dt}\bigg)_{\text{c}} \Delta t,
+\end{equation}
+where $\ten{A}_a = \rho_a \ten{u}_a \otimes (\ten{\tilde{u}}_a - \ten{u}_a)$,
+$\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
+fluid and \citet{morris1997modeling} formulation is used to discretize the
+viscosity term.
+\begin{itemize}
+\item Discuss about the homogenization force (We use GTVf).
+\item Describe $\Pi_{ij}$ for numerical stability.
+\item And other terms.
+\end{itemize}
+We add to the momentum equation an additional artificial viscosity term
+$\Pi_{ab}$~\cite{monaghan-review:2005} to maintain the stability of the
+numerical scheme, given as,
+\begin{align}
+  \label{eq:mom-av}
+  \Pi_{ab} =
+  \begin{cases}
+\frac{-\alpha h_{ab} \bar{c}_{ab} \phi_{ab}}{\bar{\rho}_{ab}}
+  & \ten{u}_{ab}\cdot \ten{r}_{ab} < 0, \\
+  0 & \ten{u}_{ab}\cdot \ten{r}_{ab} \ge 0,
+\end{cases}
+\end{align}
+where,
+%
+\begin{equation}
+  \label{eq:av-phiij}
+  \phi_{ab} = \frac{\ten{u}_{ab} \cdot \ten{r}_{ab}}{r^2_{ab} + 0.01 h^2_{ab}},
+\end{equation}
+%
+where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$, $\ten{u}_{ab} = \ten{u}_a -
+\ten{u}_b$, $h_{ab} = (h_a + h_b)/2$, $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$,
+$\bar{c}_{ab} = (c_a + c_b) / 2$, and $\alpha$ is the artificial
+viscosity parameter.
+
+%
+where $\big(\frac{d \ten{u}_a}{dt}\big)_{\text{c}}$ is the homogenization
+acceleration which ensures that the particle positions are homogeneous.
+
+\subsection{Boundary conditions}
+
+The ghost particle approach of \citet{Adami2012} is used to model the
+boundaries. We use three layers of ghost particles to model the solid wall.
+The properties of the solid wall are interpolated from the fluid particles.
+
+When computing the divergence of the velocity field on fluid particles, we
+enforce a no-penetration boundary condition and not a no-slip boundary
+condition. The velocity of the fluid is projected onto the ghost particles
+using,
+\begin{equation}
+  \label{eq:v-ghost}
+  \ten{\hat{u}}_a = \frac{\sum_b\ten{u}_b W_{ab}}{\sum_b W_{ab}},
+\end{equation}
+\begin{equation}
+  \label{eq:v-hat-ghost}
+  \ten{\check{u}}_a = \frac{\sum_b\tilde{\ten{u}}_b W_{ab}}{\sum_b W_{ab}},
+\end{equation}
+where $\ten{u}_b$, $\ten{\tilde{u}}_b$ are the momentum and transport velocity
+of the fluid respectively and $W_{ab}$ is the kernel value between the fluid
+particle and the ghost particle.
+
+The normal component of this projected velocity is then reflected and set as
+the ghost particle velocity,
+\begin{equation}
+  \label{eq:free-slip-bc-u}
+  \ten{u}_{\text{Ga}} = 2 \ten{\hat{n}}((\ten{u}_{\text{p}} - \ten{\hat{u}}_{\text{a}})\cdot \ten{\hat{n}}) + \ten{\hat{u}}_{\text{a}},
+\end{equation}
+where $\ten{u}_{\text{p}}$ is the local velocity of the boundary and
+$\ten{\hat{n}}$ is the unit normal to the boundary particle $a$. Similarly the
+transport velocity of the ghost particle is set as,
+\begin{equation}
+  \label{eq:free-slip-bc-u}
+  \tilde{\ten{u}}_{\text{Gi}} = 2 \ten{\hat{n}}((\ten{u}_{\text{p}} - \ten{\check{u}}_{\text{i}})\cdot \ten{\hat{n}}) + \ten{\check{u}}_{\text{i}},
+\end{equation}
+
+When the viscous force is computed, the no slip boundary condition is used,
+where the velocity on the boundary set as,
+\begin{equation}
+  \label{eq:no-slip-bc-u}
+  \ten{u}_{\text{Ga}} = 2 \ten{u}_{\text{p}} - \ten{\hat{u}}_{\text{a}},
+\end{equation}
+a similar form is used for the transport velocity here too,
+\begin{equation}
+  \label{eq:no-slip-bc-uhat}
+  \tilde{\ten{u}}_{\text{Ga}} = 2 \ten{u}_{\text{p}} - \ten{\check{u}}_{\text{a}}.
+\end{equation}
+
+The pressure of the boundary particle is extrapolated from its surrounding
+fluid particles by the following equation,
+\begin{equation}
+  \label{eq:pressure-bc}
+  p_w = \frac{\Sigma_f p_f W_{wf} + (\ten{g} - \ten{a}_{\ten{w}}) \cdot \Sigma_f
+    \rho_f \ten{r}_{wf} W_{wf}}{\Sigma_f W_{wf}},
+\end{equation}
+where $\ten{a}_w$ is the acceleration of the wall. The subscript $f$ denotes
+the fluid particles and $w$ denotes the wall particles.
+
+\begin{itemize}
+\item Choose the timestep
+\end{itemize}
+
+\FloatBarrier%
 \section{Rigid body dynamics}
@@
 
-\section{How to handle rigid fluid coupling}
+The state of a rigid body is defined by position of center of mass, velocity
+of center of mass, a rotation matrix to define the three rotational degrees of
+freedom and angular velocity.
+
+The equations governing the dynamics of rigid body are, balance of linear and
+angular momentum given by,
+
+\begin{equation}
+  \label{eq:balance_linear_mom}
+  \frac{d \; (M \ten{v}_{cm})}{d t} = \sum_i \ten{F}_i
+\end{equation}
+
+\begin{equation}
+  \label{eq:balance_angular_mom}
+  \frac{d \ten{L}}{d t} = \teng{\tau}_{cm}
+\end{equation}
+
+where $\teng{\tau}_i$ is the torque about center of mass due to forces on the
+particles,
+
+\begin{equation}
+  \label{eq:torque}
+  \teng{\tau}_{cm} = \sum_i \ten{F}_i \times (\ten{r}_{cm} - \ten{r}_{i})
+\end{equation}
+
+The angular momentum and the center of mass velocity of the body is updated by following
+
+\begin{equation}
+  \label{eq:ang_mom_update}
+  \ten{x}_{cm} = \ten{x}_{cm} + \frac{\ten{F}_{cm}}{M} \; \Delta t
+\end{equation}
+
+\begin{equation}
+  \label{eq:ang_mom_update}
+  \ten{L} = \ten{L} + \teng{\tau}_{cm} \; \Delta t
+\end{equation}
+
+\begin{equation}
+  \label{eq:rotation_update}
+  \ten{R} = \ten{R} + \tilde{\teng{\omega}} \, \ten{R} \; \Delta t
+\end{equation}
+
+\begin{equation}
+  \label{eq:moi_update}
+  \ten{I}^{-1} = \ten{R} \hat{\ten{I}}^{-1} \ten{R}^T
+\end{equation}
+
+\begin{equation}
+  \label{eq:moi_update}
+  \teng{\omega} = \ten{I}^{-1} \; \ten{L}
+\end{equation}
+
+Particles update
+
+\begin{equation}
+  \label{eq:rb_particle_pos_update}
+  \ten{x}_i(t) = \ten{x}_{cm}(t) + \ten{R}(t) \; \hat{\ten{r}}_{i}(t)
+\end{equation}
+
+\begin{equation}
+  \label{eq:rb_particle_vel_update}
+  \ten{v}_i(t) = \ten{v}_{cm}(t) + \teng{\omega}(t) \; \ten{r}_{i}(t)
+\end{equation}
+
+\FloatBarrier%
+\section{Rigid fluid coupling}
 \label{sec:rfc}
 
+In order to find the forces on rigid body due to fluid and vice versa, we
+assume the particles of rigid body to be dummy and consider a hydrodynamic
+mass attach to it. A three layers of particles are expected on the rigid body
+and the force acting on the fluid due to the
+
+\begin{multline}
+  \label{eq:force_on_fluid_due_to_rb}
+  \frac{\tilde{d}\ten{u}_{a}}{dt} =  \sum_{b} m^0_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I}\bigg) \bigg]
+  \cdot \nabla_{a} W_{ab}
+\end{multline}
+
+\begin{multline}
+  \label{eq:force_on_fluid_due_to_rb}
+  f_i =  m_a \sum_{b} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I}\bigg) \bigg]
+  \cdot \nabla_{a} W_{ab}
+\end{multline}
+
+The pressure on the rigid body is computed using the Adami boundary condition.
+Similarly we set no slip velocity condition for the computation of viscous
+force computation.
+
+\FloatBarrier%
 \section{Collision between rigid bodies}
@@
 
+\FloatBarrier%
+\section{Final set of governing equations}
+\label{sec:final_discretized_equations}
+
+\begin{itemize}
+\item Write the time step factor.
+\item Write the rigid body equations with real forces.
+\item Write rigid body particle equations.
+\end{itemize}
+
+\begin{multline}
+  \label{eq:sph-momentum-fluid}
+  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b \in b_f} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
+  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
+  \bigg) + \Pi_{ab} \bigg]
+  \cdot \nabla_{a} W_{ab} \\
+  + \ten{u}_{a} \sum_{b \in b_f} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
+  \nabla_{a} W_{ab} + \sum_{b \in b_f} m_b \frac{4 \eta \nabla W_{ab}\cdot
+    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} \\
+ - \sum_{b \in b_r} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
+  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
+  \bigg) + \Pi_{ab} \bigg]
+  \cdot \nabla_{a} W_{ab} \\
+  + \ten{u}_{a} \sum_{b \in b_r} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
+  \nabla_{a} W_{ab} + \sum_{b \in b_r} m_b \frac{4 \eta \nabla W_{ab}\cdot
+    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab}\\
+ - \sum_{b \in b_b} m_b \bigg[
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
+  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
+  \bigg) + \Pi_{ab} \bigg]
+  \cdot \nabla_{a} W_{ab} \\
+  + \ten{u}_{a} \sum_{b \in b_b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
+  \nabla_{a} W_{ab} + \sum_{b \in b_b} m_b \frac{4 \eta \nabla W_{ab}\cdot
+    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab}
+  + \ten{g}_{a}
+\end{multline}
+
+The particles in the current scheme are moved with the transport velocity,
+\begin{equation}
+  \label{eq:transport_velocity_position_derivative}
+  \frac{d\ten{r}_a}{dt} = \ten{\tilde{u}}_a.
+\end{equation}
+
+\todoin{Rigid body equations}
+\todoin{Expand on forces in detail}
+\begin{equation}
+  \label{eq:balance_linear_mom}
+  \frac{d \; (M \ten{v}_{cm})}{d t} = \sum_i \ten{F}_{due to fluid} \sum_i \ten{F}_{due to solids}
+\end{equation}
+
+\begin{equation}
+  \label{eq:balance_angular_mom}
+  \frac{d \ten{L}}{d t} = \sum_i \ten{F}_{due to fluid} \sum_i \ten{F}_{due to solids} \times (\ten{r}_{cm} - \ten{r}_{i})
+\end{equation}
+
+\begin{equation}
+  \label{eq:rb_particle_pos_update}
+  \ten{x}_i(t) = \ten{x}_{cm}(t) + \ten{R}(t) \; \hat{\ten{r}}_{i}(t)
+\end{equation}
+
+\begin{equation}
+  \label{eq:rb_particle_vel_update}
+  \ten{v}_i(t) = \ten{v}_{cm}(t) + \teng{\omega}(t) \; \ten{r}_{i}(t)
+\end{equation}
+
+\FloatBarrier%
 \section{Results and discussion}
@@
 
-In the current section we test the frictional part of the current solver by
-modeling the sliding of a rigid body on an inclined surface in 3D. We compare
-against the analytical solution to validate the test case.
-
-We consider a rigid body of length 0.1 m, height 0.1 and depth of 0.1m allowed
-to slide on an inclined surface at an angle $\frac{\pi}{3}$. A density of 2000
-kg\,m\textsuperscript{-3} is used for the body. Other numerical parameters,
-such as the repulsive spring stiffness $k_r=3.0 \times 10^{5}$ and tangential
-spring stiffness $k_t=3.0 \times 10^{5}$ is chosen, respectively. A particle
-spacing of $0.001$ is considered, resulting in $4400$ particles per body. From
-the analytical solution, the evolution of velocity is given by,
-\begin{equation}
-  \label{eq:ce}
-  \ten{v}(t) = (\mu \teng{g} \sin (\theta) - \teng{g} \cos (\theta)) t.
-\end{equation}
-
-We consider three different friction coefficients, $\mu=0.5$, $\mu=0.5$, and
-$\mu=0.5$. From the analytical solution, when the friction coefficient is
-greater than $\tan(frac{\pi}{3})$, the body doesn't slide.
-
-\Cref{fig:dinesh-2022-bouncing-cube-snapshots-3d} depicts the snapshots of the
-rigid body bouncing on a wall. The coefficient of restitution corresponding to
-the snapshots are equal to $1$. As the rigid body approaches the wall, its
-velocity is increases due to gravity. As soon as the body comes into contact
-of the wall, the collision happens, the body's velocity is reduced until it
-becomes zero, and then it rebounds, and bounces back to a certain height.
-
-\begin{figure}[!htpb]
-  \centering
-  \begin{subfigure}{0.48\textwidth}
-    \centering
-    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time0}
-    \subcaption{t = 2.5e-03 sec}\label{fig:passing-0}
-  \end{subfigure}
-  %
-  \begin{subfigure}{0.48\textwidth}
-    \centering
-    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time1}
-    \subcaption{t = 2.5e-03 sec}\label{fig:passing-1}
-  \end{subfigure}
-
-  \begin{subfigure}{0.48\textwidth}
-    \centering
-    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time2}
-    \subcaption{t = 2.5e-03 sec}\label{fig:passing-2}
-  \end{subfigure}
-  %
-  \begin{subfigure}{0.48\textwidth}
-    \centering
-    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time3}
-    \subcaption{t = 2.5e-03 sec}\label{fig:passing-3}
-  \end{subfigure}
-  \caption{Elastic solid sliding}
-\label{fig:mohseni-2021-sliding-3d}
-\end{figure}
-%
-
-\Cref{fig:results-solid-sliding-velocity-vs-time} shows a evolution of
-velocity of the center of mass of the rigid body for different frictional
-coefficients against the analytical solution. From
-\Cref{fig:results-solid-sliding-velocity-vs-time} we can see that the current
-solver has an excellent match with the analytical solution and covers all the
-regimes of the sliding case.
-
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
-  \caption{Velocity versus time}
-\label{fig:results-solid-sliding-velocity-vs-time}
-\end{figure}
-
-\subsubsection{A test to check the conservation properties of rigid body}
-\label{sec:conservation-of-rb-properties}
-
+\FloatBarrier%
 \subsection{A 2d and 3d rigid body sliding}
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time0}
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_2/time0}
     \subcaption{t = 2.5e-03 sec}\label{fig:passing-0}
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time1}
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_2/time1}
     \subcaption{t = 2.5e-03 sec}\label{fig:passing-1}
@@
     \centering
-    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time2}
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_2/time2}
     \subcaption{t = 2.5e-03 sec}\label{fig:passing-2}
   \end{subfigure}
-  %
-  \begin{subfigure}{0.48\textwidth}
-    \centering
-    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time3}
-    \subcaption{t = 2.5e-03 sec}\label{fig:passing-3}
-  \end{subfigure}
-  \caption{Elastic solid sliding}
+  \caption{Rigid body with friction $0.2$ sliding.}
 \label{fig:mohseni-2021-sliding-3d}
 \end{figure}
-%
 
@@
 
+\FloatBarrier%
 \subsection{Controlled Sliding on a Flat Surface}
@@
 
+In the current section we control a rigid body to slide on a frictional flat
+surface by applying an external normal $F_n$ and tangential force $F_t$. The
+friction coefficient between the body and wall is assumed to be $0.5$. The
+schematic of the rigid body as well as the wall is shown in
+\cref{fig:schematic-controlled-rigid-body-sliding}.
+\begin{figure}[!htpb]
+  \centering
+  % \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Schematic of the controlled rigid body sliding}
+\label{fig:schematic-controlled-rigid-body-sliding}
+\end{figure}
+
+\Cref{fig:velocity-vs-time-controlled-sliding} depicts the time histories of
+velocity of the center of mass of the rigid body with time, as well as the
+variation of applied external normal $F_n$ and tangential $F_t$ forces.
+\begin{itemize}
+\item How the normal force is varied?
+\item When does the tangential force come into picture?
+\item What physics is supposed to follow?
+\item Say that the current velocity variation is matching with the analytical one.
+\end{itemize}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Velocity vs time of the rigid slider}
+\label{fig:velocity-vs-time-controlled-sliding}
+\end{figure}
+
+\FloatBarrier%
+\subsection{Three bodies colliding}
+\label{sec:three-bodies-colliding}
+
+\begin{figure}[!htpb]
+  \centering
+  % \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Schematic of the controlled rigid body sliding}
+\label{fig:schematic-controlled-rigid-body-sliding}
+\end{figure}
+
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/amaro_2019_collision_between_three_rigid_cubes/Mohseni_Vyas/time0}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/amaro_2019_collision_between_three_rigid_cubes/Mohseni_Vyas/time1}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/amaro_2019_collision_between_three_rigid_cubes/Mohseni_Vyas/time2}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/amaro_2019_collision_between_three_rigid_cubes/Mohseni_Vyas/time3}
+  \end{subfigure}
+\caption{A dummy figure (To be fixed)}
+\label{fig:snapshots-three-cubes-colliding}
+\end{figure}
+%
+
+\FloatBarrier%
 \subsection{Stack of cylinders}
@@
 
+This test case is used to validate the current solid-solid contact force
+model. A stack of cylinders initially at rest are allowed to settle under
+gravity in a tank. This is simulated by Zhang (2011), where DEM is used. The
+numerical parameters of the current test case are listed in
+\Cref{tab:stack-of-cylinders}. The dimensions of the cylinder as well as the
+tank are shown in figure (Ref the schematic figure).
+
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    \toprule
+    Quantity & Values\\
+    \midrule
+    $L$, length of the domain & 1 m \\
+    Time of simulation & 2.5 s \\
+    $c_s$ & 10 m/s \\
+    $\rho_0$, reference density & 1 kg/m\textsuperscript{3} \\
+    Reynolds number & 200 \& 1000 \\
+    Resolution, $L/\Delta x_{\max} : L/\Delta x_{\min}$ & $[100:200]$ \& $[150:300]$\\
+    Smoothing length factor, $h/\Delta x$ & 1.0\\
+    \bottomrule
+  \end{tabular}
+  \caption{Parameters used for the Taylor-Green vortex problem.}%
+  \label{tab:stack-of-cylinders}
+\end{table}
+
+\Cref{fig:snapshots-stack-of-cylinders} presents a set of snapshots
+corresponding to the simulation of a stack of cylinders collapsing under
+gravity using CTVF-DEM in comparison with the corresponding experimental
+photos by Zhang. From the presented figure, the reproduced cylinder's
+positions appear to be consistent with those observed in the experiment. From
+\Cref{fig:snapshots-stack-of-cylinders}, the current solver has presented
+proper level of stability.
+
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/time0}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=0.75\textwidth]{images/stack_of_cylinders_experimental_images/time0}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/time1}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=0.75\textwidth]{images/stack_of_cylinders_experimental_images/time1}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/time2}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=0.75\textwidth]{images/stack_of_cylinders_experimental_images/time2}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/time3}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=0.75\textwidth]{images/stack_of_cylinders_experimental_images/time3}
+  \end{subfigure}
+\caption{A dummy figure (To be fixed)}
+\label{fig:snapshots-stack-of-cylinders}
+\end{figure}
+%
+
+\Cref{fig:x-com-stack-of-cylinders,fig:y-com-stack-of-cylinders} presents the
+time histories of the x and y components of the center of mass of the
+cylinders respectively as well as those from numerical simulations by
+SPH-DCDEM as well as MPS-DEM with respect to those from the experiment Zhang.
+From the presented figure, the effective center of mass of the cylinders is in
+good agreement with the experiment.
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/xcom}
+  \caption{A dummy figure (To be fixed)}
+\label{fig:x-com-stack-of-cylinders}
+\end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/ycom}
+  \caption{A dummy figure (To be fixed)}
+\label{fig:y-com-stack-of-cylinders}
+\end{figure}
+
+\FloatBarrier%
 \subsection{Falling solid in water}
@@
 
+In this section, the rigid fluid coupling part of the current solver is
+evaluated by simulation of a rigid cube falling in an hydrostatic tank (cite
+experimental paper). The CTVF-DEM solver is employed to simulate water entry
+of a rigid cube, which is studied experimentally by (cite the paper). The
+numerical parameters of the current test case are listed in
+\Cref{tab:stack-of-cylinders}. The dimensions of the schematic are shown in
+figure.
+
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    \toprule
+    Quantity & Values\\
+    \midrule
+    $L$, length of the domain & 1 m \\
+    Time of simulation & 2.5 s \\
+    $c_s$ & 10 m/s \\
+    $\rho_0$, reference density & 1 kg/m\textsuperscript{3} \\
+    Reynolds number & 200 \& 1000 \\
+    Resolution, $L/\Delta x_{\max} : L/\Delta x_{\min}$ & $[100:200]$ \& $[150:300]$\\
+    Smoothing length factor, $h/\Delta x$ & 1.0\\
+    \bottomrule
+  \end{tabular}
+  \caption{Parameters used for the Taylor-Green vortex problem.}%
+  \label{tab:stack-of-cylinders}
+\end{table}
+
+A rigid cube of a side length of 30 mm enters the water initially at
+hydrostatic state with a velocity of 30 $m/s$ in z-direction.
+\Cref{fig:snapshots-falling-solid-in-water} presents a snapshots of the rigid
+cube falling in an hydrostatic tank with the current solver as well as
+WCSPH-DEM solver as well as the experimental result. From the presented figure
+\Cref{fig:snapshots-falling-solid-in-water}, we can see that the pressure
+distribution is smooth and the simulation is stable. A zoomed in view near the
+rigid cube is presented in \cref{fig:snapshots-falling-solid-in-water-zoomed}
+when simulated with WCSPH-DEM and CTVF-DEM. From
+\cref{fig:snapshots-falling-solid-in-water-zoomed} we can see that the fluid
+particle distribution around the body with CTVF scheme is uniform when
+compared with WCSPH, thanks to the implemented transport velocity formulation.
+
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time0}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time1}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time2}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time3}
+  \end{subfigure}
+\caption{A dummy figure (To be fixed)}
+\label{fig:snapshots-falling-solid-in-water}
+\end{figure}
+
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time0}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time1}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time2}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time3}
+  \end{subfigure}
+  \caption{Zoomed in snapshots of rigid body inside water.}
+\label{fig:snapshots-falling-solid-in-water-zoomed}
+\end{figure}
+
+\Cref{fig:disp-falling-solid-in-water} presents the time history of the
+displacement of the rigid cube with time in comparison with the experimental
+result by (cite experimental paper). From the presented figure, the CTVF-DEM
+model has reproduced the displacement of the rigid cube with acceptable levels
+of stability as well as accuracy.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/y_cm_vs_time}
+  \caption{Center of mass of rigid body vs time compared with experiment}
+\label{fig:disp-falling-solid-in-water}
+\end{figure}
+
+\FloatBarrier%
 \subsection{Floating solid in water}
@@
 
-\subsection{3D dam breaking flow hitting one cube}
-\label{sec:3d-dam-breaking-one-cube-hit}
+\FloatBarrier%
+\subsection{3D dam breaking flow hitting cubes}
 
@@
 
-\subsection{3D dam breaking flow hitting three cube}
-\label{sec:3d-dam-breaking-one-cube-hit}
+In the current case we simulate a 3d dam breaking flow hitting different
+configuration of rigid cubes. This is experimentally studied by SPH DCDEM,
+where the author used Direct Linear Transform (DLT) to track the cubes as they
+move after the impact. A total three rigid body configurations are studied, a
+single cube, three cubes and a pyramid configuration, respectively. It is
+numerically studied by SPH-DCDEM, MPS-DEM, and (cite some other papers). The
+side length of each cube is $3.5$ mm and the material properties are listed in
+\cref{tab:material-properties-3d-dam-breaking-flow-hitting-cubes} and the
+numerical parameters are given in
+\cref{tab:material-properties-3d-dam-breaking-flow-hitting-cubes}. In all the
+three cases the fluid is initially allowed to flow by opening a gate which
+lifts at a velocity of 3.5 m\,s\textsuperscript{-1}
 
-\cite{amaro2019improvement}
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    \toprule
+    Quantity & Values\\
+    \midrule
+    $L$, length of the domain & 1 m \\
+    $\rho_0$, reference density & 1 kg/m\textsuperscript{3} \\
+    Reynolds number & 200 \& 1000 \\
+    Resolution, $L/\Delta x_{\max} : L/\Delta x_{\min}$ & $[100:200]$ \& $[150:300]$\\
+    \bottomrule
+  \end{tabular}
+  \caption{Parameters used for the Taylor-Green vortex problem.}%
+  \label{tab:material-properties-3d-dam-breaking-flow-hitting-cubes}
+\end{table}
 
-\subsection{3D dam breaking flow hitting pyramid cubes configuration}
-\label{sec:3d-dam-breaking-one-cube-hit}
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    \toprule
+    Quantity & Values\\
+    \midrule
+    $L$, length of the domain & 1 m \\
+    $\rho_0$, reference density & 1 kg/m\textsuperscript{3} \\
+    Reynolds number & 200 \& 1000 \\
+    Resolution, $L/\Delta x_{\max} : L/\Delta x_{\min}$ & $[100:200]$ \& $[150:300]$\\
+    \bottomrule
+  \end{tabular}
+  \caption{Parameters used for the Taylor-Green vortex problem.}%
+  \label{tab:numerical-properties-3d-dam-breaking-flow-hitting-cubes}
+\end{table}
 
-\cite{amaro2019improvement}
+\Cref{fig:snapshots-single-cube-3d-dam-breaking-flow} shows the snapshots of
+the rigid cube moving downstream of the tank when interacting with the fluid
+flow against the experimental result (cite SPH DCDEM). From
+\Cref{fig:snapshots-single-cube-3d-dam-breaking-flow} we can see that the
+rigid cube matches well with the experimental result. Further, we compare the
+positions of the rigid cube with time in
+\Cref{fig:x-position-single-cube-3d-dam-breaking-flow}, against the
+experimental results, SPH-DCDEM, MPS-DEM results. It can be seen from figure
+\Cref{fig:x-position-single-cube-3d-dam-breaking-flow} that the current solver
+is able to provide good accuracy in producing the correct displacement of the
+cube and agrees well with the experimental as well as the other numerical
+techniques.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Snapshots of a single cube under a 3d dam breaking flow}
+\label{fig:snapshots-single-cube-3d-dam-breaking-flow}
+\end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{x position of the cube with time for single cube.}
+\label{fig:x-position-single-cube-3d-dam-breaking-flow}
+\end{figure}
+
+The initial configuration of the dam breaking flow over three cubes is shown
+in figure \Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow}.
+\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow} shows the snapshots of
+the rigid cubes at different time instants from the start of fluid hit with
+the color of the fluid particles representing pressure. From the
+\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow} we can see that the
+simulated rigid bodies match well with the experimental observations. We also
+compare the x component of the effective center of mass of the three cubes
+with time in \Cref{fig:x-position-three-cubes-3d-dam-breaking-flow}, against
+the experimental results, SPH-DCDEM, MPS-DEM results. From figure
+\Cref{fig:x-position-three-cubes-3d-dam-breaking-flow}, we can see that the
+current solve is agrees well with the experimental as well as with the other
+numerical method results.
+\begin{itemize}
+\item Mention at what time does the fluid hits the rigid cubes.
+\end{itemize}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Snapshots of a three cubes under a 3d dam breaking flow}
+\label{fig:snapshots-three-cubes-3d-dam-breaking-flow}
+\end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{x position of the cubes with time for three cube.}
+\label{fig:x-position-three-cubes-3d-dam-breaking-flow}
+\end{figure}
+
+The placement of the cubes in the pyramid configuration including dimensions,
+distance from the left wall and other dimension related information can be
+seen in figure \Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow}.
+\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow} shows the snapshots of
+the rigid cubes at different time instants and the color coding of the fluid
+particles represents pressure. From
+\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow}, it can be seen that the
+rigid body positions are in match with the experimental observations. Which is
+further validated by doing a quantitative comparison of the x component of
+effective center of mass of the six cubes in time against the experimental
+results, SPH-DCDEM, MPS-DEM results in
+\Cref{fig:x-position-three-cubes-3d-dam-breaking-flow}. From these figures, we
+can see that the current solver is in good agreement with the other numerical
+and experimental results.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Snapshots of six cubes under a 3d dam breaking flow}
+\label{fig:snapshots-six-cubes-3d-dam-breaking-flow}
+\end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{x position of the six with time for three cube.}
+\label{fig:x-position-six-cube-3d-dam-breaking-flow}
+\end{figure}
 

### 2022-05-10 automate.py

@@ -73,21 +73,82 @@ def get_files_at_given_times_from_log(files, times, logfile):
     return result
 
 
-class StackOfCylinders(Problem):
+class Dinesh2022RigidBodiesCollisionNewtons3rdLawCheck2D(Problem):
     def get_name(self):
-        return 'stack_of_cylinders'
+        return 'dinesh_2022_rigid_bodies_collision_newtons_3rd_law_check_2d'
 
     def setup(self):
         get_path = self.input_path
 
-        cmd = 'python code/stack_of_cylinders.py' + backend
+        cmd = 'python code/dinesh_2022_rigid_bodies_collision_newtons_3rd_law_check_2d.py' + backend
 
         # Base case info
         self.case_info = {
-            'bui': (dict(
-                pfreq=100,
-                dem="bui",
-                ), 'Bui'),
+            'Mohseni_angle_0': (dict(
+                scheme='rb3d',
+                pfreq=10,
+                kr=1e5,
+                fric_coeff=0.4,
+                timestep=5e-5,
+                tf=0.015,
+                contact_force_model='Mohseni',
+                angle=0,
+                ), 'Mohseni angle 0'),
+
+            'Mohseni_Vyas_angle_0': (dict(
+                scheme='rb3d',
+                pfreq=10,
+                kr=1e5,
+                fric_coeff=0.4,
+                timestep=5e-5,
+                tf=0.015,
+                contact_force_model='Mohseni_Vyas',
+                angle=0,
+                ), 'Mohseni Vyas angle 0'),
+
+            'Mohseni_angle_30': (dict(
+                scheme='rb3d',
+                pfreq=10,
+                kr=1e5,
+                fric_coeff=0.4,
+                timestep=5e-5,
+                tf=0.015,
+                contact_force_model='Mohseni',
+                angle=30,
+                ), 'Mohseni angle 30'),
+
+            'Mohseni_Vyas_angle_30': (dict(
+                scheme='rb3d',
+                pfreq=10,
+                kr=1e5,
+                fric_coeff=0.4,
+                timestep=5e-5,
+                tf=0.015,
+                contact_force_model='Mohseni_Vyas',
+                angle=30,
+                ), 'Mohseni Vyas angle 30'),
+
+            'Mohseni_angle_60': (dict(
+                scheme='rb3d',
+                pfreq=10,
+                kr=1e5,
+                fric_coeff=0.4,
+                timestep=5e-5,
+                tf=0.015,
+                contact_force_model='Mohseni',
[…]

### 2022-05-10 code/amaro_2019_collision_between_three_rigid_cubes.py

@@ -17,7 +17,7 @@ from pysph.sph.integrator import EPECIntegrator
 from pysph.solver.application import Application
 from pysph.sph.scheme import SchemeChooser
 
-from rigid_body_3d import RigidBody3DScheme
+from rigid_body_3d import (RigidBody3DScheme, get_files_at_given_times_from_log)
 from geometry import hydrostatic_tank_2d
 
 from pysph.examples.solid_mech.impact import add_properties
@@ -27,7 +27,7 @@ from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
 from pysph.tools.geometry import get_2d_block
 
 
-class RigidFluidCoupling(Application):
+class Amaro2019CollisionBetweenThreeRigidCubes(Application):
     def initialize(self):
         spacing = 0.01
         self.hdx = 1.3
@@ -73,10 +73,10 @@ class RigidFluidCoupling(Application):
                                    rho=self.body1_density,
                                    m_fluid=0.,
                                    rad_s=self.body_spacing / 2.,
+                                   E=15 * 1e6,
+                                   nu=0.3,
                                    constants={
-                                       'E': 69 * 1e9,
-                                       'poisson_ratio': 0.3,
-                                       'initial_spacing0': self.body_spacing,
+                                       'spacing0': self.body_spacing,
                                    })
         body_id = np.zeros(len(xb), dtype=int)
         dem_id = np.zeros(len(xb), dtype=int)
@@ -91,7 +91,7 @@ class RigidFluidCoupling(Application):
                               height=self.body_height)
         self.body2_density = 3. / 0.2**2.
         m = self.body2_density * self.body_spacing**self.dim
-        xb += max(body1.x) - min(xb) + 0.03
+        xb += max(body1.x) - min(xb) + 0.02
         yb -= min(body1.y) - min(yb) + 0.165 - 1. * self.body_spacing
         body2 = get_particle_array(name='body2',
                                    x=xb,
@@ -101,10 +101,10 @@ class RigidFluidCoupling(Application):
                                    rho=self.body2_density,
                                    m_fluid=0.,
                                    rad_s=self.body_spacing / 2.,
+                                   E=15 * 1e6,
+                                   nu=0.3,
                                    constants={
-                                       'E': 69 * 1e9,
[…]

### 2022-05-10 code/dinesh_2022_bouncing_cube_on_a_wall_2d.py

@@ -1,256 +1,540 @@
+"""Simulation of solid-fluid mixture flow using moving particle methods
+Shuai Zhang
+
+TODO: 1. Fix the dam such that the bottom layer is y - spacing/2.
+TODO: 2. Implement a simple 2d variant of rigid body collision.
 """
-Test the collision of two rigid bodues made of same particle array
-"""
+
+from __future__ import print_function
 import numpy as np
 
-from pysph.base.kernels import CubicSpline
-# from pysph.base.utils import get_particle_array_rigid_body
-from pysph.base.utils import get_particle_array
-from pysph.sph.integrator import EPECIntegrator
 from pysph.solver.application import Application
 from pysph.sph.scheme import SchemeChooser
 
-from rigid_fluid_coupling import RigidFluidCouplingScheme
-from geometry import hydrostatic_tank_2d
+from pysph.base.utils import (get_particle_array)
 
-from pysph.examples.solid_mech.impact import add_properties
-from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
-                                                               create_fluid,
-                                                               create_sphere)
-from pysph.tools.geometry import get_2d_block
+# from rigid_fluid_coupling import RigidFluidCouplingScheme
+from rigid_body_3d import RigidBody3DScheme
+from rigid_body_common import setup_damping_coefficient
+
+from pysph.tools.geometry import get_2d_block, get_2d_tank
 
 
-class Simulation1Dinesh2022BouncingCubeOnAWall2D(Application):
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
[…]

### 2022-05-10 code/dinesh_2022_rigid_bodies_collision_newtons_3rd_law_check_3d.py

@@ -1,0 +1,267 @@
+"""
+Amaro2019Improvement
+
+An improvement of rigid bodies contact for particle-based
+non-smooth walls modeling
+
+https://doi.org/10.1007/s40571-019-00233-4
+
+An implementation of collision of three rigid bodies.
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_body_3d import RigidBody3DScheme
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block, get_3d_block, rotate
+
+
+def get_rotated_3d_block(dx, length, height, depth, angle):
+    xb_tmp, yb_tmp = get_2d_block(dx=dx, length=length,
+                                  height=height)
+    xb, yb, _zs = rotate(xb_tmp, yb_tmp, np.zeros_like(xb_tmp),
+                         axis=np.array([0., 0., 1.]),
+                         angle=-angle)
+    x = np.array([])
+    y = np.array([])
+    z = np.array([])
+
+    z_linspace = np.arange(0., depth, dx)
+
+    for i in range(len(z_linspace)):
+        z1 = np.ones(len(xb), dtype=int) * z_linspace[i]
+        x = np.concatenate((x, xb))
+        y = np.concatenate((y, yb))
+        z = np.concatenate((z, z1))
+
+    return x, y, z
+
+
+class RigidFluidCoupling(Application):
+    def initialize(self):
+        spacing = 0.03
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 3
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2 - spacing/2.
+        self.body_length = 0.2 - spacing/2.
+        self.body_depth = 0.2 - spacing/2.
+        self.body_density = 2000
[…]

### 2022-05-10 code/dinesh_2022_two_circular_bodies_hitting_head_on.py

@@ -1,0 +1,156 @@
+"""
+Amaro2019Improvement
+
+An improvement of rigid bodies contact for particle-based
+non-smooth walls modeling
+
+https://doi.org/10.1007/s40571-019-00233-4
+
+An implementation of collision of three rigid bodies.
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_body_3d import (RigidBody3DScheme, get_files_at_given_times_from_log)
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class Dinesh2022TwoCircularBodiesHittingHeadOn(Application):
+    def initialize(self):
+        spacing = 0.01
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 3
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2 - spacing/2.
+        self.body_length = 0.2 - spacing/2.
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gy = 0.
+        self.dim = 2
+
+    def create_particles(self):
+        xb, yb = get_2d_block(dx=self.body_spacing,
+                              length=self.body_length,
+                              height=self.body_height)
+        self.body1_density = 1.5 / 0.2**2.
+        m = self.body1_density * self.body_spacing**self.dim
+        # left body
[…]

### 2022-05-10 code/mohseni_2021_controlled_sliding_on_a_flat_surface_2d.py

@@ -5,7 +5,7 @@ Including the Particle Shape Effect
 https://doi.org/10.3390/ma15010286
 
 
-3.3.2 Free sliding on a slope
+3.3.2 Controlled sliding on a flat surface
 
 """
 from __future__ import print_function
@@ -16,10 +16,8 @@ from pysph.sph.scheme import SchemeChooser
 
 from pysph.base.utils import (get_particle_array)
 
-from rigid_body_3d import RigidBody3DScheme
-from rigid_fluid_coupling import get_files_at_given_times_from_log
+from rigid_fluid_coupling import RigidFluidCouplingScheme
 from pysph.sph.equation import Equation, Group
-import os
 
 from pysph.tools.geometry import get_2d_block, get_2d_tank, rotate
 
@@ -167,12 +165,12 @@ class ApplyForceOnRigidBody(Equation):
             d_fx[d_idx] += d_tmp_tangential_force[0]
 
 
-class Mohseni2021FreeSlidingOnASlope(Application):
+class Mohseni2021ControlledSlidingOnAFlatSurface(Application):
     def initialize(self):
         self.dim = 2
         spacing = 1e-2
 
-        self.wall_length = 100.
+        self.wall_length = 40.
         self.wall_height = 0.
         self.wall_spacing = spacing
         self.wall_layers = 0
@@ -183,18 +181,14 @@ class Mohseni2021FreeSlidingOnASlope(Application):
         self.rigid_body_spacing = spacing
         self.rigid_body_rho = 2700
 
-        self.angle = 30.
-
         # simulation properties
         self.hdx = 1.5
         self.alpha = 0.1
-        self.gx = 0.
-        self.gy = -9.81
-        self.gz = 0.
+        self.gy = 0.
         self.h = self.hdx * self.rigid_body_spacing
 
         # solver data
-        self.tf = 3.
+        self.tf = 0.2
         self.dt = 1e-4
 
         # Rigid body collision related data
@@ -229,54 +223,10 @@ class Mohseni2021FreeSlidingOnASlope(Application):
 
         return x, y, body_id
 
-    def get_boundary_particles(self, no_bodies):
-        from boundary_particles import (get_boundary_identification_etvf_equations,
-                                        add_boundary_identification_properties)
-        from pysph.tools.sph_evaluator import SPHEvaluator
-        from pysph.base.kernels import (QuinticSpline)
-        # create a row of six cylinders
-        x, y, body_id = self.create_rigid_body()
-
[…]

### 2022-05-10 code/mohseni_2021_controlled_sliding_on_a_flat_surface_3d.py

@@ -1,0 +1,421 @@
+"""[1] Particle-Based Numerical Simulation Study of Solid Particle
+Erosion of Ductile Materials Leading to an Erosion Model,
+Including the Particle Shape Effect
+
+https://doi.org/10.3390/ma15010286
+
+
+3.3.2 Controlled sliding on a flat surface
+
+"""
+from __future__ import print_function
+import numpy as np
+
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from pysph.base.utils import (get_particle_array)
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from pysph.sph.equation import Equation, Group
+
+from pysph.tools.geometry import get_2d_block, get_3d_block, get_2d_tank, rotate
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+def create_circle(diameter=1, spacing=0.05, center=None):
+    radius = diameter/2.
+    xtmp, ytmp = get_2d_block(spacing, diameter+spacing, diameter+spacing)
+    x = []
+    y = []
+    for i in range(len(xtmp)):
+        dist = xtmp[i]**2. + ytmp[i]**2.
+        if dist < radius**2:
+            x.append(xtmp[i])
+            y.append(ytmp[i])
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
[…]

### 2022-05-10 code/mohseni_2021_free_sliding_on_a_slope_3d.py

@@ -16,8 +16,8 @@ from pysph.sph.scheme import SchemeChooser
 
 from pysph.base.utils import (get_particle_array)
 
-# from rigid_body_3d import RigidBody3DScheme
-from rigid_fluid_coupling import RigidFluidCouplingScheme
+from rigid_body_3d import RigidBody3DScheme
+from rigid_fluid_coupling import get_files_at_given_times_from_log
 from pysph.sph.equation import Equation, Group
 import os
 
@@ -173,7 +173,7 @@ class Mohseni2021FreeSlidingOnASlope(Application):
         spacing = 1e-2
 
         # x dimension
-        self.wall_length = 100.
+        self.wall_length = 10.
         # z dimension
         self.wall_height = 0.
         # y dimension
@@ -410,18 +410,14 @@ class Mohseni2021FreeSlidingOnASlope(Application):
         return [rigid_body, wall]
 
     def create_scheme(self):
-        rfc = RigidFluidCouplingScheme(rigid_bodies=['rigid_body'],
-                                       fluids=None,
-                                       boundaries=['wall'],
-                                       dim=self.dim,
-                                       rho0=1000.,
-                                       p0=1000 * 100,
-                                       c0=10.,
-                                       gy=self.gy,
-                                       nu=0.,
-                                       h=self.h)
-
-        s = SchemeChooser(default='rfc', rfc=rfc)
+        rb3d = RigidBody3DScheme(rigid_bodies=['rigid_body'],
+                                 boundaries=['wall'],
+                                 gx=0.,
+                                 gy=self.gy,
+                                 gz=0.,
+                                 dim=3,
+                                 fric_coeff=0.45)
+        s = SchemeChooser(default='rb3d', rb3d=rb3d)
         return s
 
     def create_equations(self):
@@ -439,31 +435,19 @@ class Mohseni2021FreeSlidingOnASlope(Application):
     def configure_scheme(self):
         tf = self.tf
 
-        self.scheme.configure_solver(dt=self.dt, tf=tf, pfreq=100)
-
-    # def post_step(self, solver):
-    #     t = solver.t
-    #     # dt = solver.dt
-    #     # T = self.wall_time
-    #     for pa in self.particles:
-    #         if pa.name == 'rigid_body':
-    #             t_1 = pa.normal_force_time[0]
-
-    #             if t <= t_1:
[…]

### 2022-05-10 code/qiu_2017_falling_solid_in_water_2d.py

@@ -14,6 +14,7 @@ from pysph.base.utils import (get_particle_array)
 
 # from rigid_body_3d import RigidBody3DScheme
 from rigid_fluid_coupling import RigidFluidCouplingScheme
+from rigid_fluid_coupling import get_files_at_given_times_from_log
 from pysph.sph.equation import Equation, Group
 import os
 from pysph.tools import geometry as G
@@ -423,68 +424,82 @@ class Qiu2017FallingSolidInWater2D(Application):
         # ========================
         # x amplitude figure
         # ========================
+
+        # ========================
         # generate plots
-        i = 0
-        output_files = get_files(fname)
+        # ========================
+        info = self.read_info(fname)
+        output_files = self.output_files
         output_times = np.array([0., 0.2, 0.3, 0.4])
+        logfile = os.path.join(
+            os.path.dirname(fname),
+            'qiu_2017_falling_solid_in_water_2d.log')
+        to_plot = get_files_at_given_times_from_log(output_files, output_times,
+                                                    logfile)
 
-        for sd, body, fluid, tank in iter_output(output_files, 'rigid_body', 'fluid', 'tank'):
-            _t = sd['t']
-            # if _t in output_times:
-            if _t in output_times:
-                s = 0.2
-                # print(_t)
-                fig, axs = plt.subplots(1, 1)
-                axs.scatter(body.x, body.y, s=s, c=body.m)
-                # axs.grid()
-                axs.set_aspect('equal', 'box')
-                # axs.set_title('still a circle, auto-adjusted data limits', fontsize=10)
+        for i, f in enumerate(to_plot):
+            # print(i, f)
+            data = load(f)
+            t = data['solver_data']['t']
+            tank = data['arrays']['tank']
+            fluid = data['arrays']['fluid']
+            rigid_body = data['arrays']['rigid_body']
 
-                tank_x = tank.x
-                tank_y = tank.y
-                tank_m = tank.m
+            s = 0.2
+            # print(_t)
+            fig, axs = plt.subplots(1, 1)
+            axs.scatter(fluid.x, fluid.y, s=s, c=fluid.p)
+            axs.scatter(tank.x, tank.y, s=s, c=tank.m)
+            # axs.grid()
+            axs.set_aspect('equal', 'box')
+            # axs.set_title('still a circle, auto-adjusted data limits', fontsize=10)
 
-                tmp = axs.scatter(tank_x, tank_y, s=s, c=tank_m)
[…]

### 2022-05-10 code/qiu_2017_falling_solid_in_water_3d.py

@@ -350,7 +350,9 @@ class Qiu2017FallingSolidInWater3D(Application):
     def configure_scheme(self):
         tf = self.tf
 
-        self.scheme.configure_solver(dt=self.dt, tf=tf, pfreq=100)
+        output_at_times = np.array([0., 0.2, 0.3, 0.4])
+        self.scheme.configure_solver(dt=self.dt, tf=tf, pfreq=100,
+                                     output_at_times=output_at_times)
 
     # def post_step(self, solver):
     #     t = solver.t

### 2022-05-10 code/rigid_body_common.py

@@ -219,6 +219,8 @@ def setup_damping_coefficient(body, rigid_bodies, boundaries=[]):
             for j, k in zip(range(max(src.body_id)+1), range(l1, l2)):
                 t1 = body.total_mass[i] * src.total_mass[j]
                 t2 = body.total_mass[i] + src.total_mass[j]
+                # t1 = body.m[0] * src.m[0]
+                # t2 = body.m[0] + src.m[0]
                 m_star = t1 / t2
 
                 idx = i * body.total_no_bodies[0]
@@ -231,7 +233,8 @@ def setup_damping_coefficient(body, rigid_bodies, boundaries=[]):
         for src in boundaries:
             idx = i * body.total_no_bodies[0]
             dem_id = src.dem_id[0]
-            m_star = body.total_mass[i]
+            # m_star = body.m[0]
+            m_star = body.total_mass[0]
             t1 = log(body.coeff_of_rest[idx+dem_id])
             t2 = t1**2. + M_PI**2.
             tmp = (m_star / t2)**0.5
@@ -999,6 +1002,268 @@ class ComputeContactForce(Equation):
 
                     lt_magn = (modified_delta_lt_x**2. + modified_delta_lt_y**2. +
                                modified_delta_lt_z**2.)**0.5
+
+                    d_delta_lt_x[t2] = modified_delta_lt_x / lt_magn
+                    d_delta_lt_y[t2] = modified_delta_lt_y / lt_magn
+                    d_delta_lt_z[t2] = modified_delta_lt_z / lt_magn
+
+                    # repulsive force
+                    d_fn_x[t2] = fn_x
+                    d_fn_y[t2] = fn_y
+                    d_fn_z[t2] = fn_z
+
+            else:
+                d_overlap[t2] = 0.
+                d_ft_x[t2] = 0.
+                d_ft_y[t2] = 0.
+                d_ft_z[t2] = 0.
+                # reset the spring length
+                d_delta_lt_x[t2] = 0.
+                d_delta_lt_y[t2] = 0.
+                d_delta_lt_z[t2] = 0.
+
+                # reset the normal force
+                d_fn_x[t2] = 0.
+                d_fn_y[t2] = 0.
+                d_fn_z[t2] = 0.
+
+            # add the force
+            d_fx[d_idx] += d_fn_x[t2] + d_ft_x[t2]
+            d_fy[d_idx] += d_fn_y[t2] + d_ft_y[t2]
[…]

### 2022-05-10 code/rigid_fluid_coupling.py

@@ -42,10 +42,37 @@ from rigid_body_common import (add_properties_stride,
                                ComputeContactForceDistanceAndClosestPoint,
                                ComputeContactForce)
 
+from contact_force_mohseni_vyas import (
+    ComputeContactForceNormalsMV,
+    ComputeContactForceDistanceAndClosestPointAndWeightDenominatorMV,
+    ComputeContactForceMV,
+    TransferContactForceMV)
+
 # compute the boundary particles
 from boundary_particles import (get_boundary_identification_etvf_equations,
                                 add_boundary_identification_properties)
 from numpy import sin, cos
+
+
+def get_files_at_given_times_from_log(files, times, logfile):
+    import re
+    result = []
+    time_pattern = r"output at time\ (\d+(?:\.\d+)?)"
+    file_count, time_count = 0, 0
+    with open(logfile, 'r') as f:
+        for line in f:
+            if time_count >= len(times):
+                break
+            t = re.findall(time_pattern, line)
+            if t:
+                if float(t[0]) in times:
+                    result.append(files[file_count])
+                    time_count += 1
+                elif float(t[0]) > times[time_count]:
+                    result.append(files[file_count])
+                    time_count += 1
+                file_count += 1
+    return result
 
 
 class ClampWallPressure(Equation):
@@ -749,16 +776,17 @@ class RigidFluidCouplingScheme(Scheme):
             g5 = []
             for name in self.rigid_bodies:
                 g5.append(
-                    ComputeContactForceNormals(dest=name,
-                                               sources=self.rigid_bodies+self.boundaries))
+                    ComputeContactForceNormalsMV(
+                        dest=name,
+                        sources=self.rigid_bodies+self.boundaries))
 
             stage2.append(Group(equations=g5, real=False))
 
             g5 = []
             for name in self.rigid_bodies:
                 g5.append(
-                    ComputeContactForceDistanceAndClosestPoint(
-                        dest=name, sources=self.rigid_bodies+self.boundaries))
+                    ComputeContactForceDistanceAndClosestPointAndWeightDenominatorMV
+                    (dest=name, sources=self.rigid_bodies+self.boundaries))
             stage2.append(Group(equations=g5, real=False))
 
         if len(self.rigid_bodies) > 0:
@@ -775,17 +803,24 @@ class RigidFluidCouplingScheme(Scheme):
             g5 = []
             for name in self.rigid_bodies:
                 g5.append(
-                    ComputeContactForce(dest=name,
-                                        sources=None,
-                                        kr=self.kr,
[…]

### 2022-05-10 code/stack_of_cylinders.py

@@ -120,7 +120,7 @@ class ZhangStackOfCylinders(Application):
 
         # solver data
         self.tf = 0.5 + self.wall_time
-        self.dt = 5e-5
+        self.dt = 1e-5
 
         # Rigid body collision related data
         self.limit = 6
@@ -140,10 +140,10 @@ class ZhangStackOfCylinders(Application):
                                        h=h,
                                        m=m,
                                        rad_s=rad_s,
+                                       E=69 * 1e9,
+                                       nu=0.3,
                                        constants={
-                                           'E': 69 * 1e9,
-                                           'poisson_ratio': 0.3,
-                                           'initial_spacing0': self.cylinder_spacing,
+                                           'spacing0': self.cylinder_spacing,
                                        })
         cylinders.add_property('dem_id', type='int', data=dem_id)
         cylinders.add_property('body_id', type='int', data=body_id)
@@ -162,10 +162,8 @@ class ZhangStackOfCylinders(Application):
                                  m=m,
                                  rad_s=self.dam_spacing / 2.,
                                  name="dam",
-                                 constants={
-                                     'E': 30 * 1e8,
-                                     'poisson_ratio': 0.3,
-                                 })
+                                 E=30*1e8,
+                                 nu=0.3)
         dam.add_property('dem_id', type='int', data=max(body_id) + 1)
 
         # create wall with normals
@@ -183,10 +181,12 @@ class ZhangStackOfCylinders(Application):
                                   m=m,
                                   rad_s=self.cylinder_spacing / 2.,
                                   name="wall",
-                                  constants={
-                                      'E': 30 * 1e8,
-                                      'poisson_ratio': 0.3,
-                                  })
+                                  E=30*1e8,
+                                  nu=0.3)
+                                  # constants={
+                                  #     'E': 30 * 1e8,
+                                  #     'poisson_ratio': 0.3,
+                                  # })
         wall.add_property('dem_id', type='int', data=max(body_id) + 2)
 
         self.scheme.setup_properties([cylinders, dam, wall])
@@ -232,6 +232,8 @@ class ZhangStackOfCylinders(Application):
                                 dtype=float) * 0.6
         cylinders.add_constant('coeff_of_rest', coeff_of_rest)
[…]

### 2022-05-11 manuscript/paper.tex
Add cylinder rolling benchmark.

@@
 \FloatBarrier%
+\subsection{Cylinder rolling on an inclined plane}
+\label{sec:cylinder-rolling-on-an-inclined-plane}
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/de_2021_cylinder_rolling_on_an_inclined_plane_2d/fric_coeff_0_3/xcom_vs_time}
+  \caption{x com vs time of a cylinder with a friction coefficient of $0.3$.}
+\label{fig:cylinder-xcom-vs-time-fric-0-3}
+\end{figure}
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/de_2021_cylinder_rolling_on_an_inclined_plane_2d/fric_coeff_0_6/xcom_vs_time}
+  \caption{x com vs time of a cylinder with a friction coefficient of $0.6$.}
+\label{fig:cylinder-xcom-vs-time-fric-0-6}
+\end{figure}
+
+\FloatBarrier%
 \subsection{Three bodies colliding}

### 2022-05-11 automate.py

@@ -845,6 +845,8 @@ class Mohseni2021FreeSlidingOnASlope2D(Problem):
         self.case_info = {
             'fric_coeff_0_2': (dict(
                 scheme='rb3d',
+                contact_force_model='Mohseni_Vyas',
+                linear_contact_force=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=0.2,
@@ -853,6 +855,8 @@ class Mohseni2021FreeSlidingOnASlope2D(Problem):
 
             'fric_coeff_0_4': (dict(
                 scheme='rb3d',
+                contact_force_model='Mohseni_Vyas',
+                linear_contact_force=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=0.4,
@@ -861,6 +865,8 @@ class Mohseni2021FreeSlidingOnASlope2D(Problem):
 
             'fric_coeff_tan_30': (dict(
                 scheme='rb3d',
+                contact_force_model='Mohseni_Vyas',
+                linear_contact_force=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=np.tan(np.pi/6),
@@ -869,6 +875,8 @@ class Mohseni2021FreeSlidingOnASlope2D(Problem):
 
             'fric_coeff_0_6': (dict(
                 scheme='rb3d',
+                contact_force_model='Mohseni_Vyas',
+                linear_contact_force=None,
                 pfreq=300,
                 kr=1e5,
                 fric_coeff=0.6,
@@ -945,6 +953,8 @@ class Mohseni2021FreeSlidingOnASlope3D(Problem):
         self.case_info = {
             'fric_coeff_0_2': (dict(
                 scheme='rb3d',
+                contact_force_model='Mohseni_Vyas',
+                linear_contact_force=None,
                 pfreq=500,
                 kr=1e5,
                 fric_coeff=0.2,
@@ -953,6 +963,8 @@ class Mohseni2021FreeSlidingOnASlope3D(Problem):
 
             'fric_coeff_0_4': (dict(
                 scheme='rb3d',
+                contact_force_model='Mohseni_Vyas',
+                linear_contact_force=None,
                 pfreq=500,
                 kr=1e5,
                 fric_coeff=0.4,
@@ -961,6 +973,8 @@ class Mohseni2021FreeSlidingOnASlope3D(Problem):
 
             'fric_coeff_tan_30': (dict(
                 scheme='rb3d',
+                contact_force_model='Mohseni_Vyas',
[…]

### 2022-05-11 code/mohseni_2021_free_sliding_on_a_slope_2d.py

@@ -16,8 +16,7 @@ from pysph.sph.scheme import SchemeChooser
 
 from pysph.base.utils import (get_particle_array)
 
-from rigid_body_3d import RigidBody3DScheme
-from rigid_fluid_coupling import get_files_at_given_times_from_log
+from rigid_body_3d import RigidBody3DScheme, get_files_at_given_times_from_log
 from pysph.sph.equation import Equation, Group
 import os
 
@@ -247,11 +246,11 @@ class Mohseni2021FreeSlidingOnASlope(Application):
                                 m=m,
                                 rho=self.rigid_body_rho,
                                 rad_s=rad_s,
+                                E=69 * 1e9,
+                                nu=0.3,
                                 constants={
-                                    'E': 69 * 1e9,
-                                    'poisson_ratio': 0.3,
                                     'spacing0': self.rigid_body_spacing,
-                                    })
+                                })
 
         add_boundary_identification_properties(pa)
         # make sure your rho is not zero
@@ -289,9 +288,9 @@ class Mohseni2021FreeSlidingOnASlope(Application):
                                         m=m,
                                         rho=self.rigid_body_rho,
                                         rad_s=rad_s,
+                                        E=69 * 1e9,
+                                        nu=0.3,
                                         constants={
-                                            'E': 69 * 1e9,
-                                            'poisson_ratio': 0.3,
                                             'spacing0': self.rigid_body_spacing,
                                         })
         rigid_body.add_property('dem_id', type='int', data=dem_id)
@@ -351,10 +350,9 @@ class Mohseni2021FreeSlidingOnASlope(Application):
                                   rho=self.rigid_body_rho,
                                   rad_s=rad_s,
                                   contact_force_is_boundary=contact_force_is_boundary,
-                                  constants={
-                                      'E': 69 * 1e9,
-                                      'poisson_ratio': 0.3,
-                                  })
+                                  E=69 * 1e9,
+                                  nu=0.3)
+
         wall.add_property('dem_id', type='int', data=max(body_id) + 1)
         # remove particles outside the circle
         indices = []

### 2022-05-11 code/rigid_body_3d.py

@@ -25,7 +25,7 @@ from rigid_body_common import (add_properties_stride,
                                set_body_frame_position_vectors,
                                set_body_frame_normal_vectors,
                                set_moment_of_inertia_and_its_inverse,
-                               BodyForce, SumUpExternalForces,
+                               ResetForce, SumUpExternalForces,
                                normalize_R_orientation,
                                ComputeContactForceNormals,
                                ComputeContactForceDistanceAndClosestPoint,
@@ -672,7 +672,7 @@ class RigidBody3DScheme(Scheme):
                           help='Use nonlinear contact force model')
 
         add_bool_argument(group, 'linear-contact-force', dest='linear_contact_force',
-                          default=False,
+                          default=True,
                           help='Use linear contact force model')
 
         choices = ['Mohseni', 'Mohseni_Vyas']
@@ -710,11 +710,7 @@ class RigidBody3DScheme(Scheme):
             g5 = []
             for name in self.rigid_bodies:
                 g5.append(
-                    BodyForce(dest=name,
-                              sources=None,
-                              gx=self.gx,
-                              gy=self.gy,
-                              gz=self.gz))
+                    ResetForce(dest=name, sources=None))
             stage2.append(Group(equations=g5, real=False))
 
         if self.contact_force_model == 'Mohseni':
@@ -794,7 +790,11 @@ class RigidBody3DScheme(Scheme):
         if len(self.rigid_bodies) > 0:
             g6 = []
             for name in self.rigid_bodies:
-                g6.append(SumUpExternalForces(dest=name, sources=None))
+                g6.append(SumUpExternalForces(dest=name,
+                                              sources=None,
+                                              gx=self.gx,
+                                              gy=self.gy,
+                                              gz=self.gz))
 
             stage2.append(Group(equations=g6, real=False))
 

### 2022-05-11 code/rigid_body_common.py

@@ -112,20 +112,21 @@ def set_body_frame_normal_vectors(pa):
     pa.normal0[:] = pa.normal[:]
 
 
-class BodyForce(Equation):
-    def __init__(self, dest, sources, gx=0.0, gy=0.0, gz=0.0):
-        self.gx = gx
-        self.gy = gy
-        self.gz = gz
-        super(BodyForce, self).__init__(dest, sources)
-
-    def initialize(self, d_idx, d_m, d_fx, d_fy, d_fz):
-        d_fx[d_idx] = d_m[d_idx] * self.gx
-        d_fy[d_idx] = d_m[d_idx] * self.gy
-        d_fz[d_idx] = d_m[d_idx] * self.gz
+class ResetForce(Equation):
+    def initialize(self, d_idx, d_fx, d_fy, d_fz):
+        d_fx[d_idx] = 0.
+        d_fy[d_idx] = 0.
+        d_fz[d_idx] = 0.
 
 
 class SumUpExternalForces(Equation):
+    def __init__(self, dest, sources,
+                 gx=0.0, gy=0.0, gz=0.0):
+        self.gx = gx
+        self.gy = gy
+        self.gz = gz
+        super(SumUpExternalForces, self).__init__(dest, sources)
+
     def reduce(self, dst, t, dt):
         frc = declare('object')
         trq = declare('object')
@@ -136,6 +137,7 @@ class SumUpExternalForces(Equation):
         y = declare('object')
         z = declare('object')
         xcm = declare('object')
+        total_mass = declare('object')
         body_id = declare('object')
         j = declare('int')
         i = declare('int')
@@ -150,6 +152,7 @@ class SumUpExternalForces(Equation):
         y = dst.y
         z = dst.z
         xcm = dst.xcm
+        total_mass = dst.total_mass
         body_id = dst.body_id
 
         frc[:] = 0
@@ -173,6 +176,13 @@ class SumUpExternalForces(Equation):
             trq[i3] += (dy * fz[j] - dz * fy[j])
             trq[i3 + 1] += (dz * fx[j] - dx * fz[j])
             trq[i3 + 2] += (dx * fy[j] - dy * fx[j])
+
+        # add body force
+        for i in range(max(body_id) + 1):
+            i3 = 3 * i
+            frc[i3] += total_mass[i] * self.gx
+            frc[i3 + 1] += total_mass[i] * self.gy
+            frc[i3 + 2] += total_mass[i] * self.gz
 
 
 def normalize_R_orientation(orien):

### 2022-05-23 manuscript/paper.tex
Add controlled sliding case. Automated many examples.

@@
 \begin{abstract}
+  In this paper, a new particle-based fluid–rigid-body interaction schemes are
+  utilised to model violent free-surface flow problems. A variant of Discrete
+  element method (DEM), surface aware DEM (SADEM) is proposed to handle the
+  contact between irregular bodies, while the fluid phase is modeled using
+  corrected transport velocity formulation (CTVF) of smoothed particle
+  hydrodynamics (SPH). The accuracy the SADEM-CTVF framework are evaluated via
+  several numerical examples involving both analytical and experimental.
+  Surface aware DEM is validated using using numerical examples including: (1)
+  A free and controlled sliding of a cube, (2) A 2d rolling disc. Further, an
+  experimental benchmark, collapse of a stack of cylinders in a dam under
+  gravity is considered, three rigid bodies hitting. While the coupling method
+  is validated by modeling (1) water-entry of a sphere, (2) 3d dam breaking
+  flow hitting stacked cubes. The results indicate that the current method can
+  effectively model irregular bodies in a fluid flow.
 \end{abstract}
@@
   of problems do they give rise to? Ice-Sea? Debris?
-\item Many different ways RFC is been modeled, this includes mesh based and
-  mess less. Explain in a good detail what meshless methods are out there
-  which handles these problems. This includes SPH too.
+\item Why is it hard to model rigid fluid coupling? Then we say numerically
+  nonlinear, and this is how it is been into handled. Many different ways RFC
+  is been modeled, this includes mesh based and messless. Explain in a good
+  detail what meshless methods are out there which handles these problems.
+  This includes SPH too. (Same as next point)
+\item \todoin{Done} Describe some works where Rigid fluid coupling is handled
+  in meshless methods. MPS-DEM, SPH-DEM and other ways, recently Asai. (Same
+  as previous point)
 \item Explain SPH history and its applications in different areas. Now SPH
@@
   adaptive formulation, where the author captures the cavity.
-\item Similarly explain the many ways the rigid-rigid coupling is been
+\item \todoin{Done} Similarly explain the many ways the rigid-rigid coupling is been
   handled. Detail how non-smooth boundaries are handled.
-\item Mention the open source software which provide SPH formulation (there are 2.)
-\item Explain what we are going to do in the current work. We adapt the
+\item \todoin{Done} Explain what we are going to do in the current work. We adapt the
   Mohseni formulation to handle the non-smooth boundaries, we also incorporate
@@
   falling in water, then 3d dam break over dynamics rigid obstacles.
+% \item Mention the open source software which provide SPH formulation (there are 2.)
 \end{itemize}
+
+\textbf{Random points to be included later}.
+\begin{itemize}
+\item In the context of modeling the rigid fluid coupling by assuming both of
+  them as particles and, these are the few papers. The more relevant concern
+  the generalization of the fundamental technique of Koshizuka et al. [6] and
+  the inclusion of a state-of-the-art Distributed Contact DEM (DCDEM)
+  formulation, similar in concept to those employed by both Zhang et al. [14]
+  and Ren et al. [15]. A delta -SPH [16] term is added to the continuity equation,
+  controlling the density field fluctuations and contributing for the
+  mitigation of known solid–fluid interface deficiencies [17], particularly
+  the development of a hydrophobic area that results in a reorganization of
+  the fluid particle positions.The current work
+\item A one way coupling is done by xxxx. Then an semi empirical model is used
+  to find the force on the discrete elements by stokes law or other laws. Then
+  a two way coupling is introduced by Zhang, also Monaghan did the same
+  approach.
+\end{itemize}
+
+\textbf{1st bullet point of introduction}. Irregular bodies are modeled using
+many different variations now, one of the methods is by overlapped sphere
+method \cite{das2007modeling}, SMR-DEM by \citet{zhan2021surface}, dilated
+polyhedral DEM \citet{liu2020new}, Fourier series-based discrete element
+method \citet{lai2020fourier}, non-smooth wall modeling by
+\citet{amaro2019improvement}, GJK-DEM, DFR-DEM. In the current work we have
+extended the contact force model proposed by \citet{mohseni2021particle} to
+handle three dimensional problems, we also incorporate the damping model.
+
+\textbf{5th bullet point of introduction}. Irregular bodies are modeled using
+many different variations now, one of the methods is by overlapped sphere
+method \cite{das2007modeling}, SMR-DEM by \citet{zhan2021surface}, dilated
+polyhedral DEM \citet{liu2020new}, Fourier series-based discrete element
+method \citet{lai2020fourier}, non-smooth wall modeling by
+\citet{amaro2019improvement}, GJK-DEM, DFR-DEM. In the current work we have
+extended the contact force model proposed by \citet{mohseni2021particle} to
+handle three dimensional problems, we also incorporate the damping model.
+
+\textbf{6th bullet point of introduction}. Numerical examples, collision of
+three cubes is initially used to test the conservation property of the current
+contact mode while dealing with non-smooth boundaries. Further, a free and
+forced sliding of a 3d cube on a frictional inclined plane, and a rolling
+cylinder whose analytical solutions exists are utilised to validate the
+rigid-rigid contact model frictional model. A granular collapse of a stack of
+cylinders is modeled and compared against the experimental results. In order
+to validate the two-way rigid fluid coupled scheme a rigid circular body
+falling in a steady tank is simulated. Complex interactions of fluid in a 3D
+dam breaking with multiple rigid bodies, is studied and compared with the
+experimental results of SPH-DCDEM.
 
@@
 \label{sec:rbd}
+
+% check \cite{natsui2018sph}
 
@@
 
-\subsection{3D Bouncing cube on a wall under gravity}
-\label{sec:bouncing-cube}
+% \subsection{3D Bouncing cube on a wall under gravity}
+% \label{sec:bouncing-cube}
 
@@
 
-In the current section we test the frictional part of the current solver by
-modeling the sliding of a rigid body on an inclined surface in 3D. We compare
-against the analytical solution to validate the test case.
+\begin{itemize}
+\item Give details of gravity in schematic
+\end{itemize}
+
+In the current section we model free sliding of rigid cube on an inclined
+frictional plane. The frictional part of the current solver by is validated
+through this test. We consider both 2d and 3d case. The velocity of the center
+of mass of the cube is compared against the analytical solution for
+quantitative validation. The schematic is shown is figure
 
@@
 
+\subsubsection{2D sliding}
+\label{sec:results-2d-sliding}
+
+\Cref{fig:mohseni-2021-sliding-2d} shows the snapshots of the rigid body at
+three time instants. From \cref{fig:mohseni-2021-sliding-2d} we can see that
+the the body is freely sliding with out having any oscillations or unphysical
+jumping off the inclined wall. This is because of the new surface aware
+contact model as force is not computed by considering the wall as spherical
+particles but by ensemble of an overlap. The snapshots correspond to a
+friction coefficient of $0.2$.
+\Cref{fig:results-solid-sliding-velocity-vs-time-2d} shows a evolution of
+velocity of the center of mass of the rigid body for different frictional
+coefficients against the analytical solution. From
+\Cref{fig:results-solid-sliding-velocity-vs-time-2d} we can see that the current
+solver has an excellent match with the analytical solution and covers all the
+regimes of the sliding case.
+
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_2d/fric_coeff_0_2/time0}
+    \subcaption{t = $0$ s}\label{fig:passing-0}
+  \end{subfigure}
+  %
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_2d/fric_coeff_0_2/time1}
+    \subcaption{t = $0.5$ s}\label{fig:passing-1}
+  \end{subfigure}
+
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_2d/fric_coeff_0_2/time2}
+    \subcaption{t = $1$ s}\label{fig:passing-2}
+  \end{subfigure}
+  \caption{Rigid body with friction $0.2$ sliding.}
+\label{fig:mohseni-2021-sliding-2d}
+\end{figure}
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_2d/velocity_vs_time}
+  \caption{Velocity versus time}
+\label{fig:results-solid-sliding-velocity-vs-time-2d}
+\end{figure}
+
+\subsubsection{3D sliding}
+\label{sec:results-3d-sliding}
+
 \Cref{fig:mohseni-2021-sliding-3d} shows the snapshots of the rigid body at 4
@@
 as force is not computed by considering the wall as spherical particles but by
-ensemble of an overlap. The snapshots correspond to a friction coefficient of $0.4$.
+ensemble of an overlap. The snapshots correspond to a friction coefficient of
+$0.4$. \Cref{fig:results-solid-sliding-velocity-vs-time-3d} shows a evolution of
+velocity of the center of mass of the rigid body for different frictional
+coefficients against the analytical solution. From
+\Cref{fig:results-solid-sliding-velocity-vs-time-3d} we can see that the current
+solver has an excellent match with the analytical solution and covers all the
+regimes of the sliding case.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.6\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Velocity versus time}
+\label{fig:results-solid-sliding-velocity-vs-time-3d}
+\end{figure}
 
@@
 
-\Cref{fig:results-solid-sliding-velocity-vs-time} shows a evolution of
-velocity of the center of mass of the rigid body for different frictional
-coefficients against the analytical solution. From
-\Cref{fig:results-solid-sliding-velocity-vs-time} we can see that the current
-solver has an excellent match with the analytical solution and covers all the
-regimes of the sliding case.
-
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
-  \caption{Velocity versus time}
-\label{fig:results-solid-sliding-velocity-vs-time}
-\end{figure}
-
 \FloatBarrier%
@@
 
-In the current section we control a rigid body to slide on a frictional flat
-surface by applying an external normal $F_n$ and tangential force $F_t$. The
-friction coefficient between the body and wall is assumed to be $0.5$. The
-schematic of the rigid body as well as the wall is shown in
-\cref{fig:schematic-controlled-rigid-body-sliding}.
-\begin{figure}[!htpb]
-  \centering
-  % \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
-  \caption{Schematic of the controlled rigid body sliding}
-\label{fig:schematic-controlled-rigid-body-sliding}
-\end{figure}
-
-\Cref{fig:velocity-vs-time-controlled-sliding} depicts the time histories of
-velocity of the center of mass of the rigid body with time, as well as the
-variation of applied external normal $F_n$ and tangential $F_t$ forces.
 \begin{itemize}
@@
 \end{itemize}
-\begin{figure}[!htpb]
-  \centering
-  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+
+In the current section we control a rigid body to slide on a frictional flat
+surface by applying an external normal $F_n$ and tangential force $F_t$. The
+friction coefficient between the body and wall is assumed to be $0.5$. The
+schematic of the rigid body as well as the wall is shown in
+\cref{fig:schematic-controlled-rigid-body-sliding}.
+\begin{figure}[!htpb]
+  \centering
+  % \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \caption{Schematic of the controlled rigid body sliding}
+\label{fig:schematic-controlled-rigid-body-sliding}
+\end{figure}
+
+\Cref{fig:velocity-vs-time-controlled-sliding} depicts the time histories of
+velocity of the center of mass of the rigid body with time, as well as the
+variation of applied external normal $F_n$ and tangential $F_t$ forces.
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/mohseni_2021_controlled_sliding_on_a_flat_surface_2d/case_1/force_velocity_vs_t}
   \caption{Velocity vs time of the rigid slider}
@@
 \label{sec:cylinder-rolling-on-an-inclined-plane}
+
+\todoin{Status: Done (Except add the particle plots)}
+
+A cylinder of diameter $1.0$ m is allowed to roll on an inclined plane under
+gravity. The physical model is shown in \cref{fig:circular-body:schematic-1},
+while the computational model is in \cref{fig:circular-body:schematic-2}. In
+the computational model the $x$-axis points in the direction of the slope,
+while the gravity makes an angle $\theta$ with the vertical. The material
+properties and the numerical parameters are given in
+\cref{tab:circular-body-rolling-params}. A total of two friction coefficients
+are simulated for, and for the quantitative validation center of mass of the
+cylinder is considered, whose analytical expression is given as
+\begin{align}
+  \label{eq:analytical-x-cm-rolling-cylinder}
+  x_{cm}(t) =
+  \begin{cases}
+  x_0 + \frac{1}{2} \, g \, t^2 \, (\sin(\theta) - \mu \cos(\theta)) & \tan{\theta} > 3.5\mu,\\
+  x_0 + \frac{1}{3} \, g \, t^2 \, \sin(\theta) & \tan{\theta} \leq 3.5\mu.
+\end{cases}
+\end{align}
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{images/de_2021_cylinder_rolling_on_an_inclined_plane/schematic_1}
+    \subcaption{}\label{fig:circular-body:schematic-1}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{images/de_2021_cylinder_rolling_on_an_inclined_plane/schematic_2}
+    \subcaption{}\label{fig:circular-body:schematic-2}
+  \end{subfigure}
+  \caption{Curved interface}
+\label{fig:circular-body-schematic}
+\end{figure}
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}[!ht]{ll}
+    \toprule
+    Quantity & Values\\
+    \midrule
+    $\rho$, density & $2700$ kg\,m\textsuperscript{-3} \\
+    $\mu$, friction coefficient & $0.3$ \& $0.6$ \\
+    Time of simulation & $0.6$ s \\
+    Resolution, $\delta x$ & $0.0025$ m\\
+    Smoothing length factor, $h/\Delta x$ & 1\\
+    gravity $[g_x, g_y, g_z]$ & $[g\,\sin(\theta), g\,\cos(\theta), 0.0]$\\
+    $k_r$, Repulsive stiffness coefficient & $1e7$ \\
+    $k_f$, Repulsive stiffness coefficient & $1e5$ \\
+    $\alpha_{damp}$ & FIXME\\
+    \bottomrule
+  \end{tabular}
+  \caption{Material properties and numerical parameters used for the rolling
+    of cylinder on an inclined surface.}%
+  \label{tab:circular-body-rolling-params}
+\end{table}
+
+\Cref{fig:cylinder-xcom-vs-time-fric-0-3} and
+\cref{fig:cylinder-xcom-vs-time-fric-0-3} depicts the variation of center of
+mass of the cylinder with time for a friction coefficients of $0.3$ and $0.6$.
+From both the figures we can see that the center of mass predicted by the
+current solver is at an excellent agreement with the exact solution. Further
+\todo{put the right figure} \cref{fig:cylinder-xcom-vs-time-fric-0-3} shows
+the snapshots of the cylinder at different time stamps, from which we can see
+that the current scheme is stable.
 
@@
   % \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
-  \caption{Schematic of the controlled rigid body sliding}
-\label{fig:schematic-controlled-rigid-body-sliding}
+  \caption{Schematic of the three rigid body colliding}
+\label{fig:schematic-three-rigid-bodies-colliding}
 \end{figure}
@@
 \FloatBarrier%
-\subsection{Floating solid in water}
-\label{sec:floating-solid-in-water}
-
-\FloatBarrier%
 \subsection{3D dam breaking flow hitting cubes}

### 2022-05-23 code/mohseni_2021_controlled_sliding_on_a_flat_surface_2d.py

@@ -16,7 +16,7 @@ from pysph.sph.scheme import SchemeChooser
 
 from pysph.base.utils import (get_particle_array)
 
-from rigid_fluid_coupling import RigidFluidCouplingScheme
+from rigid_body_3d import RigidBody3DScheme, get_files_at_given_times_from_log
 from pysph.sph.equation import Equation, Group
 
 from pysph.tools.geometry import get_2d_block, get_2d_tank, rotate
@@ -239,9 +239,9 @@ class Mohseni2021ControlledSlidingOnAFlatSurface(Application):
                                         m=m,
                                         rho=self.rigid_body_rho,
                                         rad_s=rad_s,
+                                        E=69 * 1e9,
+                                        nu=0.3,
                                         constants={
-                                            'E': 69 * 1e9,
-                                            'poisson_ratio': 0.3,
                                             'spacing0': self.rigid_body_spacing,
                                         })
         rigid_body.add_property('dem_id', type='int', data=dem_id)
@@ -287,10 +287,8 @@ class Mohseni2021ControlledSlidingOnAFlatSurface(Application):
                                   rho=self.rigid_body_rho,
                                   rad_s=rad_s,
                                   contact_force_is_boundary=contact_force_is_boundary,
-                                  constants={
-                                      'E': 69 * 1e9,
-                                      'poisson_ratio': 0.3,
-                                  })
+                                  E=69 * 1e9,
+                                  nu=0.3)
         max_dem_id = max(dem_id)
         wall.add_property('dem_id', type='int', data=max_dem_id + 1)
 
@@ -309,18 +307,14 @@ class Mohseni2021ControlledSlidingOnAFlatSurface(Application):
         return [rigid_body, wall]
 
     def create_scheme(self):
-        rfc = RigidFluidCouplingScheme(rigid_bodies=['rigid_body'],
-                                       fluids=None,
-                                       boundaries=['wall'],
-                                       dim=2,
-                                       rho0=1000.,
-                                       p0=1000 * 100,
-                                       c0=10.,
-                                       gy=self.gy,
-                                       nu=0.,
-                                       h=self.h)
-
-        s = SchemeChooser(default='rfc', rfc=rfc)
[…]

### 2022-05-23 code/mohseni_2021_free_sliding_on_a_slope_2d.py

@@ -425,7 +425,7 @@ class Mohseni2021FreeSlidingOnASlope(Application):
     def configure_scheme(self):
         tf = self.tf
 
-        output_at_times = np.array([0., 0.5, 1.0, 2.0])
+        output_at_times = np.array([0., 0.5, 1.0])
         self.scheme.configure_solver(dt=self.dt, tf=tf, pfreq=500,
                                      output_at_times=output_at_times)
 
@@ -498,23 +498,22 @@ class Mohseni2021FreeSlidingOnASlope(Application):
         # x amplitude figure
         # ========================
         # generate plots
-        output_files = get_files(fname)
-        output_times = np.array([0., 5 * 1e-1, 1. * 1e-0,  2. * 1e-0])
+        info = self.read_info(fname)
+        output_files = self.output_files
+        output_times = np.array([0., 5 * 1e-1, 1. * 1e-0])
         logfile = os.path.join(os.path.dirname(fname), 'mohseni_2021_free_sliding_on_a_slope_2d.log')
         to_plot = get_files_at_given_times_from_log(output_files, output_times,
                                                     logfile)
 
         for i, f in enumerate(to_plot):
-            print(i, f)
             data = load(f)
             t = data['solver_data']['t']
             body = data['arrays']['rigid_body']
             wall = data['arrays']['wall']
 
             s = 20.
-            # print(_t)
             fig, axs = plt.subplots(1, 1)
-            axs.scatter(body.x, body.y, s=s, c=body.m)
+            axs.scatter(body.x, body.y, s=s, color="orangered")
             # axs.grid()
             axs.set_aspect('equal', 'box')
             # axs.set_title('still a circle, auto-adjusted data limits', fontsize=10)
@@ -531,7 +530,7 @@ class Mohseni2021FreeSlidingOnASlope(Application):
             wall_y = wall.y[filtr_1]
             wall_m = wall.m[filtr_1]
 
-            tmp = axs.scatter(wall_x, wall_y, s=s, c=wall_m)
+            tmp = axs.scatter(wall_x, wall_y, s=s, color="black")
 
             # save the figure
             figname = os.path.join(os.path.dirname(fname), "time" + str(i) + ".png")
@@ -547,9 +546,8 @@ class Mohseni2021FreeSlidingOnASlope(Application):
             _t = sd['t']
             if _t == 0.:
                 s = 20.
-                # print(_t)
[…]

### 2022-05-23 code/qiu_2017_falling_solid_in_water_2d.py

@@ -103,52 +103,58 @@ def setup_properties_for_gradual_force(pa):
 
 class Qiu2017FallingSolidInWater2D(Application):
     def initialize(self):
-        self.dim = 2
-        spacing = 2. * 1e-3
-        self.hdx = 1.0
-
-        # the fluid dimensions are
-        # x-dimension (this is in the plane of the paper going right)
+        # ================
+        # fluid dimensions
+        # ================
         self.fluid_length = 150. * 1e-3
-        # y-dimension (this goes into the paper)
         self.fluid_height = 131 * 1e-3
-
         self.fluid_density = 1000.0
-        self.fluid_spacing = spacing
+        # ======================
+        # fluid dimensions ends
+        # ======================
 
+        # ================
+        # tank dimensions
+        # ================
         self.tank_length = 150. * 1e-3
         self.tank_height = 140 * 1e-3
-        self.tank_spacing = spacing
         self.tank_layers = 3
+        # ======================
+        # tank dimensions ends
+        # ======================
 
-        # x dimension
+        # =======================
+        # rigid body dimensions
+        # =======================
         self.rigid_body_length = 20. * 1e-3
-        # y dimension
         self.rigid_body_height = 20. * 1e-3
-        self.rigid_body_spacing = spacing
         self.rigid_body_rho = 2120
+        # ===========================
+        # rigid body dimensions ends
+        # ===========================
 
-        self.h = self.hdx * self.fluid_spacing
+        # =====================
+        # parameters for solver
+        # =====================
+        self.dim = 2
+        self.spacing = 2. * 1e-3
+        self.hdx = 1.0
+        self.h = self.hdx * self.spacing
 
-        # self.solid_rho = 500
-        # self.m = 1000 * self.dx * self.dx
+        # fluid solver parameters
         self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
         self.p0 = self.fluid_density * self.co**2.
-        self.c0 = self.co
-        # fixme: why is it blowing up with higher alpha
         self.alpha = 0.5
+
+        # basic parameters
         self.gx = 0.
         self.gy = -9.81
         self.gz = 0.
-        self.dim = 2
-
         # solver data
         self.tf = 0.5
-        self.dt = 0.25 * self.fluid_spacing * self.hdx / (self.c0 * 1.1)
-
-        # Rigid body collision related data
-        self.limit = 6
-        self.seval = None
[…]

### 2022-05-23 code/rigid_body_3d.py

@@ -74,8 +74,8 @@ class GTVFRigidBody3DStep(IntegratorStep):
             for j in range(3):
                 # using velocity at t, move position
                 # to t + dt/2.
-                dst.vcm[i3 + j] = dst.vcm[i3 + j] + (dtb2 * dst.force[i3 + j] /
-                                                     dst.total_mass[i])
+                dst.acm[i3 + j] = dst.force[i3 + j] / dst.total_mass[i]
+                dst.vcm[i3 + j] = dst.vcm[i3 + j] + (dtb2 * dst.acm[i3 + j])
 
             # move angular velocity to t + dt/2.
             # omega_dot is
@@ -87,8 +87,18 @@ class GTVFRigidBody3DStep(IntegratorStep):
                 dst.inertia_tensor_inverse_global_frame[i9:i9 + 9].reshape(
                     3, 3), dst.ang_mom[i3:i3 + 3])
 
+            # compute the angular acceleration
+            # https://physics.stackexchange.com/questions/688426/compute-angular-acceleration-from-torque-in-3d
+            omega_cross_L = np.cross(dst.omega[i3:i3 + 3],
+                                     dst.ang_mom[i3:i3 + 3])
+            tmp = dst.torque[i3:i3 + 3] - omega_cross_L
+            dst.ang_acc[i3:i3 + 3] = np.matmul(
+                dst.inertia_tensor_inverse_global_frame[i9:i9 + 9].reshape(
+                    3, 3), tmp)
+
     def stage1(self, d_idx, d_x, d_y, d_z, d_u, d_v, d_w, d_dx0, d_dy0, d_dz0,
-               d_xcm, d_vcm, d_R, d_omega, d_body_id, d_is_boundary):
+               d_au, d_av, d_aw, d_xcm, d_vcm, d_acm, d_ang_acc, d_R, d_omega,
+               d_body_id, d_is_boundary):
         # Update the velocities to 1/2. time step
         # some variables to update the positions seamlessly
 
@@ -121,6 +131,18 @@ class GTVFRigidBody3DStep(IntegratorStep):
         d_u[d_idx] = d_vcm[i3 + 0] + du
         d_v[d_idx] = d_vcm[i3 + 1] + dv
         d_w[d_idx] = d_vcm[i3 + 2] + dw
+
+        # for particle acceleration we follow this
[…]

### 2022-05-23 code/rigid_fluid_coupling.py

@@ -36,7 +36,7 @@ from rigid_body_common import (add_properties_stride,
                                set_body_frame_position_vectors,
                                set_body_frame_normal_vectors,
                                set_moment_of_inertia_and_its_inverse,
-                               BodyForce, SumUpExternalForces,
+                               ResetForce, SumUpExternalForces,
                                normalize_R_orientation,
                                ComputeContactForceNormals,
                                ComputeContactForceDistanceAndClosestPoint,
@@ -45,7 +45,8 @@ from rigid_body_common import (add_properties_stride,
 from contact_force_mohseni_vyas import (
     ComputeContactForceNormalsMV,
     ComputeContactForceDistanceAndClosestPointAndWeightDenominatorMV,
-    ComputeContactForceMV,
+    ComputeContactForceLinearMV,
+    ComputeContactForceNonLinearMV,
     TransferContactForceMV)
 
 # compute the boundary particles
@@ -240,9 +241,6 @@ class ForceOnRigidBodyDuetoFluid(Equation):
           for both the particle properties.
 
     """
-    def __init__(self, dest, sources):
-        super(ForceOnRigidBodyDuetoFluid, self).__init__(dest, sources)
-
     def loop(self, d_idx, d_m_fsi, d_rho_fsi, d_p_fsi, s_idx, d_fx, d_fy,
              d_fz, DWIJ, s_m, s_p, s_rho):
         _t1 = s_p[s_idx] / (s_rho[s_idx]**2) + d_p_fsi[d_idx] / (d_rho_fsi[d_idx]**2)
@@ -776,58 +774,61 @@ class RigidFluidCouplingScheme(Scheme):
             g5 = []
             for name in self.rigid_bodies:
                 g5.append(
-                    ComputeContactForceNormalsMV(
-                        dest=name,
-                        sources=self.rigid_bodies+self.boundaries))
-
-            stage2.append(Group(equations=g5, real=False))
-
-            g5 = []
-            for name in self.rigid_bodies:
-                g5.append(
-                    ComputeContactForceDistanceAndClosestPointAndWeightDenominatorMV
-                    (dest=name, sources=self.rigid_bodies+self.boundaries))
+                    ResetForce(dest=name, sources=None))
             stage2.append(Group(equations=g5, real=False))
 
         if len(self.rigid_bodies) > 0:
             g5 = []
             for name in self.rigid_bodies:
                 g5.append(
-                    BodyForce(dest=name,
-                              sources=None,
-                              gx=self.gx,
[…]

### 2022-05-27 manuscript/paper.tex
Put dam breaking flow over rigid cubes figures in paper.

@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_one_cube_3d/case_1/xcom_vs_time}
   \caption{x position of the cube with time for single cube.}
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
+  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_three_stacked_cubes_3d/case_1/xcom_vs_time}
   \caption{x position of the cubes with time for three cube.}
 \label{fig:x-position-three-cubes-3d-dam-breaking-flow}
+\end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_three_stacked_cubes_3d/case_1/ycom_vs_time}
+  \caption{y position of the cubes with time for three cube.}
+\label{fig:y-position-three-cubes-3d-dam-breaking-flow}
 \end{figure}
@@
 results, SPH-DCDEM, MPS-DEM results in
-\Cref{fig:x-position-three-cubes-3d-dam-breaking-flow}. From these figures, we
+\Cref{fig:x-position-six-cubes-3d-dam-breaking-flow}. From these figures, we
 can see that the current solver is in good agreement with the other numerical
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
-  \caption{x position of the six with time for three cube.}
-\label{fig:x-position-six-cube-3d-dam-breaking-flow}
+  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_six_stacked_cubes_3d/case_1/xcom_vs_time}
+  \caption{x position of the cubes with time for six cubes.}
+\label{fig:x-position-six-cubes-3d-dam-breaking-flow}
+\end{figure}
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_six_stacked_cubes_3d/case_1/ycom_vs_time}
+  \caption{y position of the cubes with time for six cubes.}
+\label{fig:y-position-six-cubes-3d-dam-breaking-flow}
 \end{figure}

### 2022-05-27 automate.py

@@ -1951,6 +1951,26 @@ class Amaro2019DamBreakingFlowHittingOneCube3d(Problem):
 
     def run(self):
         self.make_output_dir()
+        self.move_figures()
+
+    def move_figures(self):
+        import shutil
+        import os
+
+        for name in self.case_info:
+            source = self.input_path(name)
+
+            target_dir = "manuscript/figures/" + source[8:] + "/"
+            os.makedirs(target_dir)
+            # print(target_dir)
+
+            file_names = os.listdir(source)
+
+            for file_name in file_names:
+                # print(file_name)
+                if file_name.endswith((".jpg", ".pdf", ".png")):
+                    # print(target_dir)
+                    shutil.copy(os.path.join(source, file_name), target_dir)
 
 
 class Amaro2019DamBreakingFlowHittingThreeStackedCubes3d(Problem):
@@ -1984,6 +2004,26 @@ class Amaro2019DamBreakingFlowHittingThreeStackedCubes3d(Problem):
 
     def run(self):
         self.make_output_dir()
+        self.move_figures()
+
+    def move_figures(self):
+        import shutil
+        import os
+
+        for name in self.case_info:
+            source = self.input_path(name)
+
+            target_dir = "manuscript/figures/" + source[8:] + "/"
+            os.makedirs(target_dir)
+            # print(target_dir)
+
+            file_names = os.listdir(source)
+
+            for file_name in file_names:
+                # print(file_name)
+                if file_name.endswith((".jpg", ".pdf", ".png")):
+                    # print(target_dir)
+                    shutil.copy(os.path.join(source, file_name), target_dir)
 
 
 class Amaro2019DamBreakingFlowHittingSixStackedCubes3d(Problem):
@@ -2016,6 +2056,26 @@ class Amaro2019DamBreakingFlowHittingSixStackedCubes3d(Problem):
 
     def run(self):
         self.make_output_dir()
+        self.move_figures()
+
+    def move_figures(self):
+        import shutil
+        import os
+
+        for name in self.case_info:
+            source = self.input_path(name)
+
+            target_dir = "manuscript/figures/" + source[8:] + "/"
+            os.makedirs(target_dir)
+            # print(target_dir)
+
+            file_names = os.listdir(source)
+
+            for file_name in file_names:
+                # print(file_name)
+                if file_name.endswith((".jpg", ".pdf", ".png")):
+                    # print(target_dir)
[…]

### 2022-10-17 manuscript/paper.tex
Add coupling equations. The code is messy now. But this is archieved

@@
 \usepackage{booktabs}
+\usepackage{physics}
+\usepackage{breqn}
 
@@
 \label{sec:intro}
-\begin{itemize}
-\item Rigid bodies in fluid flows in nature. Where can we find them? What kind
-  of problems do they give rise to? Ice-Sea? Debris?
-\item Why is it hard to model rigid fluid coupling? Then we say numerically
-  nonlinear, and this is how it is been into handled. Many different ways RFC
-  is been modeled, this includes mesh based and messless. Explain in a good
-  detail what meshless methods are out there which handles these problems.
-  This includes SPH too. (Same as next point)
-\item \todoin{Done} Describe some works where Rigid fluid coupling is handled
-  in meshless methods. MPS-DEM, SPH-DEM and other ways, recently Asai. (Same
-  as previous point)
-\item Explain SPH history and its applications in different areas. Now SPH
-  specifically applied in RFC area. Detail some papers where how differently
-  fluid is modelled, this includes ISPH, WCSPH, TVF, delta+ SPH. Also mention
-  the latest multiphase flow, where air is considered, then mention the
-  adaptive formulation, where the author captures the cavity.
-\item \todoin{Done} Similarly explain the many ways the rigid-rigid coupling is been
-  handled. Detail how non-smooth boundaries are handled.
-\item \todoin{Done} Explain what we are going to do in the current work. We adapt the
-  Mohseni formulation to handle the non-smooth boundaries, we also incorporate
-  the damping, and extend the formulation to 3d and simulate 3d problems.
-\item Explain the examples. 3d Sliding case, 3d controlled sliding case, body
-  falling in water, then 3d dam break over dynamics rigid obstacles.
-% \item Mention the open source software which provide SPH formulation (there are 2.)
-\end{itemize}
+
+Arbitrary shaped rigid bodies in fluid flows in nature. Debris flowing,
+particle transport chemical industries, food processing, in natural hazard
+where the bodies are capable of doing catastrophic damage while being
+sedimented. In ice-sea modeling. Study of such physics is hard to model, as
+the two-way coupling is nonlinear. Many different models were proposed to
+handle the current physics.
+
+In meshless methods, MPS-DEM \cite{guo2017numerical} and SPH-DEM
+\cite{canelas2016sph} are two ways of modeling the physics. Where Moving
+Particle Semi-implicit (MPS) method and smoothed particle hydrodynamics (SPH)
+are utilized to study the fluid dynamics, while the Discrete Element Method
+(DEM) is used to model the interaction among the rigid bodies and finally both
+SPH and MPS are coupled with the rigid bodies to handle the two way coupling.
+In addition to DEM alone to model the rigid-rigid interaction, there are also
+works where SPH \cite{amicarelli2015smoothed} itself is used to model the
+interaction. But it lacks to incorporate the friction between the bodies. In
+the current work we have used SPH to model the fluid dynamics.
+
+The SPH method is a meshless numerical method originally proposed by
+\citet{monaghan-gingold-stars-mnras-77} and \citet{lucy1977numerical} to model
+astrophysics problems. It is fairly success in modeling physics ranging
+different fields, \citet{monaghan-review:2005} provides a detailed review of
+SPH and its applications. structural dynamics, FSI, fracture to note a few.
+SPH has been extensively applied to model the dynamics of fluid in two way
+rigid fluid coupling. There are several SPH variants in which the fluid flow
+can be modeled. \citet{canelas2016sph} uses WCSPH in rigid fluid coupling in
+modeling two way rigid fluid coupling, ISPH is used in \cite{asai2021fluid},
+delta sph in \cite{lyu20223d}. Multiphase flow, where air is considered, to
+capture the cavity while the rigid body enters the water section is modeled in
+\cite{lyu2021study}. A TVF scheme is currently proposed where the particle
+shifting is introduced for better particle distribution leading to less errors
+is not yet utilized in modeling the rigid fluid coupling.
+
+All the works above are using DEM to model the rigid-rigid interaction doesn't
+consider the shape of the body and fails to model bodies with arbitrary shape.
+One of the reasons is the contact force model is between two particles, and
+those particles are assumed as spheres and the contact handling is taken care.
+This doesn't consider the shape of the surface of the rigid body in place.
+Irregular bodies are modeled using many different variations now, one of the
+methods is by overlapped sphere method \cite{das2007modeling}, SMR-DEM by
+\citet{zhan2021surface}, dilated polyhedral DEM \citet{liu2020new}, Fourier
+series-based discrete element method \citet{lai2020fourier}, non-smooth wall
+modeling by \citet{amaro2019improvement}, GJK-DEM \cite{wachs2012grains3d},
+discrete function representation based DEM \cite{lu2012critical}, level set
+DEM method \cite{duriez2021precision}. However, these are complicated to
+implement and not particle friendly and the rigid bodies have to discretized
+differently to handle the non-smooth boundaries. In the current work we have
+extended the contact force model proposed by \citet{mohseni2021particle} to
+handle three dimensional problems, we also incorporate the damping model.
+
+In the current work, we propose a new method to handle the collision between
+arbitrary shaped rigid bodies. Unlike the approach of Mohseni, the proposed
+contact force model is less sensitive to the primary secondary body selection.
+And the proposed method is robust and very simple to implement when compared
+with the existing techniques (cite zhang, Amaro) in the literature. The
+current model tries to eliminate the confusion in choosing the primary and
+secondary body in a collision instance. The rigid fluid coupling between CTVF
+is new. We explored different rigid fluid coupling strategies by simulating
+high density ratio simulations. Several examples are simulated to validate the
+current scheme, ranging from simulations compared with FEM, analytical results
+as well as experimental. Finally, in the interest of reproducibility and
+easier ability for researchers to build on this work, our code is open source
+and can be found at \url{https://gitlab.com/pypr/rfc}. We used automan package
+\cite{automan2018} to automate all the results generated in the current
+manuscript.
+
+Numerical examples, collision of three cubes is initially used to test the
+conservation property of the current contact mode while dealing with
+non-smooth boundaries. Further, a free and forced sliding of a 3d cube on a
+frictional inclined plane, and a rolling cylinder whose analytical solutions
+exists are utilised to validate the rigid-rigid contact model frictional
+model. A granular collapse of a stack of cylinders is modeled and compared
+against the experimental results. In order to validate the two-way rigid fluid
+coupled scheme a rigid circular body falling in a steady tank is simulated.
+Complex interactions of fluid in a 3D dam breaking with multiple rigid bodies,
+is studied and compared with the experimental results of SPH-DCDEM.
 
@@
 
-\textbf{1st bullet point of introduction}. Irregular bodies are modeled using
-many different variations now, one of the methods is by overlapped sphere
-method \cite{das2007modeling}, SMR-DEM by \citet{zhan2021surface}, dilated
-polyhedral DEM \citet{liu2020new}, Fourier series-based discrete element
-method \citet{lai2020fourier}, non-smooth wall modeling by
-\citet{amaro2019improvement}, GJK-DEM, DFR-DEM. In the current work we have
-extended the contact force model proposed by \citet{mohseni2021particle} to
-handle three dimensional problems, we also incorporate the damping model.
-
-\textbf{5th bullet point of introduction}. Irregular bodies are modeled using
-many different variations now, one of the methods is by overlapped sphere
-method \cite{das2007modeling}, SMR-DEM by \citet{zhan2021surface}, dilated
-polyhedral DEM \citet{liu2020new}, Fourier series-based discrete element
-method \citet{lai2020fourier}, non-smooth wall modeling by
-\citet{amaro2019improvement}, GJK-DEM, DFR-DEM. In the current work we have
-extended the contact force model proposed by \citet{mohseni2021particle} to
-handle three dimensional problems, we also incorporate the damping model.
-
-\textbf{6th bullet point of introduction}. Numerical examples, collision of
-three cubes is initially used to test the conservation property of the current
-contact mode while dealing with non-smooth boundaries. Further, a free and
-forced sliding of a 3d cube on a frictional inclined plane, and a rolling
-cylinder whose analytical solutions exists are utilised to validate the
-rigid-rigid contact model frictional model. A granular collapse of a stack of
-cylinders is modeled and compared against the experimental results. In order
-to validate the two-way rigid fluid coupled scheme a rigid circular body
-falling in a steady tank is simulated. Complex interactions of fluid in a 3D
-dam breaking with multiple rigid bodies, is studied and compared with the
-experimental results of SPH-DCDEM.
-
 \FloatBarrier%
@@
 
-The mass and momentum conservation laws that govern the dynamics of fluid motion are given in Lagrangian form by:
-\begin{equation}
-  \label{eq:ce}
-  \frac{d \rho}{d t} = - \rho \; \frac{\partial u_i}{\partial x_i},
-\end{equation}
-\begin{equation}
-  \label{eq:me}
-  \frac{d u_i}{d t} = \frac{1}{\rho} \; \frac{\partial \sigma_{ij}}{\partial x_j}
-  + g_i,
-\end{equation}
-where $\rho$ is the density, $u_i$ is the $i$\textsuperscript{th} component of
-the velocity field, $x_j$ is the $j$\textsuperscript{th} component of the
-position vector, $g_i$ is the component of body force per unit mass. And $\frac{d}{d t}$ is
-\begin{equation}
-  \label{eq:material-derivative}
-  \frac{d}{d t} = \frac{\partial }{\partial t} +
-  {u}_j \frac{\partial }{\partial x_j}.
-\end{equation}
-
-Following CTVF formulation, and moving the particles with transport velocity,
-we have the modified material derivative as
-\begin{equation}
-  \label{eq:modified-material-derivative}
-  \frac{\tilde{d} }{d t} = \frac{\partial }{\partial t} +
-  \tilde{u}_j \frac{\partial }{\partial x_j}.
-\end{equation}
-
-The adjust equations for the modified derivative are given by:
-
-\begin{equation}
-  \label{eq:ce-tvf}
-  \frac{\tilde{d} \rho}{d t} =
-  - \rho \frac{\partial \tilde{u}_j}{\partial x_j} +
-  \frac{\partial (\rho (\tilde{u}_j - u_j))}{\partial x_j}.
-\end{equation}
-\begin{equation}
-  \label{eq:mom-tvf}
-  \frac{\tilde{d} u_i}{d t} =
-  \frac{\partial}{\partial x_j} (u_i (\tilde{u}_j - u_j))
-  - u_i \frac{\partial}{\partial x_j} (\tilde{u}_j - u_j)
-  + g_i
-  +\frac{1}{\rho} \frac{\partial \sigma_{ij}}{\partial x_j}.
-\end{equation}
-
-For a weakly-compressible or incompressible fluid, a viscous force is added:
-\begin{equation}
-  \label{eq:fluid-stress-decomposition}
-  \sigma_{ij} = - p \delta_{ij} + 2 \eta \frac{\partial u_i}{\partial x_j}
-\end{equation}
-where $\eta$ is the kinematic viscosity of the fluid.
-
-In both fluid and solid modelling the pressure is computed using an
-isothermal equation of state, given as,
-\begin{equation}
-  \label{eq:pressure-equation}
-  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
-\end{equation}
-where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
-$\rho_0$ are the reference speed of sound and density, respectively. For solids,
-$c_0$ is computed as $\sqrt{\frac{E}{3 (1 - 2 \nu)\rho_{0}}}$, $\nu$ is the
-Poisson ratio.
+\subsection{Governing equations}
+\label{sec:governing-eqns-fluid-dynamics}
 
@@
   \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
-  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
-  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
-  \bigg) \bigg]
-  \cdot \nabla_{a} W_{ab} \\
-  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
-  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
+  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I}
+   \bigg]
+  \cdot \nabla_{a} W_{ab} + \\
+  \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
     \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
@@
 \end{multline}
-The particles in the current scheme are moved with the transport velocity,
-\begin{equation}
-  \label{eq:transport_velocity_position_derivative}
-  \frac{d\ten{r}_a}{dt} = \ten{\tilde{u}}_a.
-\end{equation}
-%
-The transport velocity is updated using,
-\begin{equation}
-  \label{eq:transport_velocity}
-  \ten{\tilde{u}}_a(t + \Delta t) =\ten{u}_a(t) + \Delta t \; \frac{\tilde{d} \ten{u}_a}{dt} +
-  \bigg(\frac{d \ten{u}_{a}}{dt}\bigg)_{\text{c}} \Delta t,
-\end{equation}
-where $\ten{A}_a = \rho_a \ten{u}_a \otimes (\ten{\tilde{u}}_a - \ten{u}_a)$,
-$\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
-fluid and \citet{morris1997modeling} formulation is used to discretize the
-viscosity term.
-\begin{itemize}
-\item Discuss about the homogenization force (We use GTVf).
-\item Describe $\Pi_{ij}$ for numerical stability.
-\item And other terms.
-\end{itemize}
-We add to the momentum equation an additional artificial viscosity term
-$\Pi_{ab}$~\cite{monaghan-review:2005} to maintain the stability of the
-numerical scheme, given as,
-\begin{align}
-  \label{eq:mom-av}
-  \Pi_{ab} =
-  \begin{cases}
-\frac{-\alpha h_{ab} \bar{c}_{ab} \phi_{ab}}{\bar{\rho}_{ab}}
-  & \ten{u}_{ab}\cdot \ten{r}_{ab} < 0, \\
-  0 & \ten{u}_{ab}\cdot \ten{r}_{ab} \ge 0,
-\end{cases}
-\end{align}
-where,
-%
-\begin{equation}
-  \label{eq:av-phiij}
-  \phi_{ab} = \frac{\ten{u}_{ab} \cdot \ten{r}_{ab}}{r^2_{ab} + 0.01 h^2_{ab}},
-\end{equation}
-%
-where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$, $\ten{u}_{ab} = \ten{u}_a -
-\ten{u}_b$, $h_{ab} = (h_a + h_b)/2$, $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$,
-$\bar{c}_{ab} = (c_a + c_b) / 2$, and $\alpha$ is the artificial
-viscosity parameter.
-
-%
-where $\big(\frac{d \ten{u}_a}{dt}\big)_{\text{c}}$ is the homogenization
-acceleration which ensures that the particle positions are homogeneous.
-
-\subsection{Boundary conditions}
-
-The ghost particle approach of \citet{Adami2012} is used to model the
-boundaries. We use three layers of ghost particles to model the solid wall.
-The properties of the solid wall are interpolated from the fluid particles.
-
-When computing the divergence of the velocity field on fluid particles, we
-enforce a no-penetration boundary condition and not a no-slip boundary
-condition. The velocity of the fluid is projected onto the ghost particles
-using,
-\begin{equation}
-  \label{eq:v-ghost}
-  \ten{\hat{u}}_a = \frac{\sum_b\ten{u}_b W_{ab}}{\sum_b W_{ab}},
-\end{equation}
-\begin{equation}
-  \label{eq:v-hat-ghost}
-  \ten{\check{u}}_a = \frac{\sum_b\tilde{\ten{u}}_b W_{ab}}{\sum_b W_{ab}},
-\end{equation}
-where $\ten{u}_b$, $\ten{\tilde{u}}_b$ are the momentum and transport velocity
-of the fluid respectively and $W_{ab}$ is the kernel value between the fluid
-particle and the ghost particle.
-
-The normal component of this projected velocity is then reflected and set as
-the ghost particle velocity,
-\begin{equation}
-  \label{eq:free-slip-bc-u}
-  \ten{u}_{\text{Ga}} = 2 \ten{\hat{n}}((\ten{u}_{\text{p}} - \ten{\hat{u}}_{\text{a}})\cdot \ten{\hat{n}}) + \ten{\hat{u}}_{\text{a}},
-\end{equation}
-where $\ten{u}_{\text{p}}$ is the local velocity of the boundary and
-$\ten{\hat{n}}$ is the unit normal to the boundary particle $a$. Similarly the
-transport velocity of the ghost particle is set as,
-\begin{equation}
-  \label{eq:free-slip-bc-u}
-  \tilde{\ten{u}}_{\text{Gi}} = 2 \ten{\hat{n}}((\ten{u}_{\text{p}} - \ten{\check{u}}_{\text{i}})\cdot \ten{\hat{n}}) + \ten{\check{u}}_{\text{i}},
-\end{equation}
-
-When the viscous force is computed, the no slip boundary condition is used,
-where the velocity on the boundary set as,
-\begin{equation}
-  \label{eq:no-slip-bc-u}
-  \ten{u}_{\text{Ga}} = 2 \ten{u}_{\text{p}} - \ten{\hat{u}}_{\text{a}},
-\end{equation}
-a similar form is used for the transport velocity here too,
-\begin{equation}
-  \label{eq:no-slip-bc-uhat}
-  \tilde{\ten{u}}_{\text{Ga}} = 2 \ten{u}_{\text{p}} - \ten{\check{u}}_{\text{a}}.
-\end{equation}
-
-The pressure of the boundary particle is extrapolated from its surrounding
-fluid particles by the following equation,
-\begin{equation}
-  \label{eq:pressure-bc}
-  p_w = \frac{\Sigma_f p_f W_{wf} + (\ten{g} - \ten{a}_{\ten{w}}) \cdot \Sigma_f
-    \rho_f \ten{r}_{wf} W_{wf}}{\Sigma_f W_{wf}},
-\end{equation}
-where $\ten{a}_w$ is the acceleration of the wall. The subscript $f$ denotes
-the fluid particles and $w$ denotes the wall particles.
-
-\begin{itemize}
-\item Choose the timestep
-\end{itemize}
+
+\newpage
+~\newpage
+~\newpage
 
@@
 
-% check \cite{natsui2018sph}
-
-The state of a rigid body is defined by position of center of mass, velocity
-of center of mass, a rotation matrix to define the three rotational degrees of
-freedom and angular velocity.
+\newpage
+~\newpage
+The rigid body is discretized into particles with equal spacing each particle
+with mass $m_i$ and density $\rho_i$. Rigid body has a total 6 degrees of
+freedom (DOF), divided into $3$ translational and $3$ rotational.
+
+The state of the rigid body at a given time (t) can described using position
+and velocity of the center of mass ($\ten{x}_{cm}$), velocity of center of
+mass ($\ten{v}_{cm}$), a rotation matrix ($\ten{R}$), to define the three
+rotational degrees of freedom and angular velocity($\teng{\omega}$). The
+center of mass is computed with
+\begin{equation}
+  \label{eq:center_of_mass}
+  \ten{x}_{cm} = \frac{\sum_i m_i \; \ten{x}_{i} }{\sum_i m_i }
+\end{equation}
 
@@
 angular momentum given by,
-
 \begin{equation}
   \label{eq:balance_linear_mom}
-  \frac{d \; (M \ten{v}_{cm})}{d t} = \sum_i \ten{F}_i
-\end{equation}
-
+  \frac{d \; (M \ten{v}_{cm})}{d t} = \sum_i \ten{F}_i,
+\end{equation}
 \begin{equation}
@@
 \end{equation}
-
-where $\teng{\tau}_i$ is the torque about center of mass due to forces on the
+where $\teng{\tau}_{cm}$ is the torque about center of mass due to forces on the
 particles,
-
 \begin{equation}
@@
 \end{equation}
-
-The angular momentum and the center of mass velocity of the body is updated by following
-
+and $\ten{L}$ is the angular momentum of the rigid body about center of mass,
+computed as
+\begin{equation}
+  \label{eq:moi}
+  \teng{L} =
+  \sum_i \; \ten{r}_i \times \; (\ten{\omega} \times \ten{r}_i)
+  = \sum_i \; m_i \; [(\ten{r} \cdot \ten{r}) \ten{I} - \ten{r} \otimes \ten{r}]
+\end{equation}
+\begin{equation}
+  \label{eq:omega_compute}
+  \teng{\omega} = \textit{\teng{I}}^{-1} \; \ten{L}
+\end{equation}
+
+The state of the rigid body at next time step is evolved through the
+integration of governing \cref{eq:balance_linear_mom,eq:balance_angular_mom},
+finding the linear velocity of the center of mass $\ten{v}_{cm}$ and angular
+momentum $\ten{L}$ at the next timestep as,
+\begin{equation}
+  \label{eq:lin_pos_cm_update}
+  \ten{x}_{cm}^{n+1} = \ten{x}_{cm}^{n} + \ten{v}_{cm}^{n} \; \Delta t
+\end{equation}
+\begin{equation}
+  \label{eq:lin_vel_cm_update}
+  \ten{v}_{cm}^{n+1} = \ten{v}_{cm}^{n} + \frac{\ten{F}_{cm}}{M} \; \Delta t
+\end{equation}
+ The orientation $\ten{R}$ is updated as,
+\begin{equation}
+  \label{eq:rotation_update}
+  \ten{R}^{n+1} = \ten{R}^{n} + \tilde{\teng{\omega}}^{n} \, \ten{R}^{n} \; \Delta t
+\end{equation}
 \begin{equation}
   \label{eq:ang_mom_update}
-  \ten{x}_{cm} = \ten{x}_{cm} + \frac{\ten{F}_{cm}}{M} \; \Delta t
-\end{equation}
-
-\begin{equation}
-  \label{eq:ang_mom_update}
-  \ten{L} = \ten{L} + \teng{\tau}_{cm} \; \Delta t
-\end{equation}
-
-\begin{equation}
-  \label{eq:rotation_update}
-  \ten{R} = \ten{R} + \tilde{\teng{\omega}} \, \ten{R} \; \Delta t
-\end{equation}
-
+  \ten{L}^{n+1} = \ten{L}^{n} + \teng{\tau}_{cm} \; \Delta t
+\end{equation}
+Moment of inertia at the new time step is computed as
 \begin{equation}
   \label{eq:moi_update}
-  \ten{I}^{-1} = \ten{R} \hat{\ten{I}}^{-1} \ten{R}^T
-\end{equation}
-
-\begin{equation}
-  \label{eq:moi_update}
-  \teng{\omega} = \ten{I}^{-1} \; \ten{L}
-\end{equation}
-
-Particles update
-
+  (\textit{\teng{I}}^{-1})^{n+1} = \ten{R}^{n+1} \textit{\teng{\overline{I}}}^{-1} (\ten{R}^{n+1})^T
+\end{equation}
+The angular velocity at the new time step is computed with
+\begin{equation}
+  \label{eq:ang_velocity_update}
+  \teng{\omega}^{n+1} = (\textit{\teng{I}}^{-1})^{n+1} \; \ten{L}^{n+1}.
+\end{equation}
+The position and velocity of the particles of the rigid body are updated by
 \begin{equation}
   \label{eq:rb_particle_pos_update}
-  \ten{x}_i(t) = \ten{x}_{cm}(t) + \ten{R}(t) \; \hat{\ten{r}}_{i}(t)
-\end{equation}
-
+  \ten{r}_i = \ten{R} \cdot \overline{\ten{r}}_{i}
+\end{equation}
+\begin{equation}
+  \label{eq:rb_particle_pos_update}
+  \ten{x}_i = \ten{x}_{cm} + \ten{r}_{i}
+\end{equation}
 \begin{equation}
   \label{eq:rb_particle_vel_update}
-  \ten{v}_i(t) = \ten{v}_{cm}(t) + \teng{\omega}(t) \; \ten{r}_{i}(t)
-\end{equation}
+  \ten{v}_i = \ten{v}_{cm} + \teng{\omega} \times \ten{r}_{i}
+\end{equation}
+
+% check \cite{natsui2018sph}
+We use two coordinate frames to capture the dynamics of the rigid body. The
+body fixed frame, which moves with rigid body is located always at the center
+of mass ($\ten{x}_{cm}$) of the body, computed as
+
+A body fixed coordinate system is put at the center of mass, and it translates
+and rotates with the body. The discretized particle's position vector is
+constant about this body fixed coordinate frame. Figure x shows the rigid body
+at an instant, the position vector of particle $\ten{x}_i$ about global frame
+is computed as
+\begin{equation}
+  \label{eq:global_position_vector_idea}
+  \ten{x}_{i} = \ten{x}_{cm} + \ten{r}_i = \ten{x}_{cm} + \text{Rot}(\overline{\ten{r}}_i)
+\end{equation}
+where,
+\begin{equation}
+  \label{eq:body_position_vector}
+  \overline{\ten{r}}_i = \ten{x}_i(0) - \ten{x}_{cm}(0)
+\end{equation}
+
+A 3$\times$3 rotation matrix is utilized to represent the orientation of the
+body fixed coordinate frame, representing 3 degrees of freedom.
+\begin{equation}
+  \label{eq:rotation_matrix}
+  \ten{A} = \mqty(\ten{a}_{1} & \ten{a}_{2} & \ten{a}_{3})
+\end{equation}
+where, each column $\ten{a}_{1}$, $\ten{a}_{1}$, $\ten{a}_{1}$ represents the
+body frame coordinate axes unit vectors in global frame. With which the
+position vector of the particle in local frame is translated to the global frame as,
+\begin{equation}
+  \label{eq:local_to_gloabl_translate}
+  \ten{r}_i = \ten{A} \; \overline{\ten{r}}_i.
+\end{equation}
+
+\begin{figure}[!htpb]
+  \centering
+  % \includegraphics[width=1.0\textwidth]{images/contact_force/contact_force_description}
+  \caption{2d description of local to global vector translation}
+\label{fig:local_to_global_2d_explanation}
+\end{figure}
+Rotation matrix $\ten{A}$ has to be orthogonal, with determinant equal to $1$
+and finally the magnitude of the eigenvalues is needed to be $1$. The position
+of a body point $i$, can be written as
+\begin{equation}
+  \label{eq:global_position_vector}
+  \ten{x}_{i} = \ten{x}_{cm} + \ten{A}(\overline{\ten{r}}_i)
+\end{equation}
+
+The state of the rigid body can be described by
+\begin{equation}
+  \label{eq:rotation_matrix}
+  state = \mqty(\ten{x}_{cm} & \ten{A} & \ten{v}_{cm} & \ten{\omega})
+\end{equation}
+\newpage
+~\newpage
 
@@
 
-\begin{multline}
+\begin{equation}
   \label{eq:force_on_fluid_due_to_rb}
@@
   \cdot \nabla_{a} W_{ab}
-\end{multline}
-
-\begin{multline}
+\end{equation}
+
+\begin{equation}
   \label{eq:force_on_fluid_due_to_rb}
@@
   \cdot \nabla_{a} W_{ab}
-\end{multline}
+\end{equation}
 
@@
 
+\newpage
+~\newpage
+~\newpage
+
 \FloatBarrier%
-\section{Collision between rigid bodies}
-\label{sec:contact-force}
-
-\citet{chen2019coupled} has damping model. Also he mentioned the parameters
-required in stack of cylinders example.
+\section{Contact algorithm}
+\label{sec:contact-algorithm}
+\todoin{\citet{chen2019coupled} has damping model. Also he mentioned the parameters
+required in stack of cylinders example.}
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=1.0\textwidth]{images/contact_force/contact_force_description}
+  \caption{Contact force description}
+\label{fig:contact_foce_description}
+\end{figure}
+In the current work we have utilized the contact force model proposed by
+\citet{mohseni2021particle}. The force acting on a particle $i$ of body A due
+to the interaction with the particles of body $B$ can be resolved into a
+normal and tangential component. Where, normal force component is utilised to
+make sure that the particles of different body don't penetrate into each
+other, while the tangential component is used to model the friction between
+the interacting solids. According to \citet{mohseni2021particle}, we divide the
+bodies under interaction into primary and secondary bodies, as shown in
+\cref{fig:contact_foce_description}.
+% In usual DEM to compute the force on particle i of body A, the force is
+% computed by considering the overlap of particle i with each and every
+% particle of body j by considering the particle j to be spherical. This leads
+% to unphysical modeling of contact force when the body is interacting with a
+% flat surface or surfaces which are not spherical by nature. The current
+% contact force is surface aware. The force on particle $i$ is computed by
+% equation
+The normal force ($\teng{F}_i^{n}$) on
+particle $i$ due to the interaction with the particles $j$ of body $B$ is
+computed as,
+\begin{equation}
+  \label{eq:contact-algorithm-normal}
+  \ten{F}_i = K_r \delta_{n}^{i} \ten{n}_i.
+\end{equation}
+Here, the overlap $\delta_{n}$ is computed using
+\begin{equation}
+  \label{eq:cf-distance-computation}
+  d_i = \frac{
+    \displaystyle\sum\limits_{j = 1}^{\text{NP}^{b}} \;
+    \big( \ten{n}_i \cdot \ten{x}_{ij} \big)  \frac{m_j}{\rho_j} W_{ij}}
+  {
+    \displaystyle\sum\limits_{j = 1}^{\text{NP}^{b}} \;
+    \frac{m_j}{\rho_j} W_{ij}}.
+\end{equation}
+
+The overlap is computed by $\delta_{n}^{i}$
+\begin{equation}
+  \label{eq:cf-overlap}
+  \delta_{n}^{i} = \Delta x - d_i,
+\end{equation}
+where $\Delta x$ is the initial spacing between the particles. Note that while
+computing the overlap of particle $i$ with the body $B$, we have computed an
+effective overlap, rather than per particle interaction. This effectively is
+able to model the interaction between non smooth surfaces, contrast from
+particle particle force computation.
+
+We associate a tangential spring attached to particle $i$ and body $B$ to
+compute the tangential force, which initially has a magnitude of zero
+($|\Delta \textit{\textbf{l}}_i|=0$). And the tangential spring is activated
+when the particle comes into contact with body $B$, which is conformed by
+\cref{eq:cf-overlap}. The tangential force is history-dependent. The contact
+friction force is proportional to the tangential spring displacement, which is
+integrated over the contact time as
+\begin{equation}
+  \label{eq:tangential-force}
+  \ten{F}_{i}^{t^{n+1}} =
+  -k_f \Delta \textit{\textbf{l}}_i^{\,n + 1} =
+  -k_f \big[\big(\Delta {\textit{\textbf{l}}}_i^{\,n} \
+  + \ten{v}_{ij}^{n + 1} \Delta t\big) \cdot \ten{t}_i^{n + 1} \big] \
+  \ten{t}_i^{n + 1},
+\end{equation}
+where $\Delta t$ is the time step, $\ten{v}_{ij} = \ten{v}_{i} - \ten{v}_j$ is
+the relative velocity of the primary particle $i$ with respect to the
+secondary particle $j$. The tangential unit vector is computed by,
+\begin{equation}
+  \label{eq:tangential-vect}
+  \ten{t}_i = \frac{\ten{v}_{ij} - (\ten{v}_{ij} \cdot \ten{n}_i) \ten{n}_i}{|\ten{v}_{ij} - (\ten{v}_{ij} \cdot \ten{n}_i) \ten{n}_i|}.
+\end{equation}
+
+The tangential force is coupled to the normal force through the Coulomb's law,
+\begin{equation}
+  \label{eq:Coulomb-law}
+  \ten{F}_{i}^{t} = \min(\mu |\ten{F}_{i}^{n}|, |\ten{F}_{i}^{t}|) \
+  \frac{\ten{F}_{i}^{t}}{|\ten{F}_{i}^{t}|}.
+\end{equation}
+This allows to impose the sliding friction condition between the interacting
+solids. Finally, the total force acting on the particle $i$ due to the
+interaction with body $B$ is:
+\begin{equation}
+  \label{eq:contact-force}
+  \ten{F}_{i}^{cont} = \ten{F}_{i}^{n} + \ten{F}_{i}^{t}
+\end{equation}
+
+\begin{figure}[!htpb]
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/contact_force/contact_force_description_3}
+  \caption{Force transfer to the secondary particles $j$ from the primary body particle $i$}
+\label{fig:secondary_particle_contact_foce_transfer}
+\end{figure}
+An equal and opposite force of the same magnitude is applied to the closest
+secondary particle $j$ of $i$,
+\begin{equation}
+  \label{eq:contact-force}
+  \ten{F}_{j}^{cont} = - \ten{F}_{i}^{cont}
+\end{equation}
+
+% The force on the particle $j$ is evaluated, on the
+% body belonging to the secondary surface is as follows. Particles belonging to
+% the secondary surface ($j$) which are at a distance less than the initial
+% spacing ($l_0$) share the force exerted on particle i, as following:
+% \begin{equation}
+%   \label{eq:cf-overlap}
+%   F^{ij} = - F^{i} w^{ij},
+% \end{equation}
+% where $w^{ij}$ is defined as
+% \begin{equation}
+%   \label{eq:cf-overlap}
+%   w^{ij} = \frac{n^{i} \cdot \hat{\ten{r}}^{ij}}{\sum_j n^{i} \cdot \hat{\ten{r}}^{ij}}
+% \end{equation}
+
+The current contact force model is sensitive towards the primary body chosen
+to compute the forces, i.e., the force acting on the particles is not the same
+when the primary bodies are interchanged. In the current work we have explored
+the behaviour of the current contact force model when different bodies are
+chosen as primary and secondary. Simulations such as, a rectangular solid
+sliding down an inclined plane, and a symmetric collision between elastic
+solids are two examples, where we have enquired how the bodies would behave
+when different bodies are chosen as primary, as shown in
+\cref{fig:primary-secondary-demonstration}.
+\begin{figure}[!htpb]
+  \centering
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{images/primary_vs_secondary/sliding}
+    \subcaption{A sliding body.}%\label{fig:rings:ipst-nu-0.47-0}
+  \end{subfigure}
+  \begin{subfigure}{0.48\textwidth}
+    \centering
+    \includegraphics[width=1.0\textwidth]{images/primary_vs_secondary/symmetric_collision}
+    \subcaption{A symmetric collision between rectangular solids.}%\label{fig:rings:ipst-nu-0.47-1}
+  \end{subfigure}
+  \caption{Examples used to explore the importance of choosing a primary.}
+\label{fig:primary-secondary-demonstration}
+\end{figure}
+
+\newpage
+~\newpage
 
@@
 %%% End:
+
+\begin{enumerate}
+\item DOF
+\item Variables to describe the state
+\item Governing equations
+\item Discretization
+\item Two coordinate system (Particle positions about these two)
+\item Updated state
+\item Rotation matrix
+\item (a) Describe how the particles are translated to gloabl system from
+  local using rotation matrix. Use a figure.
+\item (b) Particle positions about new Rr
+\item $\omega$ and $\ten{R}$ relation
+\item Relation $I$ and $\ten{R}$
+\item Integration of governing equations
+\item Advantages of representing the body with just boundary particles and
+  speed up
+\end{enumerate}

### 2022-10-17 automate.py

@@ -1404,6 +1404,88 @@ class Dinesh2022HydrostaticTank2D(Problem):
         self.make_output_dir()
 
 
+class Amicarelli2015FlatBodyImpingedByWaterJet2D(Problem):
+    def get_name(self):
+        return 'amicarelli_2015_flat_body_impinged_by_water_jet_2d'
+
+    def setup(self):
+        get_path = self.input_path
+
+        cmd = 'python code/amicarelli_2015_flat_body_impinged_by_water_jet_2d.py' + backend
+
+        # Base case info
+        self.case_info = {
+            'dx_0_002': (dict(
+                scheme='rfc',
+                no_edac=None,
+                pfreq=300,
+                dx=2*1e-3,
+                kr=1e5,
+                fric_coeff=0.0,
+                fluid_alpha=0.2,
+                tf=0.5,
+                ), 'dx=0.002 m'),
+        }
+
+        self.cases = [
+            Simulation(get_path(name), cmd,
+                       job_info=dict(n_core=n_core,
+                                     n_thread=n_thread), cache_nnps=None,
+                       **scheme_opts(self.case_info[name][0]))
+            for name in self.case_info
+        ]
+
+    def run(self):
+        self.make_output_dir()
+        self.plot_velocity()
+        self.move_figures()
+
+    def plot_velocity(self):
+        data = {}
+        for name in self.case_info:
+            data[name] = np.load(self.input_path(name, 'results.npz'))
+
+        for name in self.case_info:
+            t_experimental = data[name]['t_experimental']
+            y_cm_experimental = data[name]['y_cm_experimental']
+
+            t = data[name]['t']
+            y_cm_simulated = data[name]['y_cm_simulated']
+
+            plt.scatter(t, y_cm_simulated, s=1, label=self.case_info[name][1])
+
+        # experimental plot should be only once plotted
+        plt.plot(t_experimental, y_cm_experimental, label=self.case_info[name][1] + ' Experimental')
+
+        plt.xlabel('time')
+        plt.ylabel('')
+        plt.legend(prop={'size': 12})
+        # plt.tight_layout(pad=0)
+        plt.savefig(self.output_path('y_cm_vs_time.pdf'))
+        plt.clf()
+        plt.close()
+
+    def move_figures(self):
+        import shutil
+        import os
+
+        for name in self.case_info:
+            source = self.input_path(name)
+
[…]

### 2022-10-17 code/contact_force_mohseni.py

@@ -1,0 +1,481 @@
+from pysph.sph.equation import Equation
+
+
+class ComputeContactForceNormalsMohseni(Equation):
+    """Shoya Mohseni Mofidi, Particle Based Numerical Simulation Study of Solid
+    Particle Erosion of Ductile Materials Leading to an Erosion Model, Including
+    the Particle Shape Effect
+
+    Equation 22 of Materials 2022
+
+    Compute the normals on the rigid body particles (secondary surface) which is
+    interacting with wall (primary surface). Here we expect the wall has a
+    property identifying its boundary particles. Currently this equation only
+    assumes the simulation has only one rigid body with a single wall.
+
+    """
+    def initialize(self, d_idx,
+                   d_m,
+                   d_contact_force_normal_tmp_x,
+                   d_contact_force_normal_tmp_y,
+                   d_contact_force_normal_tmp_z,
+                   d_contact_force_normal_wij,
+                   d_total_no_bodies,
+                   dt, t):
+        i, t1, t2 = declare('int', 3)
+
+        t1 = d_total_no_bodies[0] * d_idx
+
+        for i in range(d_total_no_bodies[0]):
+            t2 = t1 + i
+            d_contact_force_normal_tmp_x[t2] = 0.
+            d_contact_force_normal_tmp_y[t2] = 0.
+            d_contact_force_normal_tmp_z[t2] = 0.
+            d_contact_force_normal_wij[t2] = 0.
+
+    def loop(self, d_idx,
+             d_rho, d_m, RIJ, XIJ,
+             s_idx,
+             d_contact_force_normal_tmp_x,
+             d_contact_force_normal_tmp_y,
+             d_contact_force_normal_tmp_z,
+             d_contact_force_normal_wij,
+             s_contact_force_is_boundary,
+             s_dem_id,
+             d_dem_id,
+             d_normal,
+             d_total_no_bodies,
+             dt, t, WIJ):
+        t1, t2 = declare('int', 3)
+
+        if s_contact_force_is_boundary[s_idx] == 1.:
+            if d_dem_id[d_idx] != s_dem_id[s_idx]:
+
+                t1 = d_total_no_bodies[0] * d_idx
+
+                tmp = d_m[d_idx] / (d_rho[d_idx] * RIJ) * WIJ
+
+                t2 = t1 + s_dem_id[s_idx]
+                d_contact_force_normal_tmp_x[t2] += XIJ[0] * tmp
+                d_contact_force_normal_tmp_y[t2] += XIJ[1] * tmp
[…]

### 2022-10-17 code/dem_2d.py

@@ -1,0 +1,260 @@
+import numpy as np
+
+from pysph.sph.scheme import add_bool_argument
+
+from pysph.sph.equation import Equation
+from pysph.sph.scheme import Scheme
+from pysph.sph.scheme import add_bool_argument
+from pysph.tools.sph_evaluator import SPHEvaluator
+from pysph.sph.equation import Group, MultiStageEquations
+from pysph.sph.integrator import EPECIntegrator
+from pysph.base.kernels import (QuinticSpline)
+from textwrap import dedent
+from compyle.api import declare
+from math import log, sqrt
+
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator_step import IntegratorStep
+
+# from pysph.sph.rigid_body import (BodyForce)
+
+from pysph.base.kernels import CubicSpline
+
+from pysph.sph.wc.gtvf import GTVFIntegrator
+from rigid_body_common import (add_properties_stride,
+                               set_total_mass, set_center_of_mass,
+                               set_body_frame_position_vectors,
+                               set_body_frame_normal_vectors,
+                               set_moment_of_inertia_and_its_inverse,
+                               BodyForce, SumUpExternalForces,
+                               normalize_R_orientation,
+                               ComputeContactForceNormals,
+                               ComputeContactForceDistanceAndClosestPoint,
+                               ComputeContactForce)
+
+from contact_force_mohseni_vyas import (
+    ComputeContactForceNormalsMV,
+    ComputeContactForceDistanceAndClosestPointAndWeightDenominatorMV,
+    ComputeContactForceMV,
+    TransferContactForceMV)
+
+# compute the boundary particles
+from boundary_particles import (get_boundary_identification_etvf_equations,
+                                add_boundary_identification_properties)
+from numpy import sin, cos
+
+
+class GTVFDEMStep(IntegratorStep):
+    def stage1(self, d_idx, d_m, d_x, d_y, d_z, d_u, d_v, d_w, d_fx, d_fy,
+               d_fz, d_wz, d_torz, d_moi, dt):
+        dtb2 = 0.5 * dt
+        d_u[d_idx] = d_u[d_idx] + dtb2 * d_fx[d_idx] / d_m[d_idx]
+        d_v[d_idx] = d_v[d_idx] + dtb2 * d_fy[d_idx] / d_m[d_idx]
+        d_w[d_idx] = d_w[d_idx] + dtb2 * d_fz[d_idx] / d_m[d_idx]
+
[…]

### 2022-10-17 code/dinesh_2022_3d_dam_break.py

@@ -16,6 +16,7 @@ from pysph.solver.application import Application
 from pysph.sph.scheme import SchemeChooser
 
 from rigid_fluid_coupling import RigidFluidCouplingScheme
+from fluids import CTVFScheme, GTVFScheme
 
 from pysph.examples.solid_mech.impact import add_properties
 from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
@@ -204,7 +205,28 @@ class DamBreak3D(Application):
                                        gz=self.gz,
                                        nu=0.,
                                        h=self.h)
-        s = SchemeChooser(default='rfc', rfc=rfc)
+
+        ctvf = CTVFScheme(fluids=['fluid'],
+                          boundaries=['tank'],
+                          dim=3,
+                          rho0=self.fluid_density,
+                          p0=self.p0,
+                          c0=self.c0,
+                          gz=self.gz,
+                          nu=0.,
+                          h=self.h)
+
+        gtvf = GTVFScheme(fluids=['fluid'],
+                          boundaries=['tank'],
+                          dim=3,
+                          rho0=self.fluid_density,
+                          p0=self.p0,
+                          c0=self.c0,
+                          gz=self.gz,
+                          nu=0.,
+                          h=self.h)
+
+        s = SchemeChooser(default='rfc', rfc=rfc, ctvf=ctvf, gtvf=gtvf)
         return s
 
     def configure_scheme(self):

### 2022-10-17 code/dinesh_2022_half_density_sphere_inside_hydrostatic_tank.py

@@ -1,0 +1,527 @@
+"""[1] A 3D simulation of a moving solid in viscous free-surface flows by
+coupling SPH and DEM
+
+3.2 Falling solid in water.
+
+"""
+from __future__ import print_function
+import numpy as np
+
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from pysph.base.utils import (get_particle_array)
+
+# from rigid_body_3d import RigidBody3DScheme
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from rigid_fluid_coupling import get_files_at_given_times_from_log
+from pysph.sph.equation import Equation, Group
+import os
+from pysph.tools import geometry as G
+
+from pysph.tools.geometry import get_2d_block, get_2d_tank, rotate
+from geometry import hydrostatic_tank_2d
+
+
+def create_circle_1(diameter=1, spacing=0.05, center=None):
+    dx = spacing
+    x = [0.0]
+    y = [0.0]
+    r = spacing
+    nt = 0
+    radius = diameter / 2.
+
+    tmp_dist = radius - spacing/2.
+    i = 0
+    while tmp_dist > spacing/2.:
+        perimeter = 2. * np.pi * tmp_dist
+        no_of_points = int(perimeter / spacing) + 1
+        theta = np.linspace(0., 2. * np.pi, no_of_points)
+        for t in theta[:-1]:
+            x.append(tmp_dist * np.cos(t))
+            y.append(tmp_dist * np.sin(t))
+        i = i + 1
+        tmp_dist = radius - spacing/2. - i * spacing
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
+def create_circle(diameter=1, spacing=0.05, center=None):
+    radius = diameter/2.
+    xtmp, ytmp = get_2d_block(spacing, diameter+spacing, diameter+spacing)
+    x = []
+    y = []
+    for i in range(len(xtmp)):
+        dist = xtmp[i]**2. + ytmp[i]**2.
+        if dist < radius**2:
+            x.append(xtmp[i])
+            y.append(ytmp[i])
+
+    x = np.array(x)
+    y = np.array(y)
+    x, y = (t.ravel() for t in (x, y))
+    if center is None:
+        return x, y
+    else:
+        return x + center[0], y + center[1]
+
+
[…]

### 2022-10-17 code/dinesh_2022_hydrostatic_tank_2d.py

@@ -37,6 +37,7 @@ class Dinesh2022HydrostaticTank2D(Application):
         self.fluid_density = 1000.0
         self.fluid_spacing = spacing
 
+        self.tank_denstiy = 1000
         self.tank_length = 150. * 1e-3
         self.tank_height = 140 * 1e-3
         self.tank_spacing = spacing
@@ -72,10 +73,19 @@ class Dinesh2022HydrostaticTank2D(Application):
                            default=5. * 1e-3,
                            help="Spacing between particles")
 
+        group.add_argument("--tank-rho",
+                           action="store",
+                           type=float,
+                           dest="tank_rho",
+                           default=1000.,
+                           help="Density of tank")
+
     def consume_user_options(self):
         spacing = self.options.dx
         self.fluid_spacing = spacing
         self.tank_spacing = spacing
+
+        self.tank_density = self.options.tank_rho
 
     def create_particles(self):
 
@@ -98,12 +108,13 @@ class Dinesh2022HydrostaticTank2D(Application):
         # set the initial pressure
         fluid.p[:] = - self.fluid_density * self.gy * (max(fluid.y) - fluid.y[:])
 
+        m_tank = self.tank_density * self.tank_spacing**self.dim
         tank = get_particle_array(x=xt,
                                   y=yt,
-                                  m=m_fluid,
+                                  m=m_tank,
                                   m_fluid=m_fluid,
                                   h=self.h,
-                                  rho=self.fluid_density,
+                                  rho=self.tank_density,
                                   rad_s=self.fluid_spacing/2.,
                                   contact_force_is_boundary=1.,
                                   name="tank",
@@ -126,7 +137,8 @@ class Dinesh2022HydrostaticTank2D(Application):
     def create_scheme(self):
         rfc = RigidFluidCouplingScheme(rigid_bodies=None,
                                        fluids=['fluid'],
-                                       boundaries=['tank'],
+                                       rigid_bodies_dynamic=None,
+                                       rigid_bodies_static=['tank'],
                                        dim=self.dim,
                                        rho0=self.fluid_density,
                                        p0=self.p0,

### 2022-10-17 code/dinesh_2022_particle_bouncing_on_a_wall_2d.py

@@ -1,0 +1,202 @@
+"""
+Single particle bouncing on a wall
+"""
+import numpy as np
+
+from pysph.base.kernels import QuinticSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from dem_2d import DEMScheme
+from rigid_body_common import setup_damping_coefficient
+
+from rigid_fluid_coupling import RigidFluidCouplingScheme
+from geometry import hydrostatic_tank_2d
+from rigid_fluid_coupling import get_files_at_given_times_from_log
+import os
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class ParticleOnAWall2D(Application):
+    def initialize(self):
+        spacing = 0.5
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 5
+        self.tank_spacing = spacing
+
+        self.particle_density = 20
+        self.particle_spacing = spacing
+        self.particle_radius = spacing
+        self.particle_h = self.hdx * self.particle_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gx = 0.
+        self.gy = -9.81
+        self.gz = 0.
+        self.dim = 2
+
+    # def add_user_options(self, group):
+    #     from pysph.sph.scheme import add_bool_argument
+    #     add_bool_argument(group, 'two-cubes', dest='use_two_cubes',
+    #                       default=False, help='Use two cubes')
+
+    #     add_bool_argument(group, 'three-cubes', dest='use_three_cubes',
+    #                       default=False, help='Use three cubes')
[…]

### 2022-10-17 code/fluids.py

@@ -12,20 +12,10 @@ from pysph.sph.integrator_step import IntegratorStep
 from pysph.sph.scheme import Scheme
 from pysph.sph.scheme import add_bool_argument
 from pysph.tools.sph_evaluator import SPHEvaluator
-from pysph.base.kernels import (CubicSpline, WendlandQuintic, QuinticSpline,
-                                WendlandQuinticC4, Gaussian, SuperGaussian)
-
-from solid_mech import (ComputeAuHatETVF, ComputeAuHatETVFSun2019,
-                        SavePositionsIPSTBeforeMoving, AdjustPositionIPST,
-                        CheckUniformityIPST, ComputeAuhatETVFIPST,
-                        ResetParticlePositionsIPST, setup_ipst,
-                        SetHIJForInsideParticles, ContinuityEquationUhat,
-                        ContinuityEquationETVFCorrection, GTVFEOS, ComputeAuHatGTVF,
-                        VelocityGradient2DUhat)
+from pysph.base.kernels import QuinticSpline
 
 from pysph.sph.wc.edac import (SolidWallPressureBC)
 
-from pysph.sph.integrator import PECIntegrator
 from boundary_particles import (add_boundary_identification_properties)
 
 from boundary_particles import (ComputeNormals, SmoothNormals,
@@ -45,164 +35,6 @@ from pysph.sph.solid_mech.basic import (get_speed_of_sound, get_bulk_mod,
 from solid_mech_common import AddGravityToStructure
 from pysph.sph.wc.transport_velocity import (MomentumEquationArtificialViscosity)
 from fsi_coupling import (ClampWallPressure, ClampWallPressureFSI)
-
-
-class SolidWallPressureBCFSI(Equation):
-    r"""Solid wall pressure boundary condition from Adami and Hu (transport
-    velocity formulation).
-
-    """
-    def __init__(self, dest, sources, gx=0.0, gy=0.0, gz=0.0):
-        self.gx = gx
-        self.gy = gy
-        self.gz = gz
-
-        super(SolidWallPressureBCFSI, self).__init__(dest, sources)
-
[…]

### 2022-10-17 code/mohseni_2021_controlled_sliding_on_a_flat_surface.py

@@ -1,0 +1,170 @@
+"""
+Test the collision of two rigid bodues made of same particle array
+"""
+import numpy as np
+
+from pysph.base.kernels import CubicSpline
+# from pysph.base.utils import get_particle_array_rigid_body
+from pysph.base.utils import get_particle_array
+from pysph.sph.integrator import EPECIntegrator
+from pysph.solver.application import Application
+from pysph.sph.scheme import SchemeChooser
+
+from rigid_body_3d import RigidBody3DScheme
+from geometry import hydrostatic_tank_2d
+
+from pysph.examples.solid_mech.impact import add_properties
+from pysph.examples.rigid_body.sphere_in_vessel_akinci import (create_boundary,
+                                                               create_fluid,
+                                                               create_sphere)
+from pysph.tools.geometry import get_2d_block
+
+
+class Simulation1Dinesh2022BouncingCubeOnAWall2D(Application):
+    def initialize(self):
+        spacing = 0.05
+        self.hdx = 1.3
+
+        self.fluid_length = 1.0
+        self.fluid_height = 1.0
+        self.fluid_density = 1000.0
+        self.fluid_spacing = spacing
+
+        self.tank_height = 1.5
+        self.tank_layers = 5
+        self.tank_spacing = spacing
+
+        self.body_height = 0.2
+        self.body_length = 0.2
+        self.body_density = 2000
+        self.body_spacing = spacing / 2.
+        self.body_h = self.hdx * self.body_spacing
+
+        self.h = self.hdx * self.fluid_spacing
+
+        # self.solid_rho = 500
+        # self.m = 1000 * self.dx * self.dx
+        self.co = 10 * np.sqrt(2 * 9.81 * self.fluid_height)
+        self.p0 = self.fluid_density * self.co**2.
+        self.c0 = self.co
+        self.alpha = 0.1
+        self.gx = 0.
+        self.gy = -9.81
+        self.gz = 0.
+        self.dim = 2
+
+    def create_particles(self):
+        xf, yf, xt, yt = hydrostatic_tank_2d(
+            self.fluid_length, self.fluid_height, self.tank_height,
+            self.tank_layers, self.body_spacing, self.body_spacing)
+
+        m_fluid = self.fluid_density * self.fluid_spacing**2.
+
+        xb1, yb1 = get_2d_block(dx=self.body_spacing,
+                                length=self.body_length,
+                                height=self.body_height)
[…]

### 2022-10-17 code/nrbc.py

@@ -1,0 +1,130 @@
+from pysph.sph.equation import Equation
+
+
+class ShepardInterpolateCharacteristics(Equation):
+    def initialize(self, d_idx, d_J1, d_J2u, d_J3u, d_J2v, d_J3v):
+        d_J1[d_idx] = 0.0
+        d_J2u[d_idx] = 0.0
+        d_J3u[d_idx] = 0.0
+
+        d_J2v[d_idx] = 0.0
+        d_J3v[d_idx] = 0.0
+
+    def loop(self, d_idx, d_J1, d_J2u, s_J1, s_J2u, d_J3u, s_J3u, s_idx, s_J2v,
+             s_J3v, d_J2v, d_J3v, WIJ):
+        d_J1[d_idx] += s_J1[s_idx] * WIJ
+        d_J2u[d_idx] += s_J2u[s_idx] * WIJ
+        d_J3u[d_idx] += s_J3u[s_idx] * WIJ
+
+        d_J2v[d_idx] += s_J2v[s_idx] * WIJ
+        d_J3v[d_idx] += s_J3v[s_idx] * WIJ
+
+    def post_loop(self, d_idx, d_J1, d_J2u, d_wij, d_avg_j2u, d_avg_j1, d_J3u,
+                  d_avg_j3u, d_J2v, d_J3v, d_avg_j2v, d_avg_j3v):
+        if d_wij[d_idx] > 1e-14:
+            d_J1[d_idx] /= d_wij[d_idx]
+            d_J2u[d_idx] /= d_wij[d_idx]
+            d_J3u[d_idx] /= d_wij[d_idx]
+
+            d_J2v[d_idx] /= d_wij[d_idx]
+            d_J3v[d_idx] /= d_wij[d_idx]
+
+        else:
+            d_J1[d_idx] = d_avg_j1[0]
+            d_J2u[d_idx] = d_avg_j2u[0]
+            d_J3u[d_idx] = d_avg_j3u[0]
+
+            d_J2v[d_idx] = d_avg_j2v[0]
+            d_J3v[d_idx] = d_avg_j3v[0]
+
+    def reduce(self, dst, t, dt):
+        dst.avg_j1[0] = numpy.average(dst.J1[dst.wij > 0.0001])
+        dst.avg_j2u[0] = numpy.average(dst.J2u[dst.wij > 0.0001])
+        dst.avg_j3u[0] = numpy.average(dst.J3u[dst.wij > 0.0001])
[…]

### 2022-10-17 code/rigid_body_3d.py

@@ -31,6 +31,12 @@ from rigid_body_common import (add_properties_stride,
                                ComputeContactForceDistanceAndClosestPoint,
                                ComputeContactForce)
 
+from contact_force_mohseni import (
+    ComputeContactForceNormalsMohseni,
+    ComputeContactForceDistanceAndClosestPointMohseni,
+    ComputeContactForceMohseni,
+    TransferContactForceMohseni)
+
 from contact_force_mohseni_vyas import (
     ComputeContactForceNormalsMV,
     ComputeContactForceDistanceAndClosestPointAndWeightDenominatorMV,
@@ -711,7 +717,7 @@ class RigidBody3DScheme(Scheme):
                            type=float,
                            help="Friction coefficient")
 
-        choices = ['Mohseni', 'Mohseni_Vyas']
+        choices = ['Mohseni', 'Mohseni_Vyas', 'New']
         group.add_argument(
             "--contact-force-model", action="store",
             dest='contact_force_model',
@@ -778,7 +784,54 @@ class RigidBody3DScheme(Scheme):
 
                 stage2.append(Group(equations=g5, real=False))
 
+            if len(self.rigid_bodies) > 0:
+                g5 = []
+                for name in self.rigid_bodies:
+                    g5.append(
+                        TransferContactForceMV(dest=name,
+                                               sources=self.rigid_bodies))
+
+                stage2.append(Group(equations=g5, real=False))
+
         elif self.contact_force_model == 'Mohseni_Vyas':
+            if len(self.rigid_bodies) > 0:
+                g5 = []
+                for name in self.rigid_bodies:
+                    g5.append(
+                        ComputeContactForceNormalsMV(dest=name,
+                                                   sources=self.rigid_bodies+self.boundaries))
+
+                stage2.append(Group(equations=g5, real=False))
+
+                g5 = []
+                for name in self.rigid_bodies:
+                    g5.append(
+                        ComputeContactForceDistanceAndClosestPointAndWeightDenominatorMV(
+                            dest=name, sources=self.rigid_bodies+self.boundaries))
+                stage2.append(Group(equations=g5, real=False))
+
+            if len(self.rigid_bodies) > 0:
+                g5 = []
+                for name in self.rigid_bodies:
+                    g5.append(
+                        ComputeContactForceLinearMV(dest=name,
+                                                    sources=None,
+                                                    kr=self.kr,
+                                                    kf=self.kf,
+                                                    fric_coeff=self.fric_coeff))
+
[…]
